### 2014-04-18 paper/paper.tex
Paper templates

% -----------------------------------------------
% Template for ISMIR 2014
% (based on earlier ISMIR templates)
% -----------------------------------------------

\documentclass{article}
\usepackage{ismir2014,amsmath,cite}
\usepackage{graphicx}

% Title.
% ------
\title{PAPER TEMPLATE FOR ISMIR 2014}

% Single address
% To use with only one author or several with the same address
% ---------------
%\oneauthor
% {Names should be omitted for double-blind reviewing}
% {Affiliations should be omitted for double-blind reviewing}

% Two addresses
% --------------
%\twoauthors
%  {First author} {School \\ Department}
%  {Second author} {Company \\ Address}

% Three addresses
% --------------
\threeauthors
  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
  {Second author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}

% Four addresses
% --------------
%\fourauthors
%  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
%  {Second author}{Affiliation2 \\ {\tt author2@ismir.edu}}
%  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}
%  {Fourth author} {Affiliation4 \\ {\tt author4@ismir.edu}}

\begin{document}
%
\maketitle
%
\begin{abstract}
The abstract should be placed at the top left column and should contain about 150-200 words.
\end{abstract}
%
\section{Introduction}\label{sec:introduction}

This template includes all the information about formatting manuscripts for the ISMIR 2014.
Please follow these guidelines to give the final proceedings a uniform look.
If you have any questions, please contact the Conference Management.
This template can be downloaded from the ISMIR 2014 web site (http://ismir2014.ismir.net).

\section{Page Size}\label{sec:page_size}

The proceedings will be printed on
 \underline{portrait A4-size paper} \underline{(21.0cm x 29.7cm)}.
All material on each page should fit within a rectangle of 17.2cm x 25.2cm,
centered on the page, beginning 2.0cm
from the top of the page and ending with 2.5cm from the bottom.
The left and right margins should be 1.9cm.
The text should be in two 8.2cm columns with a 0.8cm gutter.
All text must be in a two-column format.
Text must be fully justified.

\section{Typeset Text}\label{sec:typeset_text}

\subsection{Normal or Body Text}\label{subsec:body}

Please use a 10pt (point) Times font. Sans-serif or non-proportional fonts
can be used only for special purposes, such as distinguishing source code text.

The first paragraph in each section should not be indented, but all other paragraphs should be.

\subsection{Title and Authors}

The title is 14pt Times, bold, caps, upper case, centered.
Authors' names are omitted when submitting for double-blind reviewing.
The following is for making a camera-ready version.
Authors' names are centered.
The lead author's name is to be listed first (left-most), and the co-authors' names after.
If the addresses for all authors are the same, include the address only once, centered.
If the authors have different addresses, put the addresses, evenly spaced, under each authors' name.

\subsection{First Page Copyright Notice}

Please include the copyright notice exactly as it appears here in the lower left-hand corner of the page.
It is set in 8pt Times.

\subsection{Page Numbering, Headers and Footers}

Do not include headers, footers or page numbers in your submission.
These will be added when the publications are assembled.

\section{First Level Headings}

First level headings are in Times 10pt bold,
centered with 1 line of space above the section head, and 1/2 space below it.
For a section header immediately followed by a subsection header, the space should be merged.

\subsection{Second Level Headings}

Second level headings are in Times 10pt bold, flush left,
with 1 line of space above the section head, and 1/2 space below it.
The first letter of each significant word is capitalized.

\subsubsection{Third and Further Level Headings}

Third level headings are in Times 10pt italic, flush left,
with 1/2 line of space above the section head, and 1/2 space below it.
The first letter of each significant word is capitalized.

Using more than three levels of headings is highly discouraged.

\section{Footnotes and Figures}

\subsection{Footnotes}

Indicate footnotes with a number in the text.\footnote{This is a footnote.}
Use 8pt type for footnotes. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a 0.5pt horizontal rule.

\subsection{Figures, Tables and Captions}

All artwork must be centered, neat, clean, and legible.
All lines should be very dark for purposes of reproduction and art work should not be hand-drawn.
The proceedings are not in color, and therefore all figures must make sense in black-and-white form.
Figure and table numbers and captions always appear below the figure.
Leave 1 line space between the figure or table and the caption.
Each figure or table is numbered consecutively. Captions should be Times 10pt.
Place tables/figures in text as close to the reference as possible.
References to tables and figures should be capitalized, for example:
see \figref{fig:example} and \tabref{tab:example}.
Figures and tables may extend across both columns to a maximum width of 17.2cm.

\begin{table}
 \begin{center}
 \begin{tabular}{|l|l|}
  \hline
  String value & Numeric value \\
  \hline
  Hello ISMIR  & 2014 \\
  \hline
 \end{tabular}
\end{center}
 \caption{Table captions should be placed below the table.}
 \label{tab:example}
\end{table}

%\begin{figure}
% \centerline{\framebox{
% \includegraphics[width=\columnwidth]{figure.png}}}
% \caption{Figure captions should be placed below the figure.}
% \label{fig:example}
%\end{figure}

\section{Equations}

Equations should be placed on separated lines and numbered.
The number should be on the right side, in parentheses.

\begin{equation}
E=mc^{2}
\end{equation}

\section{Citations}

All bibliographical references should be listed at the end,
inside a section named ``REFERENCES,'' numbered and in alphabetical order.
Also, all references listed should be cited in the text.
When referring to a document, type the numbering square brackets
\cite{Author:00} or \cite{Author:00,Someone:10,Someone:04}.

\begin{thebibliography}{citations}

\bibitem {Author:00}
E. Author:
``The Title of the Conference Paper,''
{\it Proceedings of the International Symposium
on Music Information Retrieval}, pp.~000--111, 2000.

\bibitem{Someone:10}
A. Someone, B. Someone, and C. Someone:
``The Title of the Journal Paper,''
{\it Journal of New Music Research},
Vol.~A, No.~B, pp.~111--222, 2010.

\bibitem{Someone:04} X. Someone and Y. Someone: {\it Title of the Book},
    Editorial Acme, Porto, 2012.

\end{thebibliography}

%\bibliography{ismir2014template}

\end{document}

### 2014-04-19 paper/paper.tex
Added first pass at chord eval stuff. Floating nowhere and could use some work (to be condensed, almost certainly), but a reasonable first-take.

@@
 
-\subsection{Second Level Headings}
+\subsection{Chord Recognition}
 
-Second level headings are in Times 10pt bold, flush left,
-with 1 line of space above the section head, and 1/2 space below it.
-The first letter of each significant word is capitalized.
+% relevant papers
+% - pauwels & peeters
+% - matthais
+% - harte
+% - mirex 
+% - Utrecht agreement
+
+Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord recognition is an ongoing topic of discussion.
+%For example, ISMIR 2010 saw the fondly dubbed ``Utrecht Agreement on Chord Evaluation''\footnote{http://www.music-ir.org/mirex/wiki/The\_Utrecht\_Agreement\_on\_Chord\_Evaluation}, in which interested researchers met to discuss sane ways of quantifying the performance of automatic chord recognition systems.
+Sseveral recent articles address issues and concerns with vocabularies, comparison semantics, and other lexicographical challenges unique to chord recognition \cite{}.
+Ultimately, the source of this difficulty stems from the inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{McVicar}.
+As a result, a consensus has yet to be reached regarding the single best approach to comparing two sequences of chord labels, and instead are often compared over a set of rules, e.g Major-Minor, Sevenths, with or without inversions, and so on.
+
+Thanks to the previous efforts of Harte \cite{}, text representations of chord labels adhere to a standardized format, consisting of a root, quality, extensions, and a bass note; of these, only the root is strictly required.
+However, in order to efficiently compare chords in a variety of different ways, it is helpful to first translate a given chord label $\mathcal{C}$ into a numerical representation, shown in Figure \ref{}.
+In this example, a $G:7(9)/5$ is mapped to split into 4 pieces of information: one, the root is mapped to an absolute pitch class $\mathcal{R}$, in $[0, 11]$, where $C\to0$, $C\sharp/D\flat\to1$, etc; two, the quality is mapped to a root-invariant 12-dimensional bit vector $\mathcal{Q}$ by setting the scale degrees of the quality; three, any extensions are applied (via addition or omission) to the quality bit vector as scale degrees in a single octave, resulting in pitch vector $\mathcal{P}$; and four, the bass interval (5) is translated to the relative scale degree in semitones $\mathcal{B}$.
+Note that the add-9 is rolled into a single octave as an add-2.
+This is a matter of convenience as extended chords (9's, 11's or 13's) are traditionally resolved to a single-octave equivalent, but the bit-vector representation could be easily expanded to represent such information.
+
+Having gone through this bit of effort, it is now straightforward to compare chords along the five rules used in MIREX 2013:
+\begin{enumerate}
+\item Root:
+	\begin{enumerate}
+	\item $\mathcal{R}_{est} == \mathcal{R}_{ref}$
+	\item $\forall \mathcal{Q}_{ref}$
+	\end{enumerate}
+\item Major-Minor: Rule 1.a, plus
+	\begin{enumerate}
+	\item $\mathcal{Q}_{est} == \mathcal{Q}_{ref}$
+	\item $\mathcal{Q}_{ref} \in \{Maj, min\}$ 
+	\end{enumerate}
+\item Major-Minor w/Inversions: Rule 2, plus
+	\begin{enumerate}
+	\item $\mathcal{B}_{ref} \in \mathcal{Q}_{ref}$
+	\end{enumerate}
+\item Sevenths: Rule 1.1, plus
+	\begin{enumerate}
+	\item $\mathcal{Q}_{est} == \mathcal{Q}_{ref} $
+	\item $ \mathcal{Q}_{ref} \in \{Maj, min, Maj7, min7, 7\}$ 
+	\end{enumerate}
+\item Sevenths w/Inversions: Rule 4, plus
+	\begin{enumerate}
+	\item $\mathcal{B}_{ref} \in \mathcal{Q}_{ref}$ 
+	\end{enumerate}
+\end{enumerate}
+
+Following recent trends in MIREX, an overall score is computed by weighting each comparison by the duration of its interval, over all intervals; stated another way, this is the piecewise continuous-time integral of the intersection of two chord sequences, $(\mathbf{C}_{ref}, \mathbf{C}_{est})$, expressed as follows:
+
+\begin{equation}
+S(\mathbf{C}_{ref}, \mathbf{C}_{est}) = \frac{1}{T}\int_{t=0}^{T} \mathcal{C}_{ref}(t) == \mathcal{C}_{est}(t)
+\end{equation}
+
+\noindent Here, this is achieved here by forming the union of the boundaries in each sequence, and summing the time intervals of the correct ranges.
+Note that equivalence is subject to one of the rules defined previously.
+
+Finally, the total score over a set of $N$ items is given by a discrete summation, where the importance of each score, $S_n$, is weighted by the duration, $T_n$, of each annotation:
+
+\begin{equation}
+S_{total} = \frac{\sum_{n=0}^{N} T_n*S_n}{\sum_{n=0}^{N} T_n}
+\end{equation}
 

### 2014-04-22 code/segmentation/test_segment.py
mirex test cases for segmentation

@@ -1,0 +1,109 @@
+'''
+Unit tests for mir_eval.segment
+'''
+
+import numpy as np
+import json
+import mir_eval
+import glob
+
+# We only need 1% absolute tolerance
+A_TOL = 1e-2
+
+# Path to the fixture files
+REF_GLOB    = 'data/ref*.lab'
+EST_GLOB    = 'data/est*.lab'
+MIREX_GLOB  = 'data/score*.json'
+
+def generate_data():
+
+    ref_files = sorted(glob.glob(REF_GLOB))
+    est_files = sorted(glob.glob(EST_GLOB))
+    sco_files = sorted(glob.glob(MIREX_GLOB))
+
+    for ref_f, est_f, sco_f in zip(ref_files, est_files, sco_files):
+        ref_t, ref_l = mir_eval.io.load_intervals(ref_f)
+        est_t, est_l = mir_eval.io.load_intervals(est_f)
+
+        with open(sco_f, 'r') as f:
+            scores = json.load(f)
+
+        yield ref_t, ref_l, est_t, est_l, scores
+
+def test_boundary_detection():
+
+    def __test_detection(_window, _ref_t, _est_t):
+        precision, recall, fmeasure = mir_eval.boundary.detection(_ref_t, _est_t, window=_window)
+
+        assert np.allclose(precision,   scores['P@%.1f'%_window], atol=A_TOL)
+        assert np.allclose(recall,      scores['R@%.1f'%_window], atol=A_TOL)
+        assert np.allclose(fmeasure,    scores['F@%.1f'%_window], atol=A_TOL)
+
+    # Iterate over fixtures
+    for ref_t, ref_l, est_t, est_l, scores in generate_data():
+
+        # Test boundary detection at each window size
+        for window in [0.5, 3.0]:
+            yield (__test_detection, window, ref_t, est_t)
+
+    # Done
+    pass
+
+def test_boundary_deviation():
+    def __test_deviation(_ref_t, _est_t):
+        t_to_p, p_to_t = mir_eval.boundary.deviation(_ref_t, _est_t)
+
+        assert np.allclose(t_to_p,  scores['T_to_P'], atol=A_TOL)
+        assert np.allclose(p_to_t,  scores['P_to_T'], atol=A_TOL)
+
+    # Iterate over fixtures
+    for ref_t, ref_l, est_t, est_l, scores in generate_data():
+        # Test boundary deviation
[…]

### 2014-04-22 paper/paper.tex
checking in makefile for paper

@@
 %For example, ISMIR 2010 saw the fondly dubbed ``Utrecht Agreement on Chord Evaluation''\footnote{http://www.music-ir.org/mirex/wiki/The\_Utrecht\_Agreement\_on\_Chord\_Evaluation}, in which interested researchers met to discuss sane ways of quantifying the performance of automatic chord recognition systems.
-Sseveral recent articles address issues and concerns with vocabularies, comparison semantics, and other lexicographical challenges unique to chord recognition \cite{}.
+Several recent articles address issues and concerns with vocabularies, comparison semantics, and other lexicographical challenges unique to chord recognition \cite{}.
 Ultimately, the source of this difficulty stems from the inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{McVicar}.

### 2014-04-25 paper/paper.tex
Working on the patter discovery subsection

@@
 
+\subsection{Pattern Discovery}
+
+This recent MIREX task aims to evaluate algorithms that identify musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
+Given the novelty of this task, the metrics used in 2013 (the first year to appear on MIREX) are subject to modifications in further editions.
+However, Colins\cite{TomColins2013} put together all the available metrics for this task for the first MIREX edition, which resulted in 21 different scores, each one implemented in MIR eval.
+
 \subsubsection{Third and Further Level Headings}

### 2014-04-27 paper/paper.tex
added bib file, starting melody section

--- 2014-04-22 paper/paper.tex
@@
 
+\subsection{Melody Extraction}
+Melody extraction, or predominant fundamental frequency ($f_0$) estimation,
+involves the estimation of the pitch ($f_0$) sequence of the melody from a
+polyphonic music recording \cite{salamon:MelodyReview:IEEESPM13}.
+
 \subsubsection{Third and Further Level Headings}
@@
 
-\begin{thebibliography}{citations}
+% \begin{thebibliography}{citations}
+% 
+% \bibitem {Author:00}
+% E. Author:
+% ``The Title of the Conference Paper,''
+% {\it Proceedings of the International Symposium
+% on Music Information Retrieval}, pp.~000--111, 2000.
+% 
+% \bibitem{Someone:10}
+% A. Someone, B. Someone, and C. Someone:
+% ``The Title of the Journal Paper,''
+% {\it Journal of New Music Research},
+% Vol.~A, No.~B, pp.~111--222, 2010.
+% 
+% \bibitem{Someone:04} X. Someone and Y. Someone: {\it Title of the Book},
+%     Editorial Acme, Porto, 2012.
+% 
+% \end{thebibliography}
 
-\bibitem {Author:00}
-E. Author:
-``The Title of the Conference Paper,''
-{\it Proceedings of the International Symposium
-on Music Information Retrieval}, pp.~000--111, 2000.
-
-\bibitem{Someone:10}
-A. Someone, B. Someone, and C. Someone:
-``The Title of the Journal Paper,''
-{\it Journal of New Music Research},
-Vol.~A, No.~B, pp.~111--222, 2010.
-
-\bibitem{Someone:04} X. Someone and Y. Someone: {\it Title of the Book},
-    Editorial Acme, Porto, 2012.
-
-\end{thebibliography}
-
-%\bibliography{ismir2014template}
+\bibliography{mir_eval}
 

### 2014-04-27 paper/paper.tex
more melody

@@
 \subsection{Melody Extraction}
-Melody extraction, or predominant fundamental frequency ($f_0$) estimation,
-involves the estimation of the pitch ($f_0$) sequence of the melody from a
-polyphonic music recording \cite{salamon:MelodyReview:IEEESPM13}.
+\subsubsection{Task definition}
+Melody extraction algorithms aim to produce a sequence of frequency values
+corresponding to the pitch of the dominant melody from a musical recording
+\cite{salamon:MelodyReview:IEEESPM13}. The estimated pitch is represented as a
+time series of fundamental frequency ($f_0$) values in Hz sampled on a fixed
+time grid (e.g.~every 10 ms). To evaluate the estimated sequence, a reference
+sequence is generated by running a pitch tracker on the monophonic melody track
+(requiring access to the multi-track recording session) and manually correcting
+any mistakes made by the pitch tracker. The estimate is then evaluated against
+the reference by comparing the two frequency sequences on a frame-by-frame
+basis, and computing five global measures, first used in the MIREX 2005 AME
+evaluation \cite{polinerMelodyEval}. The goal of these measures, defined below,
+is to assess the algorithm's performance on two subtasks of melody extraction:
+(1) pitch estimation, i.e.~how well the algorithm estimates the pitch of the
+melody, and (2) voicing detection, i.e.~how well the algorithm determines when
+the melody is present in a frame (a \textit{voiced} frame) or absent (an
+\textit{unvoiced} frame). To allow evaluation of these two subtasks
+independently, a melody extraction algorithm can provide a frequency estimate
+even for frames it has determined to be unvoiced.
 
-\subsubsection{Third and Further Level Headings}
+\subsubsection{Evaluation measures}
+The following definitions are taken from
+\cite{salamon:MelodyReview:IEEESPM13} with permission from the authors. Let the estimated melody pitch frequency
+vector be $\mathbf{f}$, and the true sequence (reference) be $\mathbf{f}^*$. Let
+us also define a voicing indicator vector $\mathbf{v}$, whose $\tau^\text{th}$
+element $v_\tau = 1$ when a melody pitch is detected, with corresponding ground
+truth $\mathbf{v}^*$.  We also define an ``unvoicing'' indicator $\bar{v}_\tau =
+1 - v_\tau$.  Recall that an algorithm may report an estimated melody pitch
+($f_\tau > 0$) even for times where it reports no voicing ($v_\tau = 0$).   
+Then the measures are:
+\begin{itemize}
+  \item \textbf{Voicing Recall Rate}: The proportion of frames labeled as
+  melody frames in the reference that are estimated as melody frames by the
+  algorithm.
+\begin{equation}
+\text{Rec}_\text{vx} = \frac{\sum_\tau v_\tau v^*_\tau}{\sum_\tau v^*_\tau}
+\end{equation}
 
-Third level headings are in Times 10pt italic, flush left,
-with 1/2 line of space above the section head, and 1/2 space below it.
-The first letter of each significant word is capitalized.
+  \item \textbf{Voicing False Alarm Rate}: The proportion of frames
+  labeled as non-melody in the reference that are mistakenly estimated as
+  melody frames by the algorithm.
+\begin{equation}
+\text{FA}_\text{vx} = \frac{\sum_\tau v_\tau \bar{v}^*_\tau}{\sum_\tau \bar{v}^*_\tau}
+\end{equation}
 
-Using more than three levels of headings is highly discouraged.
+  \item \textbf{Raw Pitch Accuracy}: The proportion of melody frames in the
+  reference for which $f_\tau$ is considered
+  correct (i.e.~within half a semitone of the ground
+  truth $f^*_\tau$).
+\begin{equation}
+\text{Acc}_\text{pitch}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] }{\sum_\tau v^*_\tau}
+\end{equation}
+where $\mathcal{T}$ is a threshold function defined by:
+\begin{equation}
+\mathcal{T}[a] = \begin{cases}
+1 \quad \text{if } |a| < 0.5 \\
+0 \quad \text{if } |a| \ge 0.5
+\end{cases}
+\end{equation}
+and $\mathcal{M}$ maps a frequency in Hertz to a melodic 
+axis as a real-valued number of semitones above an arbitrary
+reference frequency $f_\text{ref}$:
+\begin{equation}
+\mathcal{M}(f) = 12 \log_2\left( \frac{f}{f_\text{ref}} \right)
+\end{equation}
 
-\section{Footnotes and Figures}
+  \item \textbf{Raw Chroma Accuracy}: As raw pitch accuracy, except
+  that both the estimated and reference $f_0$ sequences are mapped onto a
+  single octave. This gives a measure of pitch accuracy which ignores octave
+  errors, a common error made by melody extraction systems:
+\begin{equation}
+\text{Acc}_\text{chroma}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\left<\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau)\right>_{12} \right] }{\sum_\tau v^*_\tau}
+\end{equation}
+Octave equivalence is achieved by taking the difference between the semitone-scale pitch 
+values modulo 12 (one octave), where
+\begin{equation}
+\left<a\right>_{12} = a - 12 \lfloor \frac{a}{12} + 0.5 \rfloor .
+\end{equation}
 
-\subsection{Footnotes}
+  \item \textbf{Overall Accuracy}: this measure combines the performance of the
+  pitch estimation and voicing detection tasks to give an overall performance
+  score for the system. It is defined as the proportion of all frames
+   correctly estimated by the algorithm, where for non-melody
+  frames this means the algorithm labeled them as non-melody, and for melody
+  frames the algorithm both labeled them as melody frames and provided a correct
+  $f_0$ estimate for the melody (i.e.~within half a semitone of the
+  reference):
 
-Indicate footnotes with a number in the text.\footnote{This is a footnote.}
-Use 8pt type for footnotes. Place the footnotes at the bottom of the page on which they appear.
-Precede the footnote with a 0.5pt horizontal rule.
+\begin{equation}
+\text{Acc}_\text{ov} 
+= \frac{1}{L} \sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] + \bar{v}^*_\tau \bar{v}_\tau 
+\end{equation}
+where $L$ is the total number of frames.
+\end{itemize}
 
-\subsection{Figures, Tables and Captions}
+The performance of an algorithm on an entire music collection for a given
+measure is obtained by averaging the per-excerpt scores for that measure over
+all excerpts in the collection.
 
-All artwork must be centered, neat, clean, and legible.
-All lines should be very dark for purposes of reproduction and art work should not be hand-drawn.
-The proceedings are not in color, and therefore all figures must make sense in black-and-white form.
-Figure and table numbers and captions always appear below the figure.
-Leave 1 line space between the figure or table and the caption.
-Each figure or table is numbered consecutively. Captions should be Times 10pt.
-Place tables/figures in text as close to the reference as possible.
-References to tables and figures should be capitalized, for example:
-see \figref{fig:example} and \tabref{tab:example}.
-Figures and tables may extend across both columns to a maximum width of 17.2cm.
+\subsubsection{Discussion}
 
-\begin{table}
- \begin{center}
- \begin{tabular}{|l|l|}
-  \hline
-  String value & Numeric value \\
-  \hline
-  Hello ISMIR  & 2014 \\
-  \hline
- \end{tabular}
-\end{center}
- \caption{Table captions should be placed below the table.}
- \label{tab:example}
-\end{table}
+% \subsection{Figures, Tables and Captions}
+% 
+% All artwork must be centered, neat, clean, and legible.
+% All lines should be very dark for purposes of reproduction and art work should not be hand-drawn.
+% The proceedings are not in color, and therefore all figures must make sense in black-and-white form.
+% Figure and table numbers and captions always appear below the figure.
+% Leave 1 line space between the figure or table and the caption.
+% Each figure or table is numbered consecutively. Captions should be Times 10pt.
+% Place tables/figures in text as close to the reference as possible.
+% References to tables and figures should be capitalized, for example:
+% see \figref{fig:example} and \tabref{tab:example}.
+% Figures and tables may extend across both columns to a maximum width of 17.2cm.
+
+% \begin{table}
+%  \begin{center}
+%  \begin{tabular}{|l|l|}
+%   \hline
+%   String value & Numeric value \\
+%   \hline
+%   Hello ISMIR  & 2014 \\
+%   \hline
+%  \end{tabular}
+% \end{center}
+%  \caption{Table captions should be placed below the table.}
+%  \label{tab:example}
+% \end{table}
 
@@
 %\end{figure}
-
-\section{Equations}
-
-Equations should be placed on separated lines and numbered.
-The number should be on the right side, in parentheses.
-
-\begin{equation}
-E=mc^{2}
-\end{equation}
-
-\section{Citations}
-
-All bibliographical references should be listed at the end,
-inside a section named ``REFERENCES,'' numbered and in alphabetical order.
-Also, all references listed should be cited in the text.
-When referring to a document, type the numbering square brackets
-\cite{Author:00} or \cite{Author:00,Someone:10,Someone:04}.
 

### 2014-04-27 paper/paper.tex
melody discussion

@@
 
+In the measure definitions provided above, it is assumed that both the estimate
+and reference sequences are sampled using the same time grid (hop size). In
+practice, however, this is not always the case, since the time grid of the
+reference depends on the hop size used by the pitch tracker that produced
+it, and similarly the time grid of the estimate depends on the specific melody
+extraction algorithm that produced it. This means that the sequences must be
+resampled onto a common time-grid prior to the computation of the measures. For
+the MIREX AME task, any sequence (be it reference or estimate) that is not
+sampled using a 10 ms hop size is resampled using $0^{th}$ order interpolation,
+i.e.~each frequency value in the target sequence is set to its nearest
+neighbour (in time) from the source sequence. This kind of interpolation can
+potentially have a detrimental effect on the evaluation, depending on the
+difference between the source and target time grids. In particular, it can
+result in artificially low scores for sequences with rapidly changing pitch
+values, such as opera singing with deep vibrato.
+
+For this reason, the melody evaluator in mir\_eval uses $1^{st}$ order (linear)
+interpolation by default in order to map the reference and estimate sequences
+onto a common time-grid. Assuming the original timestamps of both sequences
+correspond to the \textit{center} of each analysis frame (as they should),
+using $1^{st}$ order rather than $0^{th}$ order interpolation means the results
+returned by mir\_eval are lower-bounded by the MIREX results and are, in our
+view, more accurate.
+
 % \subsection{Figures, Tables and Captions}

### 2014-04-27 paper/paper.tex
typo

@@
 the MIREX AME task, any sequence (be it reference or estimate) that is not
-sampled using a 10 ms hop size is resampled using $0^{th}$ order interpolation,
+sampled using a 10 ms hop size is resampled using $0^{th}$-order interpolation,
 i.e.~each frequency value in the target sequence is set to its nearest
@@
 
-For this reason, the melody evaluator in mir\_eval uses $1^{st}$ order (linear)
+For this reason, the melody evaluator in mir\_eval uses $1^{st}$-order (linear)
 interpolation by default in order to map the reference and estimate sequences
@@
 correspond to the \textit{center} of each analysis frame (as they should),
-using $1^{st}$ order rather than $0^{th}$ order interpolation means the results
+using $1^{st}$-order rather than $0^{th}$-order interpolation means the results
 returned by mir\_eval are lower-bounded by the MIREX results and are, in our

### 2014-04-27 paper/paper.tex
temporary commit for pulling

--- 2014-04-27 paper/paper.tex
@@
 \usepackage{graphicx}
+
+\def\eg{\emph{e.g.\/}}
+\def\ie{\emph{i.e.\/}}
+\def\etc{\emph{etc.\/}}
+\def\etal{\emph{et al.\/}}
 
@@
 
-\subsection{Melody Extraction}
-\subsubsection{Task definition}
-Melody extraction algorithms aim to produce a sequence of frequency values
-corresponding to the pitch of the dominant melody from a musical recording
-\cite{salamon:MelodyReview:IEEESPM13}. The estimated pitch is represented as a
-time series of fundamental frequency ($f_0$) values in Hz sampled on a fixed
-time grid (e.g.~every 10 ms). To evaluate the estimated sequence, a reference
-sequence is generated by running a pitch tracker on the monophonic melody track
-(requiring access to the multi-track recording session) and manually correcting
-any mistakes made by the pitch tracker. The estimate is then evaluated against
-the reference by comparing the two frequency sequences on a frame-by-frame
-basis, and computing five global measures, first used in the MIREX 2005 AME
-evaluation \cite{polinerMelodyEval}. The goal of these measures, defined below,
-is to assess the algorithm's performance on two subtasks of melody extraction:
-(1) pitch estimation, i.e.~how well the algorithm estimates the pitch of the
-melody, and (2) voicing detection, i.e.~how well the algorithm determines when
-the melody is present in a frame (a \textit{voiced} frame) or absent (an
-\textit{unvoiced} frame). To allow evaluation of these two subtasks
-independently, a melody extraction algorithm can provide a frequency estimate
-even for frames it has determined to be unvoiced.
+\subsection{Segmentation}
 
-\subsubsection{Evaluation measures}
-The following definitions are taken from
-\cite{salamon:MelodyReview:IEEESPM13} with permission from the authors. Let the estimated melody pitch frequency
-vector be $\mathbf{f}$, and the true sequence (reference) be $\mathbf{f}^*$. Let
-us also define a voicing indicator vector $\mathbf{v}$, whose $\tau^\text{th}$
-element $v_\tau = 1$ when a melody pitch is detected, with corresponding ground
-truth $\mathbf{v}^*$.  We also define an ``unvoicing'' indicator $\bar{v}_\tau =
-1 - v_\tau$.  Recall that an algorithm may report an estimated melody pitch
-($f_\tau > 0$) even for times where it reports no voicing ($v_\tau = 0$).   
-Then the measures are:
-\begin{itemize}
-  \item \textbf{Voicing Recall Rate}: The proportion of frames labeled as
-  melody frames in the reference that are estimated as melody frames by the
-  algorithm.
-\begin{equation}
-\text{Rec}_\text{vx} = \frac{\sum_\tau v_\tau v^*_\tau}{\sum_\tau v^*_\tau}
-\end{equation}
+Music segmentation evaluation metrics can be grouped into two main categories: boundary annotation, and structural annotation.
+In the former, the task is to accurately predict the times of boundaries between adjacent segments (\eg, where a \emph{verse} transitions to a \emph{chorus}).
+Structural annotation metrics are primarily concerned with the labeling task: correctly identifying multiple segments as belonging to the same or different classes.
 
-  \item \textbf{Voicing False Alarm Rate}: The proportion of frames
-  labeled as non-melody in the reference that are mistakenly estimated as
-  melody frames by the algorithm.
-\begin{equation}
-\text{FA}_\text{vx} = \frac{\sum_\tau v_\tau \bar{v}^*_\tau}{\sum_\tau \bar{v}^*_\tau}
-\end{equation}
+In both tasks, we assume that annotations take the form of a partitioning of the track 
+into intervals ${(s_i, t_i)}_{i=1}^m$, where $s_0=0$ denotes the beginning of track, 
+$t_m$ denotes the end of the track, and $t_i = s_{i+1}$.
+Structural annotation additionally requires that each interval be assigned a string
+descriptor.
 
-  \item \textbf{Raw Pitch Accuracy}: The proportion of melody frames in the
-  reference for which $f_\tau$ is considered
-  correct (i.e.~within half a semitone of the ground
-  truth $f^*_\tau$).
-\begin{equation}
-\text{Acc}_\text{pitch}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] }{\sum_\tau v^*_\tau}
-\end{equation}
-where $\mathcal{T}$ is a threshold function defined by:
-\begin{equation}
-\mathcal{T}[a] = \begin{cases}
-1 \quad \text{if } |a| < 0.5 \\
-0 \quad \text{if } |a| \ge 0.5
-\end{cases}
-\end{equation}
-and $\mathcal{M}$ maps a frequency in Hertz to a melodic 
-axis as a real-valued number of semitones above an arbitrary
-reference frequency $f_\text{ref}$:
-\begin{equation}
-\mathcal{M}(f) = 12 \log_2\left( \frac{f}{f_\text{ref}} \right)
-\end{equation}
+\subsubsection{Boundary annotation}
 
-  \item \textbf{Raw Chroma Accuracy}: As raw pitch accuracy, except
-  that both the estimated and reference $f_0$ sequences are mapped onto a
-  single octave. This gives a measure of pitch accuracy which ignores octave
-  errors, a common error made by melody extraction systems:
-\begin{equation}
-\text{Acc}_\text{chroma}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\left<\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau)\right>_{12} \right] }{\sum_\tau v^*_\tau}
-\end{equation}
-Octave equivalence is achieved by taking the difference between the semitone-scale pitch 
-values modulo 12 (one octave), where
-\begin{equation}
-\left<a\right>_{12} = a - 12 \lfloor \frac{a}{12} + 0.5 \rfloor .
-\end{equation}
+Within boundary annotation, there are two categories of evaluation metrics: detection,
+and deviation~\cite{turnbull2007}.
 
-  \item \textbf{Overall Accuracy}: this measure combines the performance of the
-  pitch estimation and voicing detection tasks to give an overall performance
-  score for the system. It is defined as the proportion of all frames
-   correctly estimated by the algorithm, where for non-melody
-  frames this means the algorithm labeled them as non-melody, and for melody
-  frames the algorithm both labeled them as melody frames and provided a correct
-  $f_0$ estimate for the melody (i.e.~within half a semitone of the
-  reference):
+Let $B_R$ ($B_E$) denote the set of unique interval boundary times in the reference 
+(estimated) annotation, and let $W$ denote a tolerance window, typically either $0.5$s
+or $3.0$s.
 
-\begin{equation}
-\text{Acc}_\text{ov} 
-= \frac{1}{L} \sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] + \bar{v}^*_\tau \bar{v}_\tau 
-\end{equation}
-where $L$ is the total number of frames.
-\end{itemize}
+\subsubsection{Structural annotation}
 
-The performance of an algorithm on an entire music collection for a given
-measure is obtained by averaging the per-excerpt scores for that measure over
-all excerpts in the collection.
+\section{Footnotes and Figures}
 
-\subsubsection{Discussion}
+\subsection{Footnotes}
 
-% \subsection{Figures, Tables and Captions}
-% 
-% All artwork must be centered, neat, clean, and legible.
-% All lines should be very dark for purposes of reproduction and art work should not be hand-drawn.
-% The proceedings are not in color, and therefore all figures must make sense in black-and-white form.
-% Figure and table numbers and captions always appear below the figure.
-% Leave 1 line space between the figure or table and the caption.
-% Each figure or table is numbered consecutively. Captions should be Times 10pt.
-% Place tables/figures in text as close to the reference as possible.
-% References to tables and figures should be capitalized, for example:
-% see \figref{fig:example} and \tabref{tab:example}.
-% Figures and tables may extend across both columns to a maximum width of 17.2cm.
+Indicate footnotes with a number in the text.\footnote{This is a footnote.}
+Use 8pt type for footnotes. Place the footnotes at the bottom of the page on which they appear.
+Precede the footnote with a 0.5pt horizontal rule.
 
-% \begin{table}
-%  \begin{center}
-%  \begin{tabular}{|l|l|}
-%   \hline
-%   String value & Numeric value \\
-%   \hline
-%   Hello ISMIR  & 2014 \\
-%   \hline
-%  \end{tabular}
-% \end{center}
-%  \caption{Table captions should be placed below the table.}
-%  \label{tab:example}
-% \end{table}
+\subsection{Figures, Tables and Captions}
+
+All artwork must be centered, neat, clean, and legible.
+All lines should be very dark for purposes of reproduction and art work should not be hand-drawn.
+The proceedings are not in color, and therefore all figures must make sense in black-and-white form.
+Figure and table numbers and captions always appear below the figure.
+Leave 1 line space between the figure or table and the caption.
+Each figure or table is numbered consecutively. Captions should be Times 10pt.
+Place tables/figures in text as close to the reference as possible.
+References to tables and figures should be capitalized, for example:
+see \figref{fig:example} and \tabref{tab:example}.
+Figures and tables may extend across both columns to a maximum width of 17.2cm.
+
+\begin{table}
+ \begin{center}
+ \begin{tabular}{|l|l|}
+  \hline
+  String value & Numeric value \\
+  \hline
+  Hello ISMIR  & 2014 \\
+  \hline
+ \end{tabular}
+\end{center}
+ \caption{Table captions should be placed below the table.}
+ \label{tab:example}
+\end{table}
 
@@
 
-% \begin{thebibliography}{citations}
-% 
-% \bibitem {Author:00}
-% E. Author:
-% ``The Title of the Conference Paper,''
-% {\it Proceedings of the International Symposium
-% on Music Information Retrieval}, pp.~000--111, 2000.
-% 
-% \bibitem{Someone:10}
-% A. Someone, B. Someone, and C. Someone:
-% ``The Title of the Journal Paper,''
-% {\it Journal of New Music Research},
-% Vol.~A, No.~B, pp.~111--222, 2010.
-% 
-% \bibitem{Someone:04} X. Someone and Y. Someone: {\it Title of the Book},
-%     Editorial Acme, Porto, 2012.
-% 
-% \end{thebibliography}
+\section{Equations}
 
-\bibliography{mir_eval}
+Equations should be placed on separated lines and numbered.
+The number should be on the right side, in parentheses.
+
+\begin{equation}
+E=mc^{2}
+\end{equation}
+
+\section{Citations}
+
+All bibliographical references should be listed at the end,
+inside a section named ``REFERENCES,'' numbered and in alphabetical order.
+Also, all references listed should be cited in the text.
+When referring to a document, type the numbering square brackets
+\cite{Author:00} or \cite{Author:00,Someone:10,Someone:04}.
+
+\begin{thebibliography}{citations}
+
+\bibitem {Author:00}
+E. Author:
+``The Title of the Conference Paper,''
+{\it Proceedings of the International Symposium
+on Music Information Retrieval}, pp.~000--111, 2000.
+
+\bibitem{Someone:10}
+A. Someone, B. Someone, and C. Someone:
+``The Title of the Journal Paper,''
+{\it Journal of New Music Research},
+Vol.~A, No.~B, pp.~111--222, 2010.
+
+\bibitem{Someone:04} X. Someone and Y. Someone: {\it Title of the Book},
+    Editorial Acme, Porto, 2012.
+
+\end{thebibliography}
+
+%\bibliography{ismir2014template}
 

### 2014-04-28 paper/paper.tex
added boundary detection section

--- 2014-04-27 paper/paper.tex
@@
 \usepackage{graphicx}
+
+\def\eg{\emph{e.g.\/}}
+\def\ie{\emph{i.e.\/}}
+\def\etc{\emph{etc.\/}}
+\def\etal{\emph{et al.\/}}
+\DeclareMathOperator*{\median}{median}
 
@@
 \end{equation}
+
+\subsection{Segmentation}
+
+Evaluation criteria for segmentation fall into two categories: boundary annotation, and structural annotation.
+\emph{Boundary annotation} is the task of predicting the times at which structural changes occur, such as when a \emph{verse} transitions to a \emph{refrain}.
+\emph{Structural annotation} is the task of assigning labels to detected segments.  
+The estimated labels may be arbitrary strings --- such as $A$, $B$, $C$, \etc{} --- and they need not describe functional concepts.
+
+In both tasks, we assume that annotations take the form of a partitioning of the track 
+into intervals ${(s_i, t_i)}_{i=1}^m$, where $s_0=0$ denotes the beginning of track, 
+$t_m$ denotes the end of the track, and $t_i = s_{i+1}$.
+Structural annotation additionally requires that each interval be assigned a label $y_i$.
+
+\subsubsection{Boundary annotation}
+
+Within boundary annotation, there are two categories of evaluation metrics: detection,
+and deviation~\cite{turnbull2007supervised}.
+
+\emph{Boundary detection} measures the precision, recall, and f-measure of boundary prediction within a tolerance window.
+Let $B_R$ ($B_E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
+a tolerance window, typically either $0.5$s or $3.0$s.  
+A \emph{hit} is defined as a pair $b_e \in B_E$, $b_r \in B_R$ such that $|b_e - b_r|
+\leq W$.
+
+To define detection metrics, we require that no estimated boundary is counted for more than one reference boundary, and vice versa.
+This is accomplished by computing a maximum bipartite matching $H_W$ between $B_E$ and $B_R$ (subject to the window constraint $W$) using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  
+Precision and recall with window $W$ are defined as
+\begin{align}
+P_W(B_R, B_E) &:= \frac{|H_W|}{|B_E|}\\
+R_W(B_R, B_E) &:= \frac{|H_W|}{|B_R|},
+\end{align}
+and the corresponding f-measure is defined by taking their harmonic mean.
+
+\emph{Boundary deviation} is comprised of two scores, which measure the median time between a reference boundary and its nearest corresponding estimated boundary, and vice versa.
+These two metrics have previously been defined as \emph{true-to-predicted} (T-to-P) and \emph{predicted-to-true} (P-to-T), though in the terminology of this document, we use 
+alternative naming of \emph{reference-to-estimated} (R-to-E) and \emph{estimated-to-reference} (E-to-R):
+\begin{align}
+\text{R-to-E}(B_R, B_E) &:= \displaystyle\median_{b_r \in B_R} \min_{b_e \in B_E} \left|b_r - b_e\right|\\
+\text{E-to-R}(B_R, B_E) &:= \displaystyle\median_{b_e \in B_E} \min_{b_r \in B_R} \left|b_r - b_e\right|.
+\end{align}
+
+\subsubsection{Structural annotation}
 

### 2014-04-28 paper/paper.tex
added boundary detection section
added structure section

@@
 \usepackage{graphicx}
+\usepackage{dsfont}
+\usepackage{stmaryrd}
+\usepackage{braket}
 
@@
 \DeclareMathOperator*{\median}{median}
+\newcommand{\ind}[1]{\ensuremath{\left\llbracket#1\right\rrbracket}}
+\def\given{\ensuremath{|~}}
+\def\defeq{\ensuremath{:=}}
+
+% \newcommand*{\defeq}{\mathrel{\rlap{%
+%                     \raisebox{0.25ex}{$\m@th\cdot$}}%
+%                     \raisebox{-0.25ex}{$\m@th\cdot$}}%
+%                     =}
 
@@
 \emph{Boundary detection} measures the precision, recall, and f-measure of boundary prediction within a tolerance window.
-Let $B_R$ ($B_E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
+Let $B^R$ ($B^E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
 a tolerance window, typically either $0.5$s or $3.0$s.  
-A \emph{hit} is defined as a pair $b_e \in B_E$, $b_r \in B_R$ such that $|b_e - b_r|
+A \emph{hit} is defined as a pair $b_e \in B^E$, $b_r \in B^R$ such that $|b_e - b_r|
 \leq W$.
 
-To define detection metrics, we require that no estimated boundary is counted for more than one reference boundary, and vice versa.
-This is accomplished by computing a maximum bipartite matching $H_W$ between $B_E$ and $B_R$ (subject to the window constraint $W$) using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  
+No estimated boundary is counted as a hit for more than one reference boundary, and vice versa.
+This is accomplished by computing a maximum bipartite matching $H_W$ between $B^E$ and $B^R$ (subject to the window constraint $W$) using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  
 Precision and recall with window $W$ are defined as
 \begin{align}
-P_W(B_R, B_E) &:= \frac{|H_W|}{|B_E|}\\
-R_W(B_R, B_E) &:= \frac{|H_W|}{|B_R|},
+P_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^E|}\\
+R_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^R|},
 \end{align}
@@
 \begin{align}
-\text{R-to-E}(B_R, B_E) &:= \displaystyle\median_{b_r \in B_R} \min_{b_e \in B_E} \left|b_r - b_e\right|\\
-\text{E-to-R}(B_R, B_E) &:= \displaystyle\median_{b_e \in B_E} \min_{b_r \in B_R} \left|b_r - b_e\right|.
+\text{R-to-E}(B^R, B^E) &\defeq \displaystyle\median_{b_r \in B^R} \min_{b_e \in B^E} \left|b_r - b_e\right|\\
+\text{E-to-R}(B^R, B^E) &\defeq \displaystyle\median_{b_e \in B^E} \min_{b_r \in B^R} \left|b_r - b_e\right|.
 \end{align}
@@
 \subsubsection{Structural annotation}
+Two standard methods of evaluating structural annotation accuracy are \emph{pairwise classification}~\cite{levy2008structural}
+and conditional entropy~\cite{lukashevich2008towards}.  In both methods, a collection of samples are generated by sampling the
+labels at time steps between $0$ and the track duration.  Each sample $x_i$ is assigned a reference label $y_i^R$ and
+and estimated label $y_i^E$.  Our implementation follows the MIREX guidelines, and generates samples at a default rate of 10Hz.
+
+In order for annotation metrics to be well-defined, both reference and estimated annotations must span the same duration of time.
+This is accomplished in our implementation by trimming or padding the estimated annotation to exactly match the start and end-times
+reported in the reference annotation, and synthesizing unique reference labels if necessary.  Note that the reference annotation is
+never modified, only the estimated annotations: in this way, comparison of multiple estimations cannot be compromised by an
+estimator reporting an incorrect track duration.
+
+Given the labels for the samples $\{(y_i^R, y_i^E)\}_{i=1}^n$, the \emph{pairwise classification} metrics are defined as precision,
+recall, and f-measure of label agreement over all unique, distinct pairs $i \neq j$.  
+Let $A_R = \{ \{i, j\} \given y_i^R = y_j^R\}$ denote the set of similarly labeled frames in the reference, with $A_E$ defined
+analogously for the estimation.  Then the precision and recall are defined simply as
+\begin{align}
+P_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_E| }\\
+R_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_R| }.
+\end{align}
+
+\emph{Normalized conditional entropy} scores are computed by estimating the conditional entropy of the estimated label $y^E$ given
+the reference label $y^R$ and vice versa.  Let $P$ denote the empirical joint distribution over reference and estimated labels:
+\begin{align}
+P_{ij} &\propto \left|\{t \given y_t^R = i \wedge y_t^E = j\}\right|.
+\end{align}
+Then the conditional entropies $H(E \given R)$ and $H(R \given E)$ (in bits) are derived from the 
+marginals ${p_i^R = \sum_j P_{ij}}$ and ${p_j^E = \sum_i P_{ij}}$ as described by Lukashevich~\cite{lukashevich2008towards}.
+
+The final scores are defined as \emph{over-segmentation} ($S_\text{O}$)
+and \emph{under-segmentation} ($S_\text{U}$):
+\begin{align}
+S_\text{O} &\defeq 1 - \frac{H(E \given R)}{\log_2 |\ell^E|}\\
+S_\text{U} &\defeq 1 - \frac{H(R \given E)}{\log_2 |\ell^R|},
+\end{align}
+where $\ell^R$ and $\ell^E$ denote the sets of unique label values given in the reference and estimation.
 

### 2014-04-28 paper/paper.tex
revision to text

@@
 
-In both tasks, we assume that annotations take the form of a partitioning of the track 
+In both tasks, we assume that annotations express a partitioning of the track 
 into intervals ${(s_i, t_i)}_{i=1}^m$, where $s_0=0$ denotes the beginning of track, 
@@
 
-\emph{Boundary detection} measures the precision, recall, and f-measure of boundary prediction within a tolerance window.
+\emph{Boundary detection} measures the precision, recall, and F-measure of boundary prediction within a window.
 Let $B^R$ ($B^E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
-a tolerance window, typically either $0.5$s or $3.0$s.  
+a window, typically either $0.5$s or $3.0$s.  
 A \emph{hit} is defined as a pair $b_e \in B^E$, $b_r \in B^R$ such that $|b_e - b_r|
@@
 No estimated boundary is counted as a hit for more than one reference boundary, and vice versa.
-This is accomplished by computing a maximum bipartite matching $H_W$ between $B^E$ and $B^R$ (subject to the window constraint $W$) using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  
-Precision and recall with window $W$ are defined as
+This is accomplished by computing a maximum bipartite matching $H_W$ between $B^E$ and $B^R$ (subject to the window constraint $W$)
+using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  This deviates from the greedy heuristic used in the MIREX
+implementation, but it is guaranteed to produce a correct matching.  Precision and recall at window $W$ are defined as
 \begin{align}
@@
 \end{align}
-and the corresponding f-measure is defined by taking their harmonic mean.
+and the corresponding F-measure is defined by taking their harmonic mean.
 
@@
 and conditional entropy~\cite{lukashevich2008towards}.  In both methods, a collection of samples are generated by sampling the
-labels at time steps between $0$ and the track duration.  Each sample $x_i$ is assigned a reference label $y_i^R$ and
+labels at time steps between $0$ and the track duration.  The $i$th sample is assigned a reference label $y_i^R$ and
 and estimated label $y_i^E$.  Our implementation follows the MIREX guidelines, and generates samples at a default rate of 10Hz.
 
-In order for annotation metrics to be well-defined, both reference and estimated annotations must span the same duration of time.
+Reference and estimated annotations must span identical time durations for annotation metrics to be well-defined.
 This is accomplished in our implementation by trimming or padding the estimated annotation to exactly match the start and end-times
-reported in the reference annotation, and synthesizing unique reference labels if necessary.  Note that the reference annotation is
-never modified, only the estimated annotations: in this way, comparison of multiple estimations cannot be compromised by an
-estimator reporting an incorrect track duration.
+reported in the reference annotation, and synthesizing unique labels if necessary.
 
 Given the labels for the samples $\{(y_i^R, y_i^E)\}_{i=1}^n$, the \emph{pairwise classification} metrics are defined as precision,
-recall, and f-measure of label agreement over all unique, distinct pairs $i \neq j$.  
+recall, and F-measure of label agreement over all unique, distinct pairs $i \neq j$.  
 Let $A_R = \{ \{i, j\} \given y_i^R = y_j^R\}$ denote the set of similarly labeled frames in the reference, with $A_E$ defined
-analogously for the estimation.  Then the precision and recall are defined simply as
+analogously for the estimation.  Precision and recall are defined as
 \begin{align}
@@
 \end{align}
-Then the conditional entropies $H(E \given R)$ and $H(R \given E)$ (in bits) are derived from the 
-marginals ${p_i^R = \sum_j P_{ij}}$ and ${p_j^E = \sum_i P_{ij}}$ as described by Lukashevich~\cite{lukashevich2008towards}.
+Let $Y^R$ and $Y^E$ denote random variables corresponding to the reference and estimated label for an arbitrary sample.
+The conditional entropies $H\left(Y^E \given Y^R\right)$ and $H\left(Y^R \given Y^E\right)$ are estimated from the 
+empirical marginals ${p_i^R = \sum_j P_{ij}}$ and ${p_j^E = \sum_i P_{ij}}$ as described by 
+Lukashevich~\cite{lukashevich2008towards}.
 
-The final scores are defined as \emph{over-segmentation} ($S_\text{O}$)
-and \emph{under-segmentation} ($S_\text{U}$):
+The final scores are defined as \emph{over-segmentation} ($S_\text{O}$) and \emph{under-segmentation} ($S_\text{U}$):
 \begin{align}

### 2014-04-29 code/beat/beat.py
Beat experiment #2

@@ -1,0 +1,126 @@
+# -*- coding: utf-8 -*-
+# <nbformat>3.0</nbformat>
+
+# <codecell>
+
+'''
+Compare mir_eval against MIREX 2012 beat results
+'''
+
+# <codecell>
+
+import glob
+import os
+import csv
+import mir_eval
+import shutil
+import joblib
+
+# <codecell>
+
+BASE_DATA_PATH = '../../data/beat/'
+METRIC_KEYS = ['F-Measure', 'Cemgil', 'Goto', 'McKinney P-score', 'CMLc', 'CMLt', 'AMLc', 'AMLt', 'D (bits)']
+
+# <codecell>
+
+# A typical row in a MIREX results .csv looks like:
+#0,smc_001,14.2860,13.9210,0.0000,35.7140,0.0000,0.0000,0.0000,0.0000,1.0967
+# Where the order of the metrics is
+# F-Measure,Cemgil,Goto,McKinney P-score,CMLc,CMLt,AMLc,AMLt,D (bits)
+# The first column is "fold", which is not useful for us.
+# The second column is the file, but it's not the filename.
+# So, remove the first column and make the second look like the filename
+for filename in glob.glob(os.path.join(BASE_DATA_PATH, '*', 'raw_scores', '*.csv')):
+    output_list = []
+    with open(filename, 'r') as f:
+        csv_reader = csv.reader(f)
+        for row in csv_reader:
+            # Skip the label row
+            if row[0] != '*Fold':
+                # Construct the filename/output path
+                output_filename = 'transcription' + row[1].replace('_', '') + '.txt'
+                output_path = filename.replace('mirex_scores_raw', 'mirex_scores')
+                output_path = os.path.join(os.path.split(output_path)[0], os.path.split(output_path)[1].replace('.csv', ''))
+                # Make sure output dir exists
+                try:
+                    os.makedirs(output_path)
+                except OSError:
+                    pass
+                np.savetxt(os.path.join(output_path, output_filename), [float(x) for x in row[2:]])
+
+# <codecell>
+
+def get_mir_eval_scores(reference_beats, estimated_beats):
+    ''' Computes all mir_eval metrics and returns them in a list with the order
+    F-Measure,Cemgil,Goto,McKinney P-score,CMLc,CMLt,AMLc,AMLt,D (bits)
+    '''
+    scores = []
+    for metric_name in ['F-measure', 'Cemgil', 'Goto', 'P-score', 'Continuity', 'Information Gain']:
+        
[…]

### 2014-04-29 code/convert_json_labels_to_lab.py
From jpauwels

@@ -1,0 +1,95 @@
+#!/usr/bin/env python
+
+# Script to convert a directory of js-files coming from NEMA to the corresponding 
+# lab-files. It should be called from the command line with the following parameters:
+# 
+# <list>		a plain text file containing the base names (without extension)
+# 				of the files to convert, separated by newlines
+# <js_dir>		the directory with the js-files
+# <lab_dir>		the directory in which the resulting lab-files should be saved
+# 
+# Author: Johan Pauwels (johan.pauwels@gmail.com)
+# Last changed: 2010-08-08
+# License: GPL
+# 
+# Made for Python 2.6
+
+import json
+import re
+import os
+import sys
+import os.path
+
+def convert_json_file_to_lab_files(base_name, js_dir, lab_dir):
+	"""Convert NEMA js-file to lab-files
+
+	Converts the file <base_name>.js located in <js_dir> to a set of
+	lab-files in <lab_dir>. For each of the data series present in 
+	the js-file, a subdirectory will be created. The resulting lab-files
+	are thus written to <lab_dir>/<series_name>/<base_name>.lab, 
+	e.g. /path/to/lab_dir/Ground-truth/chordschordmrx09000000.lab
+
+	"""
+
+	# Read js-file and store into single-line string
+	js_path = os.path.join(js_dir, base_name+'.js')
+	with open(js_path) as js_file:
+		js_content = js_file.read()
+		js_content = js_content.replace('\n','')
+		
+		# Use regexp to isolate json
+		data_exp = re.compile('var .*_data = ([^;]*);')
+		names_exp = re.compile('var .*_seriesNames = ([^;]*);')
+		data_match = data_exp.search(js_content)
+		names_match = names_exp.search(js_content)
+		names = names_match.group(1)
+		data = data_match.group(1)
+		
+		# Convert into proper json by quoting strings
+		data = data.replace('o:','"o":')
+		data = data.replace('f:','"f":')
+		data = data.replace('l:','"l":')
+		data = data.replace('a:','"a":')
+		
+		# Replace problematic labels
+		data = data.replace('\t','    ')
+		data = data.replace('\\','\\\\')
+		
+		# Parse json
+		n = json.loads(names)
+		d = json.loads(data)
+		
+		# Write lab file for each series
+		for j in range(len(n)):
[…]

### 2014-04-29 paper/paper.tex
Working on paper

--- 2014-04-28 paper/paper.tex
@@
 \usepackage{graphicx}
-
-\def\eg{\emph{e.g.\/}}
-\def\ie{\emph{i.e.\/}}
-\def\etc{\emph{etc.\/}}
-\def\etal{\emph{et al.\/}}
-\DeclareMathOperator*{\median}{median}
 
@@
 
-\subsection{Segmentation}
+\subsection{Pattern Discovery}
 
-Evaluation criteria for segmentation fall into two categories: boundary annotation, and structural annotation.
-\emph{Boundary annotation} is the task of predicting the times at which structural changes occur, such as when a \emph{verse} transitions to a \emph{refrain}.
-\emph{Structural annotation} is the task of assigning labels to detected segments.  
-The estimated labels may be arbitrary strings --- such as $A$, $B$, $C$, \etc{} --- and they need not describe functional concepts.
+This recent MIREX task aims to evaluate algorithms that identify musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
+Given the novelty of this task, the metrics used in 2013 (the first year to appear on MIREX) are subject to modifications in further editions.
+However, Colins\cite{TomColins2013} put together all the previously existent metrics and a few new ones for this task in its first appearance in MIREX, which resulted in 21 different scores, each one implemented in MIR-eval.
 
-In both tasks, we assume that annotations take the form of a partitioning of the track 
-into intervals ${(s_i, t_i)}_{i=1}^m$, where $s_0=0$ denotes the beginning of track, 
-$t_m$ denotes the end of the track, and $t_i = s_{i+1}$.
-Structural annotation additionally requires that each interval be assigned a label $y_i$.
+\subsubsection{Third and Further Level Headings}
 
-\subsubsection{Boundary annotation}
+Third level headings are in Times 10pt italic, flush left,
+with 1/2 line of space above the section head, and 1/2 space below it.
+The first letter of each significant word is capitalized.
 
-Within boundary annotation, there are two categories of evaluation metrics: detection,
-and deviation~\cite{turnbull2007supervised}.
+Using more than three levels of headings is highly discouraged.
 
-\emph{Boundary detection} measures the precision, recall, and f-measure of boundary prediction within a tolerance window.
-Let $B_R$ ($B_E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
-a tolerance window, typically either $0.5$s or $3.0$s.  
-A \emph{hit} is defined as a pair $b_e \in B_E$, $b_r \in B_R$ such that $|b_e - b_r|
-\leq W$.
+\section{Footnotes and Figures}
 
-To define detection metrics, we require that no estimated boundary is counted for more than one reference boundary, and vice versa.
-This is accomplished by computing a maximum bipartite matching $H_W$ between $B_E$ and $B_R$ (subject to the window constraint $W$) using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  
-Precision and recall with window $W$ are defined as
-\begin{align}
-P_W(B_R, B_E) &:= \frac{|H_W|}{|B_E|}\\
-R_W(B_R, B_E) &:= \frac{|H_W|}{|B_R|},
-\end{align}
-and the corresponding f-measure is defined by taking their harmonic mean.
+\subsection{Footnotes}
 
-\emph{Boundary deviation} is comprised of two scores, which measure the median time between a reference boundary and its nearest corresponding estimated boundary, and vice versa.
-These two metrics have previously been defined as \emph{true-to-predicted} (T-to-P) and \emph{predicted-to-true} (P-to-T), though in the terminology of this document, we use 
-alternative naming of \emph{reference-to-estimated} (R-to-E) and \emph{estimated-to-reference} (E-to-R):
-\begin{align}
-\text{R-to-E}(B_R, B_E) &:= \displaystyle\median_{b_r \in B_R} \min_{b_e \in B_E} \left|b_r - b_e\right|\\
-\text{E-to-R}(B_R, B_E) &:= \displaystyle\median_{b_e \in B_E} \min_{b_r \in B_R} \left|b_r - b_e\right|.
-\end{align}
+Indicate footnotes with a number in the text.\footnote{This is a footnote.}
+Use 8pt type for footnotes. Place the footnotes at the bottom of the page on which they appear.
+Precede the footnote with a 0.5pt horizontal rule.
 
-\subsubsection{Structural annotation}
+\subsection{Figures, Tables and Captions}
 
-\subsection{Melody Extraction}
-\subsubsection{Task definition}
-Melody extraction algorithms aim to produce a sequence of frequency values
-corresponding to the pitch of the dominant melody from a musical recording
-\cite{salamon:MelodyReview:IEEESPM13}. The estimated pitch is represented as a
-time series of fundamental frequency ($f_0$) values in Hz sampled on a fixed
-time grid (e.g.~every 10 ms). To evaluate the estimated sequence, a reference
-sequence is generated by running a pitch tracker on the monophonic melody track
-(requiring access to the multi-track recording session) and manually correcting
-any mistakes made by the pitch tracker. The estimate is then evaluated against
-the reference by comparing the two frequency sequences on a frame-by-frame
-basis, and computing five global measures, first used in the MIREX 2005 AME
-evaluation \cite{polinerMelodyEval}. The goal of these measures, defined below,
-is to assess the algorithm's performance on two subtasks of melody extraction:
-(1) pitch estimation, i.e.~how well the algorithm estimates the pitch of the
-melody, and (2) voicing detection, i.e.~how well the algorithm determines when
-the melody is present in a frame (a \textit{voiced} frame) or absent (an
-\textit{unvoiced} frame). To allow evaluation of these two subtasks
-independently, a melody extraction algorithm can provide a frequency estimate
-even for frames it has determined to be unvoiced.
+All artwork must be centered, neat, clean, and legible.
+All lines should be very dark for purposes of reproduction and art work should not be hand-drawn.
+The proceedings are not in color, and therefore all figures must make sense in black-and-white form.
+Figure and table numbers and captions always appear below the figure.
+Leave 1 line space between the figure or table and the caption.
+Each figure or table is numbered consecutively. Captions should be Times 10pt.
+Place tables/figures in text as close to the reference as possible.
+References to tables and figures should be capitalized, for example:
+see \figref{fig:example} and \tabref{tab:example}.
+Figures and tables may extend across both columns to a maximum width of 17.2cm.
 
-\subsubsection{Evaluation measures}
-The following definitions are taken from
-\cite{salamon:MelodyReview:IEEESPM13} with permission from the authors. Let the estimated melody pitch frequency
-vector be $\mathbf{f}$, and the true sequence (reference) be $\mathbf{f}^*$. Let
-us also define a voicing indicator vector $\mathbf{v}$, whose $\tau^\text{th}$
-element $v_\tau = 1$ when a melody pitch is detected, with corresponding ground
-truth $\mathbf{v}^*$.  We also define an ``unvoicing'' indicator $\bar{v}_\tau =
-1 - v_\tau$.  Recall that an algorithm may report an estimated melody pitch
-($f_\tau > 0$) even for times where it reports no voicing ($v_\tau = 0$).   
-Then the measures are:
-\begin{itemize}
-  \item \textbf{Voicing Recall Rate}: The proportion of frames labeled as
-  melody frames in the reference that are estimated as melody frames by the
-  algorithm.
-\begin{equation}
-\text{Rec}_\text{vx} = \frac{\sum_\tau v_\tau v^*_\tau}{\sum_\tau v^*_\tau}
-\end{equation}
-
-  \item \textbf{Voicing False Alarm Rate}: The proportion of frames
-  labeled as non-melody in the reference that are mistakenly estimated as
-  melody frames by the algorithm.
-\begin{equation}
-\text{FA}_\text{vx} = \frac{\sum_\tau v_\tau \bar{v}^*_\tau}{\sum_\tau \bar{v}^*_\tau}
-\end{equation}
-
-  \item \textbf{Raw Pitch Accuracy}: The proportion of melody frames in the
-  reference for which $f_\tau$ is considered
-  correct (i.e.~within half a semitone of the ground
-  truth $f^*_\tau$).
-\begin{equation}
-\text{Acc}_\text{pitch}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] }{\sum_\tau v^*_\tau}
-\end{equation}
-where $\mathcal{T}$ is a threshold function defined by:
-\begin{equation}
-\mathcal{T}[a] = \begin{cases}
-1 \quad \text{if } |a| < 0.5 \\
-0 \quad \text{if } |a| \ge 0.5
-\end{cases}
-\end{equation}
-and $\mathcal{M}$ maps a frequency in Hertz to a melodic 
-axis as a real-valued number of semitones above an arbitrary
-reference frequency $f_\text{ref}$:
-\begin{equation}
-\mathcal{M}(f) = 12 \log_2\left( \frac{f}{f_\text{ref}} \right)
-\end{equation}
-
-  \item \textbf{Raw Chroma Accuracy}: As raw pitch accuracy, except
-  that both the estimated and reference $f_0$ sequences are mapped onto a
-  single octave. This gives a measure of pitch accuracy which ignores octave
-  errors, a common error made by melody extraction systems:
-\begin{equation}
-\text{Acc}_\text{chroma}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\left<\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau)\right>_{12} \right] }{\sum_\tau v^*_\tau}
-\end{equation}
-Octave equivalence is achieved by taking the difference between the semitone-scale pitch 
-values modulo 12 (one octave), where
-\begin{equation}
-\left<a\right>_{12} = a - 12 \lfloor \frac{a}{12} + 0.5 \rfloor .
-\end{equation}
-
-  \item \textbf{Overall Accuracy}: this measure combines the performance of the
-  pitch estimation and voicing detection tasks to give an overall performance
-  score for the system. It is defined as the proportion of all frames
-   correctly estimated by the algorithm, where for non-melody
-  frames this means the algorithm labeled them as non-melody, and for melody
-  frames the algorithm both labeled them as melody frames and provided a correct
-  $f_0$ estimate for the melody (i.e.~within half a semitone of the
-  reference):
-
-\begin{equation}
-\text{Acc}_\text{ov} 
-= \frac{1}{L} \sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] + \bar{v}^*_\tau \bar{v}_\tau 
-\end{equation}
-where $L$ is the total number of frames.
-\end{itemize}
-
-The performance of an algorithm on an entire music collection for a given
-measure is obtained by averaging the per-excerpt scores for that measure over
-all excerpts in the collection.
-
-\subsubsection{Discussion}
-
-In the measure definitions provided above, it is assumed that both the estimate
-and reference sequences are sampled using the same time grid (hop size). In
-practice, however, this is not always the case, since the time grid of the
-reference depends on the hop size used by the pitch tracker that produced
-it, and similarly the time grid of the estimate depends on the specific melody
-extraction algorithm that produced it. This means that the sequences must be
-resampled onto a common time-grid prior to the computation of the measures. For
-the MIREX AME task, any sequence (be it reference or estimate) that is not
-sampled using a 10 ms hop size is resampled using $0^{th}$-order interpolation,
-i.e.~each frequency value in the target sequence is set to its nearest
-neighbour (in time) from the source sequence. This kind of interpolation can
-potentially have a detrimental effect on the evaluation, depending on the
-difference between the source and target time grids. In particular, it can
-result in artificially low scores for sequences with rapidly changing pitch
-values, such as opera singing with deep vibrato.
-
-For this reason, the melody evaluator in mir\_eval uses $1^{st}$-order (linear)
-interpolation by default in order to map the reference and estimate sequences
-onto a common time-grid. Assuming the original timestamps of both sequences
-correspond to the \textit{center} of each analysis frame (as they should),
-using $1^{st}$-order rather than $0^{th}$-order interpolation means the results
-returned by mir\_eval are lower-bounded by the MIREX results and are, in our
-view, more accurate.
-
-% \subsection{Figures, Tables and Captions}
-% 
-% All artwork must be centered, neat, clean, and legible.
-% All lines should be very dark for purposes of reproduction and art work should not be hand-drawn.
-% The proceedings are not in color, and therefore all figures must make sense in black-and-white form.
-% Figure and table numbers and captions always appear below the figure.
-% Leave 1 line space between the figure or table and the caption.
-% Each figure or table is numbered consecutively. Captions should be Times 10pt.
-% Place tables/figures in text as close to the reference as possible.
-% References to tables and figures should be capitalized, for example:
-% see \figref{fig:example} and \tabref{tab:example}.
-% Figures and tables may extend across both columns to a maximum width of 17.2cm.
-
-% \begin{table}
-%  \begin{center}
-%  \begin{tabular}{|l|l|}
-%   \hline
-%   String value & Numeric value \\
-%   \hline
-%   Hello ISMIR  & 2014 \\
-%   \hline
-%  \end{tabular}
-% \end{center}
-%  \caption{Table captions should be placed below the table.}
-%  \label{tab:example}
-% \end{table}
+\begin{table}
+ \begin{center}
+ \begin{tabular}{|l|l|}
+  \hline
+  String value & Numeric value \\
+  \hline
+  Hello ISMIR  & 2014 \\
+  \hline
+ \end{tabular}
+\end{center}
+ \caption{Table captions should be placed below the table.}
+ \label{tab:example}
+\end{table}
 

### 2014-04-29 paper/paper.tex

--- 2014-04-28 paper/paper.tex
@@
 \end{equation}
+
+\subsection{Pattern Discovery}
+
+This recent MIREX task aims to evaluate algorithms that identify musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
+Given the novelty of this task, the metrics used in 2013 (the first year to appear on MIREX) are subject to modifications in further editions.
+However, Colins\cite{TomColins2013} put together all the previously existent metrics and a few new ones for this task in its first appearance in MIREX, which resulted in 21 different scores, each one implemented in MIR-eval.
 
@@
 
+\subsection{Blind Source Separation}
+
 % \subsection{Figures, Tables and Captions}

### 2014-04-29 paper/paper.tex
Pattern discovery description added

--- 2014-04-28 paper/paper.tex
@@
 \end{equation}
+
+\subsection{Pattern Discovery}
+
+This task aims to evaluate algorithms that identify musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
+Given the novelty of this task \footnote{The first year to appear on MIREX was 2013.}, the evaluation metrics are likely to be modified in further editions.
+Nonetheless, Collins put together all the previously existent metrics and a few new ones for this task in its first appearance in MIREX\cite{Collins2013}, which resulted in 19 different scores, each one (except for the two that evaluate the algorithm execution time) implemented in MIR-eval and described below:
+
+\begin{itemize}
+    \item
+      \textbf{Standard F-measure, Precision, and Recall (F$_1$, P, R)}: This metric, composed of three scores, checks if the prototype patterns of the reference match possible key-transposed patterns in the prototype patterns of the estimations.
+      Since the sizes of these prototypes must be equal, this metric is quite restrictive and it tends to be 0 most of the time (see 2013 MIREX results).
+    \item
+      \textbf{Establishment F-measure, Precision, and Recall (F1$_{est}$, P$_{est}$, R$_{est}$)}: These scores evaluate the amount of patterns that were successfully identified by the estimated results, no matter how many occurrences they found.
+      In other words, this metric captures the ability of the algorithm to \textit{establish} that the estimated patterns are actually contained in the reference annotation.
+    \item 
+      \textbf{Occurrence F-measure, Precision, and Recall (F1$_{occ}$, P$_{occ}$, R$_{occ}$)}: Independently of how many patterns were correctly established, we may also want to know how well the algorithm finds all their respective occurrences throughout the piece.
+      This metric aims to quantize this \textit{occurrence} retrieval quality of the algorithm.
+      This metric has a tolerance parameter $c$ to allow differences when evaluating the similarity between occurrences, and in MIREX they use $c=.75$ and $c=.5$.
+    \item
+      \textbf{Three-layer F-measure, Precision, and Recall (TLF$_1$, P$_3$, R$_3$)}: These scores can be seen as an improved version of the standard metrics.
+      They capture both the establishment of the patterns and the occurrence retrieval in a single set of scores, being more permissive than the standard evaluation.
+    \item
+      \textbf{First $N$ patterns metrics (FFTP$_{est}$, FFP)}: This includes the first $N$ patterns target proportion establishment recall, and the first $N$ patterns three-layer precision. 
+      By analyzing the first $N$ patterns only, we evaluate the ability of the algorithm of sorting the identified patterns based on their relevance. 
+      In MIREX, $N=5$.
+
+\end{itemize}
 

### 2014-04-29 code/onset/onset.py
Updates to reflect not needing to remove negative events, also code which is closer to MIREX

@@ -88,13 +88,33 @@ for alg_name in ALG_NAMES:
 # <codecell>
 
 def clean_onsets(onsets):
-    ''' Simple function to remove negative onsets and sort '''
+    ''' Turns 0-dim onset lists (floats) into 1-dim arrays '''
     if onsets.ndim == 0:
-        onsets = np.array([onsets])
-    if onsets.size > 0:
-        return np.sort(onsets[onsets > 0])
+        return np.array([onsets])
     else:
         return onsets
+
+# <codecell>
+
+def f_measure_greedy(reference_onsets, estimated_onsets, window=.05):
+    # If either list is empty, return 0s
+    if reference_onsets.size == 0 or estimated_onsets.size == 0:
+        return 0., 0., 0.
+    correct = 0.0
+    count = 0
+    for onset in reference_onsets:
+        for n in xrange(count, estimated_onsets.shape[0]):
+            if np.abs(estimated_onsets[n] - onset) < window:
+                correct += 1
+                count = n + 1
+                break
+            elif estimated_onsets[n] > (onset + window):
+                count = n
+                break
+    precision = correct/estimated_onsets.shape[0]
+    recall = correct/reference_onsets.shape[0]
+    # Compute F-measure and return all statistics
+    return mir_eval.util.f_measure(precision, recall), precision, recall
 
 # <codecell>
 
@@ -144,8 +164,8 @@ mirex_scores = np.vstack(mirex_scores)
 
 # <codecell>
 
-diff = np.abs(mirex_scores - np.round(mir_eval_scores, 3))
-diff[np.less_equal(diff, .0010001)] = 0
+diff = np.abs(mirex_scores - np.round(mir_eval_scores, 4))
+diff[np.less_equal(diff, .00010001)] = 0
 print np.sum(diff, axis=0)/np.sum(mirex_scores, axis=0)
-print np.sum(diff, axis=0)/mirex_scores.shape[0]
+print np.mean(diff, axis=0)
 

### 2014-04-30 code/melody/melody.py
Melody experiment for #4

@@ -1,0 +1,276 @@
+# -*- coding: utf-8 -*-
+# <nbformat>3.0</nbformat>
+
+# <codecell>
+
+import urllib
+import glob
+import os
+import sys
+sys.path.append('../')
+import convert_json_instants_to_lab
+import shutil
+import csv
+import mir_eval
+import scipy.interpolate
+
+# <codecell>
+
+BASE_DATA_PATH = '../../data/melody'
+METRIC_KEYS = ['Overall Accuracy', 'Raw Pitch Accuracy', 'Raw Chroma Accuracy', 'Voicing Recall Rate', 'Voicing False-Alarm Rate']
+ALG_NAMES = ['SG2']
+
+# <codecell>
+
+# Download MIREX's reported files, which are subsampled to 50ms
+subsampled_dir = os.path.join(BASE_DATA_PATH, 'raw_50ms_js')
+try:
+    os.makedirs(subsampled_dir)
+except OSError:
+    pass
+JS_URL = 'http://nema.lis.illinois.edu/nema_out/mirex2011/results/ame/adc04/sg2melodytranscriptmeladc040000{:02d}.js'
+for n in xrange(12):
+    file_url = JS_URL.format(n)
+    urllib.urlretrieve(file_url, os.path.join(subsampled_dir, os.path.split(file_url)[1]))
+JS_URL = 'http://nema.lis.illinois.edu/nema_out/mirex2011/results/ame/adc04/sg2melodytranscriptmeladc04nv00000{}.js'
+for n in xrange(8):
+    file_url = JS_URL.format(n)
+    urllib.urlretrieve(file_url, os.path.join(subsampled_dir, os.path.split(file_url)[1]))
+
+# <codecell>
+
+# Maps between ADC2004 names and MIREX names
+FILENAME_MAPPING = {'opera_male5REF.txt' : 'sg2melodytranscriptmeladc04000000.js',
+                    'daisy3REF.txt' : 'sg2melodytranscriptmeladc04000001.js',
+                    'daisy1REF.txt' : 'sg2melodytranscriptmeladc04000002.js',
+                    'daisy2REF.txt' : 'sg2melodytranscriptmeladc04000003.js',
+                    'opera_male3REF.txt' : 'sg2melodytranscriptmeladc04000004.js',
+                    'daisy4REF.txt' : 'sg2melodytranscriptmeladc04000005.js',
+                    'pop1REF.txt' : 'sg2melodytranscriptmeladc04000006.js',
[…]

### 2014-04-30 code/beat/beat.py
Updated to download MIREX scores instead of relying on them locally.

@@ -13,13 +13,51 @@ import glob
 import os
 import csv
 import mir_eval
+sys.path.append('../')
+import convert_json_instants_to_lab
 import shutil
 import joblib
+import urllib
 
 # <codecell>
 
 BASE_DATA_PATH = '../../data/beat/'
 METRIC_KEYS = ['F-Measure', 'Cemgil', 'Goto', 'McKinney P-score', 'CMLc', 'CMLt', 'AMLc', 'AMLt', 'D (bits)']
+ALG_NAMES = ['FW4', 'ZDBG1', 'FW2', 'FW1', 'KFRO1', 'ZDG1', 'ZDG2', 'CDF2', 'CDF1', 'GP3',
+             'DP1', 'SB6', 'GP1', 'GKC3', 'SB5', 'GP2', 'ES3', 'ES1', 'EWFS1', 'FK1']
+
+# <codecell>
+
+datasets = ['dav', 'maz', 'mck']
+js_prefixes = ['smc', 'beatmaz000', 'beatmck000']
+# SMC dataset is missing a lot of entries.
+file_ranges = [np.delete(np.arange(1, 290), [19,24,28,30,38,39,44,48,49,52,61,69,
+                                             76,77,80,82,89,90,93,96,101,106,107,
+                                             109,111,114,121,122,124,127,128,130,
+                                             131,133,135,137,140,143,144,154,155,
+                                             159,161,162,163,164,176,179,182,184,
+                                             185,188,190,195,199,200,209,217,227,
+                                             229,230,232,233,237,239,244,245,246,
+                                             249,266,267,269]), range(322), range(140)]
+JS_URL = "http://nema.lis.illinois.edu/nema_out/mirex2013/results/abt/{}/transcription{}{:03d}.js"
+raw_js_dir = os.path.join(BASE_DATA_PATH, 'raw_js_data')
+if not os.path.exists(raw_js_dir):
+    os.makedirs(raw_js_dir)
+for dataset, js_prefix, file_range in zip(datasets, js_prefixes, file_ranges):
+    for n in file_range:
+        file_url = JS_URL.format(dataset, js_prefix, n)
+        urllib.urlretrieve(file_url, os.path.join(raw_js_dir, os.path.split(file_url)[1]))
+
+# <codecell>
+
+RESULT_URL = "http://nema.lis.illinois.edu/nema_out/mirex2013/results/abt/{}/{}/per_track_results.csv"
+csv_dir = os.path.join(BASE_DATA_PATH, 'mirex_scores_raw')
[…]

### 2014-04-30 code/melody/melody.py
Makes sense to report the mean abs error

@@ -265,7 +265,7 @@ diff = mirex_scores - np.round(mir_eval_scores, 4)
 for n, key in enumerate(METRIC_KEYS):
     print ' '*14*n + key
 print np.sum(np.abs(diff), axis=0)/np.sum(mirex_scores, axis=0)
-print np.mean(diff, axis=0)
+print np.mean(np.abs(diff), axis=0)
 
 # <codecell>
 

### 2014-04-30 code/melody/melody.py
Updated melody experiment #4 to match new changes in mir_eval

@@ -161,23 +161,6 @@ for filename in glob.glob(os.path.join(csv_dir, '*.csv')):
 
 # <codecell>
 
-def constant_hop_times(max_time, hop):
-    # Avoid float problems
-    max_time = np.round(max_time*1e10)*1e-10
-    times_new = np.linspace(0, hop*int(np.floor(max_time/hop)), int(np.floor(max_time/hop)) + 1)
-    times_new = np.round(times_new*1e10)*1e-10
-    return times_new
-
-# <codecell>
-
-def resample_zero(times, values, times_new):
-    if times_new.max() > times.max():
-        times = np.append(times, times_new.max())
-        values = np.append(values, 0)
-    return scipy.interpolate.interp1d(times, values, 'zero')(times_new)
-
-# <codecell>
-
 for ds in ['reference', 'estimated']:
     for mirex_file in glob.glob(os.path.join(BASE_DATA_PATH, '{}_mirex_50ms'.format(ds), '*', '*.txt')):
         mirex_times, mirex_values = mir_eval.io.load_time_series(mirex_file)
@@ -215,7 +198,8 @@ def process_one_algorithm(algorithm_directory, skip=False):
                                                                          os.path.split(estimated_melody_file)[1]))):
             ref_time, ref_freq = mir_eval.io.load_time_series(reference_melody_file)
             ref_v, est_v, ref_c, est_c = mir_eval.melody.to_cent_voicing(ref_time, ref_freq,
-                                                                         est_time, est_freq)
+                                                                         est_time, est_freq,
+                                                                         kind='zero', hop=0.01)
             for n, metric_name in enumerate(METRIC_KEYS):
                 if metric_name == 'Voicing Recall Rate':
                     vx_recall, vx_false_alm = mir_eval.melody.voicing_measures(ref_v, est_v)
@@ -261,11 +245,19 @@ np.set_printoptions(precision=10, threshold=10000, linewidth=150, suppress=True)
 
 # <codecell>
 
-diff = mirex_scores - np.round(mir_eval_scores, 4)
+print "Relative"
+print ' ',
 for n, key in enumerate(METRIC_KEYS):
-    print ' '*14*n + key
+    print '{:13s}'.format(key[:12]),
+print
 print np.sum(np.abs(diff), axis=0)/np.sum(mirex_scores, axis=0)
-print np.mean(np.abs(diff), axis=0)
+print
[…]

### 2014-04-30 code/onset/onset.py
Consistency

@@ -41,7 +41,7 @@ for alg in ALG_NAMES:
 
 # <codecell>
 
-for filename in glob.glob(os.path.join(BASE_DATA_PATH, 'mirex_scores_raw', '*.csv')):
+for filename in glob.glob(os.path.join(csv_dir, '*.csv')):
     output_list = []
     with open(filename, 'r') as f:
         csv_reader = csv.reader(f)

### 2014-04-30 paper/paper.tex
Added title, authors, section headings, removed ISMIR template stuff

@@
 \usepackage{braket}
+%\usepackage{authblk}
 
@@
 
-% \newcommand*{\defeq}{\mathrel{\rlap{%
-%                     \raisebox{0.25ex}{$\m@th\cdot$}}%
-%                     \raisebox{-0.25ex}{$\m@th\cdot$}}%
-%                     =}
-
-% Title.
 % ------
-\title{PAPER TEMPLATE FOR ISMIR 2014}
+\title{mir\_eval}
 
@@
 
+%\author[1]{Colin Raffel}
+%\author[1]{Brian McFee}
+%\author[2]{Justin Salamon}
+%\author[2]{Eric J. Humphrey}
+%\author[2]{Oriol Nieto}
+%\author[1]{Dawen Liang}
+%\author[1]{Daniel P. W. Ellis}
+%\affil[1]{LabROSA, Dept. of Electrical Engineering\\Columbia University, New York}
+%\affil[2]{Music and Audio Research Lab\\New York University, New York}
+
 % Four addresses
@@
 \begin{abstract}
-The abstract should be placed at the top left column and should contain about 150-200 words.
+
 \end{abstract}
 %
-\section{Introduction}\label{sec:introduction}
+\section{Evaluating MIR Algorithms}\label{sec:introduction}
 
-This template includes all the information about formatting manuscripts for the ISMIR 2014.
-Please follow these guidelines to give the final proceedings a uniform look.
-If you have any questions, please contact the Conference Management.
-This template can be downloaded from the ISMIR 2014 web site (http://ismir2014.ismir.net).
-
-\section{Page Size}\label{sec:page_size}
-
-The proceedings will be printed on
- \underline{portrait A4-size paper} \underline{(21.0cm x 29.7cm)}.
-All material on each page should fit within a rectangle of 17.2cm x 25.2cm,
-centered on the page, beginning 2.0cm
-from the top of the page and ending with 2.5cm from the bottom.
-The left and right margins should be 1.9cm.
-The text should be in two 8.2cm columns with a 0.8cm gutter.
-All text must be in a two-column format.
-Text must be fully justified.
-
-\section{Typeset Text}\label{sec:typeset_text}
-
-\subsection{Normal or Body Text}\label{subsec:body}
-
-Please use a 10pt (point) Times font. Sans-serif or non-proportional fonts
-can be used only for special purposes, such as distinguishing source code text.
-
-The first paragraph in each section should not be indented, but all other paragraphs should be.
-
-\subsection{Title and Authors}
-
-The title is 14pt Times, bold, caps, upper case, centered.
-Authors' names are omitted when submitting for double-blind reviewing.
-The following is for making a camera-ready version.
-Authors' names are centered.
-The lead author's name is to be listed first (left-most), and the co-authors' names after.
-If the addresses for all authors are the same, include the address only once, centered.
-If the authors have different addresses, put the addresses, evenly spaced, under each authors' name.
-
-\subsection{First Page Copyright Notice}
-
-Please include the copyright notice exactly as it appears here in the lower left-hand corner of the page.
-It is set in 8pt Times.
-
-\subsection{Page Numbering, Headers and Footers}
-
-Do not include headers, footers or page numbers in your submission.
-These will be added when the publications are assembled.
-
-\section{First Level Headings}
-
-First level headings are in Times 10pt bold,
-centered with 1 line of space above the section head, and 1/2 space below it.
-For a section header immediately followed by a subsection header, the space should be merged.
+\section{Tasks included in mir\_eval}
 
@@
 
-% \subsection{Figures, Tables and Captions}
-% 
-% All artwork must be centered, neat, clean, and legible.
-% All lines should be very dark for purposes of reproduction and art work should not be hand-drawn.
-% The proceedings are not in color, and therefore all figures must make sense in black-and-white form.
-% Figure and table numbers and captions always appear below the figure.
-% Leave 1 line space between the figure or table and the caption.
-% Each figure or table is numbered consecutively. Captions should be Times 10pt.
-% Place tables/figures in text as close to the reference as possible.
-% References to tables and figures should be capitalized, for example:
-% see \figref{fig:example} and \tabref{tab:example}.
-% Figures and tables may extend across both columns to a maximum width of 17.2cm.
+\section{Comparison to Existing Implementations}
 
-% \begin{table}
-%  \begin{center}
-%  \begin{tabular}{|l|l|}
-%   \hline
-%   String value & Numeric value \\
-%   \hline
-%   Hello ISMIR  & 2014 \\
-%   \hline
-%  \end{tabular}
-% \end{center}
-%  \caption{Table captions should be placed below the table.}
-%  \label{tab:example}
-% \end{table}
-
-%\begin{figure}
-% \centerline{\framebox{
-% \includegraphics[width=\columnwidth]{figure.png}}}
-% \caption{Figure captions should be placed below the figure.}
-% \label{fig:example}
-%\end{figure}
-
-% \begin{thebibliography}{citations}
-% 
-% \bibitem {Author:00}
-% E. Author:
-% ``The Title of the Conference Paper,''
-% {\it Proceedings of the International Symposium
-% on Music Information Retrieval}, pp.~000--111, 2000.
-% 
-% \bibitem{Someone:10}
-% A. Someone, B. Someone, and C. Someone:
-% ``The Title of the Journal Paper,''
-% {\it Journal of New Music Research},
-% Vol.~A, No.~B, pp.~111--222, 2010.
-% 
-% \bibitem{Someone:04} X. Someone and Y. Someone: {\it Title of the Book},
-%     Editorial Acme, Porto, 2012.
-% 
-% \end{thebibliography}
+\section{Discussion}
 

### 2014-05-01 paper/paper.tex
Abstract

@@
 \begin{abstract}
-
+Central to the field of MIR research is the evaluation of algorithms used to extract information from music data.
+We present mir\_eval, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
+In the present work, we enumerate the metrics implemented by mir\_eval and quantitatively compare each to an existing implementation.
+When the score reported by mir\_eval differs substantially from the reference, we detail the differences in implementation.
+We also provide a brief overview of mir\_eval's architecture, design, and intended use.
 \end{abstract}
 %
-\section{Evaluating MIR Algorithms}\label{sec:introduction}
+\section{Evaluating MIR Algorithms}
 

### 2014-05-01 paper/paper.tex
Beat metrics described

@@
 
+% MIR intends to act like humans
+% Human evaluation is costly
+% Metrics are used as a proxy
+
+% Evaluation should be easy and standardized
+% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, etc.
+% As a result many different implementations of metrics, and implementation matters
+% mir_eval as the antidote to the above
+
 \section{Tasks included in mir\_eval}
+
+\subsection{Beat Detection}
+
+The aim of a beat detection algorithm is to report the times at which a typical human listener might tap their foot to a piece of music.
+As a result, most metrics for evaluating the performance of beat tracking systems involve computing the error between the estimated beat times and some reference list of beat locations.
+Many metrics additionally compare the beat sequences at different metric levels in order to deal with the ambiguity of tempo \cite{levy2011improving}.
+
+mir\_eval includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}: The f-measure of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat; Cemgil's score, which computes the sum of Gaussian errors for each beat; Goto's score, a binary score which is 1 when some specific heuristic criteria are met, McKinney's P-score, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains; continuity-based scores which compute the proportion of the beat sequence which is continuously correct; and finally the information gain of the beat error histogram to a uniform distribution.
 

### 2014-05-01 paper/paper.tex
Short onset detection section

--- 2014-05-01 paper/paper.tex
@@
 
+% MIR intends to act like humans
+% Human evaluation is costly
+% Metrics are used as a proxy
+
+% Evaluation should be easy and standardized
+% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, etc.
+% As a result many different implementations of metrics, and implementation matters
+% mir_eval as the antidote to the above
+
+\section{mir\_eval's architecture}
+
+% Task submodules, one function per metric
+% io submodule for loading in data
+% Evaluators
+
 \section{Tasks included in mir\_eval}
+
+\subsection{Beat Detection}
+
+The aim of a beat detection algorithm is to report the times at which a typical human listener might tap their foot to a piece of music.
+As a result, most metrics for evaluating the performance of beat tracking systems involve computing the error between the estimated beat times and some reference list of beat locations.
+Many metrics additionally compare the beat sequences at different metric levels in order to deal with the ambiguity of tempo \cite{levy2011improving}.
+
+mir\_eval includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}: The \textbf{f-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat; \textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat; \textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met, \textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains; \textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct; and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.
 
@@
 
+\subsection{Onset Detection}
+
+The goal of an onset detection algorithm is to automatically determine when notes are played in a piece of music.
+As is also done in beat tracking and segment boundary detection, the primary method used to evaluate onset detectors is to first determine which estimated onsets are ``correct'', where correctness is defined as being within a small window of a reference onset \cite{bock2012evaluating}.
+From this, \textbf{precision}, \textbf{recall}, and \textbf{f-measure} scores are computed.
+
 \subsection{Blind Source Separation}

### 2014-05-01 paper/paper.tex
Adding results table with garbage values

@@
 %\usepackage{authblk}
+\usepackage{booktabs}
 
@@
 
+% Compared each mir_eval task to an existing implementation
+% Parameterized the same wherever possible
+
+% Beat: Compared against MIREX 2013
+% Chord: Compared against ??
+% Segmentation: Compared against ??
+% Melody: Compared against MIREX 2011, SG2 only
+% Pattern: Compared against development set, MATLAB code
+% Source Separation: Compared against SiSEC dev sets
+% Onset: Compared against MIREX 2013
+
+\begin{table*}[t]
+  \centering
+\begin{tabular}{c c c c c c c c c}
+\toprule
+ \multicolumn{9}{ c }{Beat Tracking} \\
+  \cmidrule(lr){1-9}
+ F-Measure  &  Cemgil   &   Goto    &    P-score & CMLc     &     CMLt       &   AMLc     &     AMLt    &      D (bits)\\
+ 0.00659 & 0.00035 & 0.00060  & 0.00877 & 0.00157 & 0.00135 & 0.00137&  0.00135 & 0.10566\\
+  \midrule
+ \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{4}{ c }{Something else}  \\
+  \cmidrule(lr){1-5}
+  \cmidrule(lr){6-9}
+ Root  &  Maj/Min   &   Maj/Min + Inv    &     Sevenths     &     Sevenths + Inv & CMLt      &   AMLc     &     AMLt    &      D (bits)\\
+ ??? & ??? & ???  & ??? & ??? & 0.00135 & 0.00137&  0.00135 & 0.10566\\
+  \midrule
+ \multicolumn{3}{ c }{Onset Detection} & \multicolumn{6}{ c }{Blah}  \\
+  \cmidrule(lr){1-3}
+  \cmidrule(lr){4-9}
+ F-Measure  &  Precision   &  Recall    &     McKinney P-s & CMLc     &     CMLt       &   AMLc     &     AMLt    &      D (bits)\\
+ 0.00203 & 0.00202 & 0.00203  & 0.00877 & 0.00157 & 0.00135 & 0.00137&  0.00135 & 0.10566\\
+  \bottomrule
+
+\end{tabular}
+\end{table*}
+
 \section{Discussion}

### 2014-05-03 code/segmentation/segmentation.py
Segmentation experiment for #1

@@ -1,0 +1,274 @@
+# -*- coding: utf-8 -*-
+# <nbformat>3.0</nbformat>
+
+# <codecell>
+
+'''
+Compare mir_eval against MIREX 2013 segmentation results
+'''
+
+# <codecell>
+
+import glob
+import os
+import csv
+import mir_eval
+sys.path.append('../')
+import convert_json_labels_to_lab
+import shutil
+import joblib
+import urllib
+
+# <codecell>
+
+BASE_DATA_PATH = '../../data/segment/'
+METRIC_KEYS = ['Normalised conditional entropy based over-segmentation score',
+               'Normalised conditional entropy based under-segmentation score',
+               'Frame pair clustering F-measure',
+               'Frame pair clustering precision rate',
+               'Frame pair clustering recall rate',
+               'Random clustering index',
+               'Segment boundary recovery evaluation measure @ 0.5sec',
+               'Segment boundary recovery precision rate @ 0.5sec',
+               'Segment boundary recovery recall rate @ 0.5sec',
+               'Segment boundary recovery evaluation measure @ 3sec',
+               'Segment boundary recovery precision rate @ 3sec',
+               'Segment boundary recovery recall rate @ 3sec',
+               'Median distance from an annotated segment boundary to the closest found boundary',
+               'Median distance from a found segment boundary to the closest annotated one']
+ALG_NAMES = ['RBH3', 'RBH2', 'RBH1', 'MP1', 'RBH4', 'MP2', 'CF5', 'CF6']
+
+# <codecell>
+
+datasets = ['mrx09', 'mrx10_1', 'mrx10_2', 'sal']
+js_prefixes = ['structmrx09', 'structmrx10', 'structmrx10', 'salami']
+# Salami is missing a bunch of entries
+file_ranges = [range(297),
+               range(100),
+               range(100),
+               np.delete(np.arange(1643),
+                         [1, 2, 3, 4, 6, 12, 16, 17, 18, 19, 26, 27, 30, 31, 32, 38, 39, 40, 41,
+                          43, 45, 49, 50, 51, 52, 57, 58, 59, 60, 61, 62, 65, 71, 72, 73, 74, 75,
+                          76, 77, 78, 82, 84, 85, 87, 88, 100, 101, 102, 103, 104, 107, 108, 109,
+                          110, 111, 112, 114, 115, 116, 117, 118, 124, 130, 133, 134, 136, 137,
[…]

### 2014-05-03 code/segmentation/segmentation.py
Misnomer

@@ -261,14 +261,13 @@ np.set_printoptions(precision=5, threshold=10000, linewidth=150, suppress=True)
 
 # <codecell>
 
-score_max = np.mean(np.dstack([np.round(mirex_scores, 3), np.round(mir_eval_scores, 3)]), axis=-1)
-score_max = score_max + (score_max == 0)
+score_mean = np.mean(np.dstack([np.round(mirex_scores, 3), np.round(mir_eval_scores, 3)]), axis=-1)
+score_mean = score_max + (score_max == 0)
 
 # <codecell>
 
 diff = np.round(mirex_scores, 4) - np.round(mir_eval_scores, 4)
 diff[np.less_equal(np.abs(diff), .00010001)] = 0
-for n, (key, score) in enumerate(zip(METRIC_KEYS, np.mean(np.abs(diff)/score_max, axis=0))):
-    print key
-    print score
+for n, (key, score) in enumerate(zip(METRIC_KEYS, np.mean(np.abs(diff)/score_mean, axis=0))):
+    print "{} : {:.5f}".format(key, score)
 

### 2014-05-03 code/segmentation/segmentation.py
Better error reporting

@@ -230,7 +230,7 @@ def process_one_algorithm(algorithm_directory, skip=False):
                 scores += get_mir_eval_scores(ref_intervals, ref_labels, est_intervals, est_labels)
             except Exception as e:
                 N = N - 1
-                print "Skipping {} because {}".format(reference_segments_file, str(e))
+                print "Skipping {} because {}".format(os.path.split(reference_segments_file)[1], str(e))
         if N >= 0:
             # Compute mean
             scores /= float(N + 1)

### 2014-05-03 code/beat/beat.py
Fixing on a relative change score

@@ -4,7 +4,7 @@
 # <codecell>
 
 '''
-Compare mir_eval against MIREX 2012 beat results
+Compare mir_eval against MIREX 2013 beat results
 '''
 
 # <codecell>
@@ -183,23 +183,20 @@ mirex_scores = np.vstack(mirex_scores)
 
 # <codecell>
 
-np.set_printoptions(precision=10, threshold=10000, linewidth=150, suppress=True)
+np.set_printoptions(precision=5, threshold=10000, linewidth=150, suppress=True)
+
+# <codecell>
+
+score_mean = np.mean(np.dstack([np.round(mirex_scores, 3), np.round(mir_eval_scores, 3)]), axis=-1)
+score_mean = score_mean + (score_mean == 0)
 
 # <codecell>
 
 diff = np.round(mirex_scores, 3) - np.round(mir_eval_scores, 3)
 diff[np.less_equal(np.abs(diff), .0010001)] = 0
-print "Relative"
 print ' ',
 for n, key in enumerate(METRIC_KEYS):
-    print '{:13s}'.format(key[:12]),
+    print '{:8s}'.format(key[:7]),
 print
-print np.sum(np.abs(diff), axis=0)/np.sum(mirex_scores, axis=0)
-print
-print "Absolute"
-print ' ',
-for n, key in enumerate(METRIC_KEYS):
-    print '{:13s}'.format(key[:12]),
-print
-print np.mean(np.abs(diff), axis=0)/100.
+print np.mean(np.abs(diff)/score_mean, axis=0)
 

### 2014-05-03 code/melody/melody.py
Fixing on a relative change calculation

@@ -245,19 +245,18 @@ np.set_printoptions(precision=10, threshold=10000, linewidth=150, suppress=True)
 
 # <codecell>
 
-print "Relative"
+score_mean = np.mean(np.dstack([np.round(mirex_scores, 4), np.round(mir_eval_scores, 4)]), axis=-1)
+score_mean = score_mean + (score_mean == 0)
+
+# <codecell>
+
+diff = np.round(mirex_scores, 4) - np.round(mir_eval_scores, 4)
+diff[np.less_equal(np.abs(diff), .00010001)] = 0
 print ' ',
 for n, key in enumerate(METRIC_KEYS):
     print '{:13s}'.format(key[:12]),
 print
-print np.sum(np.abs(diff), axis=0)/np.sum(mirex_scores, axis=0)
-print
-print "Absolute"
-print ' ',
-for n, key in enumerate(METRIC_KEYS):
-    print '{:13s}'.format(key[:12]),
-print
-print np.mean(np.abs(diff), axis=0)/100.
+print np.mean(np.abs(diff)/score_mean, axis=0)
 
 # <codecell>
 

### 2014-05-03 code/segmentation/segmentation.py
Should round by 4

@@ -261,7 +261,7 @@ np.set_printoptions(precision=5, threshold=10000, linewidth=150, suppress=True)
 
 # <codecell>
 
-score_mean = np.mean(np.dstack([np.round(mirex_scores, 3), np.round(mir_eval_scores, 3)]), axis=-1)
+score_mean = np.mean(np.dstack([np.round(mirex_scores, 4), np.round(mir_eval_scores, 4)]), axis=-1)
 score_mean = score_max + (score_max == 0)
 
 # <codecell>

### 2014-05-03 code/onset/onset.py
Fixing on relative change computation

@@ -164,8 +164,20 @@ mirex_scores = np.vstack(mirex_scores)
 
 # <codecell>
 
-diff = np.abs(mirex_scores - np.round(mir_eval_scores, 4))
-diff[np.less_equal(diff, .00010001)] = 0
-print np.sum(diff, axis=0)/np.sum(mirex_scores, axis=0)
-print np.mean(diff, axis=0)
+np.set_printoptions(precision=10, threshold=10000, linewidth=150, suppress=True)
+
+# <codecell>
+
+score_mean = np.mean(np.dstack([np.round(mirex_scores, 4), np.round(mir_eval_scores, 4)]), axis=-1)
+score_mean = score_mean + (score_mean == 0)
+
+# <codecell>
+
+diff = np.round(mirex_scores, 4) - np.round(mir_eval_scores, 4)
+diff[np.less_equal(np.abs(diff), .00010001)] = 0
+print ' ',
+for n, key in enumerate(METRIC_KEYS):
+    print '{:13s}'.format(key[:12]),
+print
+print np.mean(np.abs(diff)/score_mean, axis=0)
 

### 2014-05-03 code/segmentation/segmentation.py
updated experiment code for segments

@@ -13,6 +13,8 @@ import glob
 import os
 import csv
 import mir_eval
+import sys
+import numpy as np
 sys.path.append('../')
 import convert_json_labels_to_lab
 import shutil
@@ -192,9 +194,9 @@ def get_mir_eval_scores(ref_intervals, ref_labels, est_intervals, est_labels):
     scores.append(precision)
     scores.append(recall)
     
-    ari_score = mir_eval.structure.ari(ref_intervals, ref_labels,
+    rand_score = mir_eval.structure.rand_index(ref_intervals, ref_labels,
                                          est_intervals, est_labels)
-    scores.append(ari_score)
+    scores.append(rand_score)
     
     P05, R05, F05 = mir_eval.boundary.detection(ref_intervals, est_intervals, window=0.5)
     scores.append(F05)
@@ -262,7 +264,7 @@ np.set_printoptions(precision=5, threshold=10000, linewidth=150, suppress=True)
 # <codecell>
 
 score_mean = np.mean(np.dstack([np.round(mirex_scores, 4), np.round(mir_eval_scores, 4)]), axis=-1)
-score_mean = score_max + (score_max == 0)
+score_mean = score_mean + (score_mean == 0)
 
 # <codecell>
 

### 2014-05-03 code/segmentation/segmentation.py
don't use adjusted intervals for boundary

@@ -171,29 +171,29 @@ def get_mir_eval_scores(ref_intervals, ref_labels, est_intervals, est_labels):
     ''' Computes all mir_eval segment metrics and returns them in the order of METRIC_KEYS
     '''
     scores = []
-    ref_intervals, ref_labels = mir_eval.util.adjust_intervals(ref_intervals,
-                                                               ref_labels,
-                                                               t_min=0)
-    est_intervals, est_labels = mir_eval.util.adjust_intervals(est_intervals,
-                                                               est_labels,
-                                                               t_min=0,
-                                                               t_max=ref_intervals.max())
+    ref_intervals_adj, ref_labels_adj = mir_eval.util.adjust_intervals(ref_intervals,
+                                                                       ref_labels,
+                                                                       t_min=0)
+    est_intervals_adj, est_labels_adj = mir_eval.util.adjust_intervals(est_intervals,
+                                                                       est_labels,
+                                                                       t_min=0,
+                                                                       t_max=ref_intervals.max())
     
-    S_over, S_under, S_F = mir_eval.structure.nce(ref_intervals, ref_labels,
-                                                  est_intervals, est_labels)
+    S_over, S_under, S_F = mir_eval.structure.nce(ref_intervals_adj, ref_labels_adj,
+                                                  est_intervals_adj, est_labels_adj)
     scores.append(S_over)
     scores.append(S_under)
     
-    precision, recall, f = mir_eval.structure.pairwise(ref_intervals,
-                                                       ref_labels,
-                                                       est_intervals,
-                                                       est_labels)
+    precision, recall, f = mir_eval.structure.pairwise(ref_intervals_adj,
+                                                       ref_labels_adj,
+                                                       est_intervals_adj,
+                                                       est_labels_adj)
     scores.append(f)
     scores.append(precision)
     scores.append(recall)
     
-    ari_score = mir_eval.structure.ari(ref_intervals, ref_labels,
-                                         est_intervals, est_labels)
+    ari_score = mir_eval.structure.ari(ref_intervals_adj, ref_labels_adj,
+                                       est_intervals_adj, est_labels_adj)
     scores.append(ari_score)
     
     P05, R05, F05 = mir_eval.boundary.detection(ref_intervals, est_intervals, window=0.5)
[…]

### 2014-05-03 paper/paper.tex

@@
 The performance of an algorithm on an entire music collection for a given
-measure is obtained by averaging the per-excerpt scores for that measure over
-all excerpts in the collection.
+measure is obtained by averaging the per-song scores for that measure over
+all songs in the collection.
 

### 2014-05-03 code/onset/onset.py
Missing imports

@@ -12,6 +12,7 @@ import convert_json_instants_to_lab
 import shutil
 import csv
 import mir_eval
+import numpy as np
 
 # <codecell>
 

### 2014-05-03 code/segmentation/segmentation.py
MIREX doesn't include this score

@@ -194,9 +194,6 @@ def get_mir_eval_scores(ref_intervals, ref_labels, est_intervals, est_labels):
     scores.append(precision)
     scores.append(recall)
 
-    ari_score = mir_eval.structure.ari(ref_intervals_adj, ref_labels_adj,
-                                       est_intervals_adj, est_labels_adj)
-    scores.append(ari_score)
     rand_score = mir_eval.structure.rand_index(ref_intervals_adj, ref_labels_adj,
                                                est_intervals_adj, est_labels_adj)
     scores.append(rand_score)
@@ -235,7 +232,7 @@ def process_one_algorithm(algorithm_directory, skip=False):
                 scores += get_mir_eval_scores(ref_intervals, ref_labels, est_intervals, est_labels)
             except Exception as e:
                 N = N - 1
-                print "Skipping {} because {}".format(os.path.split(reference_segments_file)[1], str(e))
+                print "Skipping {} because {}".format(os.path.split(reference_segments_file)[1], e)
         if N >= 0:
             # Compute mean
             scores /= float(N + 1)
@@ -275,3 +272,4 @@ diff = np.round(mirex_scores, 4) - np.round(mir_eval_scores, 4)
 diff[np.less_equal(np.abs(diff), .00010001)] = 0
 for n, (key, score) in enumerate(zip(METRIC_KEYS, np.mean(np.abs(diff)/score_mean, axis=0))):
     print "{} : {:.5f}".format(key, score)
+

### 2014-05-03 code/chord/chord.py
First pass at reference comparison ... realizing some MIREX comparisons are quite different. Hooraaayy

@@ -1,0 +1,57 @@
+'''
+Compare mir_eval against MIREX 2013 chord results
+'''
+
+import json
+import numpy as np
+from mir_eval import chord
+
+# Consists of three aligned lists
+#   referece_files
+#   estimation_files
+#   scores
+result_json_file = "./data/result_sample.json"
+with open(result_json_file) as fp:
+    results = json.load(fp)
+
+VOCABS = ['root', 'majmin', 'majmin-inv', 'sevenths', 'sevenths-inv']
+MIREX_VOCABS = ["MirexRoot", "MirexMajMinBass", "MirexMajMin",
+                "MirexSeventhsBass", "MirexSevenths"]
+
+
+def get_mir_eval_scores(reference_files, estimation_files):
+    '''Computes all mir_eval metrics and returns them in a list with the order
+    ['root', 'majmin', 'majmin-inv', 'sevenths', 'sevenths-inv'].
+    '''
+
+    scores = dict([(k, list()) for k in VOCABS])
+
+    for ref, est in zip(reference_files, estimation_files):
+        single_score = chord.evaluate_file_pair(ref, est, VOCABS)
+        for name, score in single_score.items():
+            # Skip weights and errors
+            if name in scores:
+                scores[name].append(score)
+
+    return [100*np.array(scores[name]) for name in VOCABS]
+
+mir_eval_scores = get_mir_eval_scores(results['reference_files'],
+                                      results['estimation_files'])
+
+
+def get_mirex_scores(scores):
+    vocab_scores = dict([(k, list()) for k in MIREX_VOCABS])
+    for single_score in scores:
+        for name, score in single_score.items():
+            # Skip weights and errors
+            if name in vocab_scores:
+                vocab_scores[name].append(score)
+
+    return [np.array(vocab_scores[name]) for name in MIREX_VOCABS]
+
+
+mirex_scores = get_mirex_scores(results['scores'])
+
+errors = np.array([np.abs(a - b)
+                   for a, b in zip(mir_eval_scores, mirex_scores)])
+

### 2014-05-04 code/chord/chord.py
Added chord reference framework ... apparently a few comparison 'bugs' to fix in mir_eval.chord

@@ -5,18 +5,24 @@ Compare mir_eval against MIREX 2013 chord results
 import json
 import numpy as np
 from mir_eval import chord
+from os.path import basename
 
 # Consists of three aligned lists
 #   referece_files
 #   estimation_files
 #   scores
-result_json_file = "./data/result_sample.json"
+result_json_file = "./data/mirex_results.json"
 with open(result_json_file) as fp:
     results = json.load(fp)
 
 VOCABS = ['root', 'majmin', 'majmin-inv', 'sevenths', 'sevenths-inv']
-MIREX_VOCABS = ["MirexRoot", "MirexMajMinBass", "MirexMajMin",
-                "MirexSeventhsBass", "MirexSevenths"]
+MIREX_VOCABS = [
+    "resultsMirexRoot", "resultsMirexMajMin", "resultsMirexMajMinBass",
+    "resultsMirexSevenths", "resultsMirexSeventhsBass"]
+
+
+def filebase(fpath):
+    return basename(fpath).split('.')[0]
 
 
 def get_mir_eval_scores(reference_files, estimation_files):
@@ -39,18 +45,18 @@ mir_eval_scores = get_mir_eval_scores(results['reference_files'],
                                       results['estimation_files'])
 
 
-def get_mirex_scores(scores):
+def get_mirex_scores(estimation_files, score_object):
     vocab_scores = dict([(k, list()) for k in MIREX_VOCABS])
-    for single_score in scores:
-        for name, score in single_score.items():
-            # Skip weights and errors
-            if name in vocab_scores:
-                vocab_scores[name].append(score)
+    for est_file in estimation_files:
+        algo, filename = est_file.split("/")[-2:]
+        track_base = filebase(filename)
+        for task in MIREX_VOCABS:
+            vocab_scores[task].append(score_object[track_base][algo][task])
 
     return [np.array(vocab_scores[name]) for name in MIREX_VOCABS]
 
 
-mirex_scores = get_mirex_scores(results['scores'])
+mirex_scores = get_mirex_scores(results['estimation_files'], results['scores'])
 
 errors = np.array([np.abs(a - b)
                    for a, b in zip(mir_eval_scores, mirex_scores)])

### 2014-05-04 paper/paper.tex

@@
 
-\def\eg{\emph{e.g.\/}}
-\def\ie{\emph{i.e.\/}}
-\def\etc{\emph{etc.\/}}
-\def\etal{\emph{et al.\/}}
+\def\eg{\emph{e.g.}}
+\def\ie{\emph{i.e.}}
+\def\etc{\emph{etc.}}
+\def\etal{\emph{et al.}}
 \DeclareMathOperator*{\median}{median}
@@
 \def\defeq{\ensuremath{:=}}
+
+\def\mireval{\texttt{mir\_eval}}
 
@@
 
-\subsubsection{Boundary annotation}
+\mireval implements the following MIREX-compatible boundary detection metrics:
+\begin{description}
+\item[Boundary detection:] precision, recall, and F-measure for detecting boundary
+events within a tolerance window $w\in \{0.5, 3\}$~\cite{turnbull2007supervised};
+\item[Boundary deviation:] median absolute time difference from a reference boundary
+to its nearest estimated boundary, and vice versa~\cite{turnbull2007supervised},
+\end{description}
+and the following structure annotation metrics
+\begin{description}
+\item[Pairwise classification:] precision, recall, and F-measure for classifying pairs
+of sampled time instants as belonging to the same structural
+component~\cite{levy2008structural};
+\item[Rand index:\footnote{The MIREX results page refers to Rand index as ``random
+clustering index''.}] reference and estimated annotations are sampled uniformly
+throughout the track, and the induced clusterings are compared by the Rand index
+~\cite{rand1971objective};
+\item[Normalized conditional entropy:] reference and estimated labels are sampled
+uniformly, and interpreted as samples of random variables $Y_R, Y_E$, which are
+computed by estimating the conditional entropy of $Y_R$ given $Y_E$
+(\emph{under-segmentation}) and $Y_E$ given $Y_R$ 
+(\emph{over-segmentation})~\cite{lukashevich2008towards}.
+\end{description}
 
-Within boundary annotation, there are two categories of evaluation metrics: detection,
-and deviation~\cite{turnbull2007supervised}.
+% \subsubsection{Boundary annotation}
 
-\emph{Boundary detection} measures the precision, recall, and F-measure of boundary prediction within a window.
-Let $B^R$ ($B^E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
-a window, typically either $0.5$s or $3.0$s.  
-A \emph{hit} is defined as a pair $b_e \in B^E$, $b_r \in B^R$ such that $|b_e - b_r|
-\leq W$.
+% Within boundary annotation, there are two categories of evaluation metrics: detection,
+% and deviation~\cite{turnbull2007supervised}.
 
-No estimated boundary is counted as a hit for more than one reference boundary, and vice versa.
-This is accomplished by computing a maximum bipartite matching $H_W$ between $B^E$ and $B^R$ (subject to the window constraint $W$)
-using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  This deviates from the greedy heuristic used in the MIREX
-implementation, but it is guaranteed to produce a correct matching.  Precision and recall at window $W$ are defined as
-\begin{align}
-P_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^E|}\\
-R_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^R|},
-\end{align}
-and the corresponding F-measure is defined by taking their harmonic mean.
+% \emph{Boundary detection} measures the precision, recall, and F-measure of boundary prediction within a window.
+% Let $B^R$ ($B^E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
+% a window, typically either $0.5$s or $3.0$s.  
+% A \emph{hit} is defined as a pair $b_e \in B^E$, $b_r \in B^R$ such that $|b_e - b_r|
+% \leq W$.
 
-\emph{Boundary deviation} is comprised of two scores, which measure the median time between a reference boundary and its nearest corresponding estimated boundary, and vice versa.
-These two metrics have previously been defined as \emph{true-to-predicted} (T-to-P) and \emph{predicted-to-true} (P-to-T), though in the terminology of this document, we use 
-alternative naming of \emph{reference-to-estimated} (R-to-E) and \emph{estimated-to-reference} (E-to-R):
-\begin{align}
-\text{R-to-E}(B^R, B^E) &\defeq \displaystyle\median_{b_r \in B^R} \min_{b_e \in B^E} \left|b_r - b_e\right|\\
-\text{E-to-R}(B^R, B^E) &\defeq \displaystyle\median_{b_e \in B^E} \min_{b_r \in B^R} \left|b_r - b_e\right|.
-\end{align}
+% No estimated boundary is counted as a hit for more than one reference boundary, and vice versa.
+% This is accomplished by computing a maximum bipartite matching $H_W$ between $B^E$ and $B^R$ (subject to the window constraint $W$)
+% using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  This deviates from the greedy heuristic used in the MIREX
+% implementation, but it is guaranteed to produce a correct matching.  Precision and recall at window $W$ are defined as
+% \begin{align}
+% P_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^E|}\\
+% R_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^R|},
+% \end{align}
+% and the corresponding F-measure is defined by taking their harmonic mean.
 
-\subsubsection{Structural annotation}
-Two standard methods of evaluating structural annotation accuracy are \emph{pairwise classification}~\cite{levy2008structural}
-and conditional entropy~\cite{lukashevich2008towards}.  In both methods, a collection of samples are generated by sampling the
-labels at time steps between $0$ and the track duration.  The $i$th sample is assigned a reference label $y_i^R$ and
-and estimated label $y_i^E$.  Our implementation follows the MIREX guidelines, and generates samples at a default rate of 10Hz.
+% \emph{Boundary deviation} is comprised of two scores, which measure the median time between a reference boundary and its nearest corresponding estimated boundary, and vice versa.
+% These two metrics have previously been defined as \emph{true-to-predicted} (T-to-P) and \emph{predicted-to-true} (P-to-T), though in the terminology of this document, we use 
+% alternative naming of \emph{reference-to-estimated} (R-to-E) and \emph{estimated-to-reference} (E-to-R):
+% \begin{align}
+% \text{R-to-E}(B^R, B^E) &\defeq \displaystyle\median_{b_r \in B^R} \min_{b_e \in B^E} \left|b_r - b_e\right|\\
+% \text{E-to-R}(B^R, B^E) &\defeq \displaystyle\median_{b_e \in B^E} \min_{b_r \in B^R} \left|b_r - b_e\right|.
+% \end{align}
 
-Reference and estimated annotations must span identical time durations for annotation metrics to be well-defined.
-This is accomplished in our implementation by trimming or padding the estimated annotation to exactly match the start and end-times
-reported in the reference annotation, and synthesizing unique labels if necessary.
+% \subsubsection{Structural annotation}
+% Two standard methods of evaluating structural annotation accuracy are \emph{pairwise classification}~\cite{levy2008structural}
+% and conditional entropy~\cite{lukashevich2008towards}.  In both methods, a collection of samples are generated by sampling the
+% labels at time steps between $0$ and the track duration.  The $i$th sample is assigned a reference label $y_i^R$ and
+% and estimated label $y_i^E$.  Our implementation follows the MIREX guidelines, and generates samples at a default rate of 10Hz.
 
-Given the labels for the samples $\{(y_i^R, y_i^E)\}_{i=1}^n$, the \emph{pairwise classification} metrics are defined as precision,
-recall, and F-measure of label agreement over all unique, distinct pairs $i \neq j$.  
-Let $A_R = \{ \{i, j\} \given y_i^R = y_j^R\}$ denote the set of similarly labeled frames in the reference, with $A_E$ defined
-analogously for the estimation.  Precision and recall are defined as
-\begin{align}
-P_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_E| }\\
-R_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_R| }.
-\end{align}
+% Reference and estimated annotations must span identical time durations for annotation metrics to be well-defined.
+% This is accomplished in our implementation by trimming or padding the estimated annotation to exactly match the start and end-times
+% reported in the reference annotation, and synthesizing unique labels if necessary.
 
-\emph{Normalized conditional entropy} scores are computed by estimating the conditional entropy of the estimated label $y^E$ given
-the reference label $y^R$ and vice versa.  Let $P$ denote the empirical joint distribution over reference and estimated labels:
-\begin{align}
-P_{ij} &\propto \left|\{t \given y_t^R = i \wedge y_t^E = j\}\right|.
-\end{align}
-Let $Y^R$ and $Y^E$ denote random variables corresponding to the reference and estimated label for an arbitrary sample.
-The conditional entropies $H\left(Y^E \given Y^R\right)$ and $H\left(Y^R \given Y^E\right)$ are estimated from the 
-empirical marginals ${p_i^R = \sum_j P_{ij}}$ and ${p_j^E = \sum_i P_{ij}}$ as described by 
-Lukashevich~\cite{lukashevich2008towards}.
+% Given the labels for the samples $\{(y_i^R, y_i^E)\}_{i=1}^n$, the \emph{pairwise classification} metrics are defined as precision,
+% recall, and F-measure of label agreement over all unique, distinct pairs $i \neq j$.  
+% Let $A_R = \{ \{i, j\} \given y_i^R = y_j^R\}$ denote the set of similarly labeled frames in the reference, with $A_E$ defined
+% analogously for the estimation.  Precision and recall are defined as
+% \begin{align}
+% P_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_E| }\\
+% R_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_R| }.
+% \end{align}
 
-The final scores are defined as \emph{over-segmentation} ($S_\text{O}$) and \emph{under-segmentation} ($S_\text{U}$):
-\begin{align}
-S_\text{O} &\defeq 1 - \frac{H(E \given R)}{\log_2 |\ell^E|}\\
-S_\text{U} &\defeq 1 - \frac{H(R \given E)}{\log_2 |\ell^R|},
-\end{align}
-where $\ell^R$ and $\ell^E$ denote the sets of unique label values given in the reference and estimation.
+% \emph{Normalized conditional entropy} scores are computed by estimating the conditional entropy of the estimated label $y^E$ given
+% the reference label $y^R$ and vice versa.  Let $P$ denote the empirical joint distribution over reference and estimated labels:
+% \begin{align}
+% P_{ij} &\propto \left|\{t \given y_t^R = i \wedge y_t^E = j\}\right|.
+% \end{align}
+% Let $Y^R$ and $Y^E$ denote random variables corresponding to the reference and estimated label for an arbitrary sample.
+% The conditional entropies $H\left(Y^E \given Y^R\right)$ and $H\left(Y^R \given Y^E\right)$ are estimated from the 
+% empirical marginals ${p_i^R = \sum_j P_{ij}}$ and ${p_j^E = \sum_i P_{ij}}$ as described by 
+% Lukashevich~\cite{lukashevich2008towards}.
+
+% The final scores are defined as \emph{over-segmentation} ($S_\text{O}$) and \emph{under-segmentation} ($S_\text{U}$):
+% \begin{align}
+% S_\text{O} &\defeq 1 - \frac{H(E \given R)}{\log_2 |\ell^E|}\\
+% S_\text{U} &\defeq 1 - \frac{H(R \given E)}{\log_2 |\ell^R|},
+% \end{align}
+% where $\ell^R$ and $\ell^E$ denote the sets of unique label values given in the reference and estimation.
 

### 2014-05-05 code/pattern/pattern.py
Pattern experiment

@@ -1,0 +1,168 @@
+# -*- coding: utf-8 -*-
+# <nbformat>3.0</nbformat>
+
+# <codecell>
+
+import glob
+import os
+import sys
+import shutil
+import mir_eval
+import numpy as np
+
+# <codecell>
+
+BASE_DATA_PATH = '../../data/pattern/'
+METRIC_KEYS = ['P_est', 'R_est', 'F1_est', 'P_occ(c=.75)', 'R_occ(c=.75)', 'F_1occ(c=.75)', 'P_3', 'R_3',
+               'TLF_1', 'FFTP_est', 'FFP', 'P_occ(c=.5)', 'R_occ(c=.5)', 'F_1occ(c=.5)', 'P', 'R', 'F_1']
+
+# <codecell>
+
+# Convert flat .txt to dirs
+current_algorithm = ''
+current_file = ''
+with open(os.path.join(BASE_DATA_PATH, 'matlab_scores_raw', 'resultsMATLAB.txt')) as f:
+    for line in f:
+        if 'Algorithm' in line:
+            current_algorithm = line.strip()[-3:]
+        elif 'monophonic' in line:
+            current_phonic = 'monophonic'
+            current_file = line.strip().replace('-monophonic', '')
+        elif 'polyphonic' in line:
+            current_phonic = 'polyphonic'
+            current_file = line.strip().replace('-polyphonic', '')
+        else:
+            try:
+                scores = np.array([float(n) for n in line.strip().split(',')])
+            except ValueError:
+                continue
+            output_path = os.path.join(BASE_DATA_PATH, current_phonic, 'matlab_scores', current_algorithm)
+            if not os.path.exists(output_path):
+                os.makedirs(output_path)
+            np.savetxt(os.path.join(output_path, current_file + '.txt'), scores)
+
+# <codecell>
+
+mir_eval.pattern.METRICS.keys()
+
+# <codecell>
+
+help(mir_eval.pattern.first_n_target_proportion_R)
+
+# <codecell>
+
+def get_mir_eval_scores(reference_pattern, estimated_pattern):
+    ''' Computes all mir_eval pattern metrics and returns them in the correct order
+    '''
+    #METRIC_KEYS = ['P_est', 'R_est', 'F1_est', 'P_occ(c=.75)', 'R_occ(c=.75)', 'F_1occ(c=.75)', 'P_3', 'R_3',
[…]

### 2014-05-06 paper/paper.tex
Filled out table

--- 2014-05-03 paper/paper.tex
@@
 
+% Beat - 9 metrics
+% Chord - 5 metrics
+% Segmentation - 14 metrics
+% Melody - 5 metrics
+% Pattern - 21 metrics
+% Onset - 3 metrics
+% Source Separation - 3 metrics
+
 \begin{table*}[t]
   \centering
-\begin{tabular}{c c c c c c c c c}
+\begin{tabular}{c c c c c c c c c c}
 \toprule
- \multicolumn{9}{ c }{Beat Tracking} \\
-  \cmidrule(lr){1-9}
- F-Measure  &  Cemgil   &   Goto    &    P-score & CMLc     &     CMLt       &   AMLc     &     AMLt    &      D (bits)\\
- 0.00659 & 0.00035 & 0.00060  & 0.00877 & 0.00157 & 0.00135 & 0.00137&  0.00135 & 0.10566\\
+ \multicolumn{5}{ c }{Chord} & \multicolumn{5}{ c }{Melody}\\
+  \cmidrule(lr){1-5}
+  \cmidrule(lr){5-10}
+ Root & M/m & M/m + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Raw Chroma & Voicing R & Voicing F-A\\
+ ??? & ??? & ??? & ??? & ??? & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
   \midrule
- \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{4}{ c }{Something else}  \\
-  \cmidrule(lr){1-5}
-  \cmidrule(lr){6-9}
- Root  &  Maj/Min   &   Maj/Min + Inv    &     Sevenths     &     Sevenths + Inv & CMLt      &   AMLc     &     AMLt    &      D (bits)\\
- ??? & ??? & ???  & ??? & ??? & 0.00135 & 0.00137&  0.00135 & 0.10566\\
+ \multicolumn{10}{ c }{Segmentation} \\
+  \cmidrule(lr){1-10}
+  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5       & F@3 \\
+3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\% &    0.393\% \\
   \midrule
- \multicolumn{3}{ c }{Onset Detection} & \multicolumn{6}{ c }{Blah}  \\
+ \multicolumn{4}{ c }{Segmentation} & \multicolumn{6}{ c }{Beat}\\
+  \cmidrule(lr){1-4}
+  \cmidrule(lr){5-10}
+  P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt \\
+  0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% \\
+  \midrule
+ \multicolumn{3}{ c }{Beat} & \multicolumn{7}{ c }{Pattern}\\
   \cmidrule(lr){1-3}
-  \cmidrule(lr){4-9}
- F-Measure  &  Precision   &  Recall    &     McKinney P-s & CMLc     &     CMLt       &   AMLc     &     AMLt    &      D (bits)\\
- 0.00203 & 0.00202 & 0.00203  & 0.00877 & 0.00157 & 0.00135 & 0.00137&  0.00135 & 0.10566\\
+  \cmidrule(lr){4-10}
+  AMLc       & AMLt       & D (bits) & Pat & Pat & Pat & Pat & Pat & Pat & Pat \\
+  0.137\% &    0.139\% &   10.166\% &  ??? & ??? & ??? & ??? & ??? & ??? & ???\\
+  \midrule
+ \multicolumn{10}{ c }{Pattern}\\
+  \cmidrule(lr){1-10}
+  Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat\\
+  ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ???\\
+  \midrule
+ \multicolumn{4}{ c }{Pattern}  & \multicolumn{3}{ c }{Onset}  & \multicolumn{3}{ c }{Source Separation}\\
+  \cmidrule(lr){1-4}
+  \cmidrule(lr){5-7}
+  \cmidrule(lr){8-10}
+ Pat & Pat & Pat & Pat & F-measure  & Precision  & Recall & SDR & SIR & SAR \\
+ ??? & ??? & ??? & ??? &    0.165\% &    0.165\% &    0.165\% & ??? & ??? & ??? \\
   \bottomrule

### 2014-05-06 paper/paper.tex
Adding introduction first draft

@@
 
-% MIR intends to act like humans
-% Human evaluation is costly
-% Metrics are used as a proxy
+Many tasks in the field of Music Information Retrieval (MIR) involve the development of systems which can automatically produce semantic information about a piece of music.
+The effectiveness of such a system is typically judged based on how similar it acts to a human \cite{downie2003toward}.
+A straightforward way to make this judgement would be for a human to study the output produced by the system and judge its correctness.
+However, this process is inherently subjective and also extremely time-consuming when evaluating a system's output over a large corpus of music.
 
-% Evaluation should be easy and standardized
-% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, etc.
-% As a result many different implementations of metrics, and implementation matters
-% mir_eval as the antidote to the above
+As a result, metrics have been defined for each task which provide a well-defined way of computing a score which denotes the correctness of a system's output.
+These metrics typically involve a heuristically-motivated comparison of the system's output to a reference which is known to be correct.
+Over time, certain metrics have become standard for each task, so that the performance of systems created by different researchers can be compared when they are evaluated over the same dataset \cite{downie2003toward}.
+Unfortunately, this comparison can be confounded by the fact that the actual implementation of the metric can affect the scores it produces.
+
+% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, not used outside of MIREX, etc.
+For the past 10 years, the yearly Music Information Retrieval EXchange (MIREX) has provided setting in which different MIR algorithms may be compared against common datasets \cite{downie2008music}.
+By providing a standardized shared-task setting to track progress, MIREX has proven to be critically useful in the evolution of MIR research.
+MIREX relies on the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
+The NEMA codebase includes multiple programming languages and dependencies (including proprietary ones, e.g. MATLAB) so compiling and running it for research uses is nontrivial.
+
+Due to its scale, characteristics, and intended use, the NEMA system is rarely used for evaluating MIR algorithms outside of the setting of MIREX \cite{downie2008music}.
+As a result, researchers typically create their own implementations of common metrics for evaluating their algorithms.
+These implementations are not standardized, and even worse, may contain bugs.
+Both of these factors can confound comparison of different systems.
+
+These factors motivate the development of a standardized software package which implements the most common metrics used to evaluate MIR systems.
+Such a package should be straightforward to use and well-documented so that it can be easily adopted and understood by MIR researchers.
+In addition, it should be community-developed and transparently implemented so that all design decisions are well-reasoned and easily understood.
+
+Motivated by these criteria, we present \mireval, a software package which intends to provide an easy and standardized way to evaluate MIR systems.
+The present work first discusses the architecture and design of \mireval in Section \ref{sec:architecture}.
+In Section \ref{sec:tasks}, we describe all of the tasks covered by \mireval and the metrics included.
+In order to validate our implementation decisions, we compare \mireval to existing software in Section \ref{sec:comparison}.
+Finally, we discuss and summarize our contributions in Section \ref{sec:discussion}.
 
 \section{mir\_eval's architecture}
+\label{sec:architecture}
 
@@
 \section{Tasks included in mir\_eval}
+\label{sec:tasks}
 
@@
 \section{Comparison to Existing Implementations}
+\label{sec:comparison}
 
@@
 \section{Discussion}
+\label{sec:discussion}
 

### 2014-05-06 paper/paper.tex
Cap

@@
 
-mir\_eval includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}: The \textbf{f-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat; \textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat; \textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met, \textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains; \textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct; and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.
+mir\_eval includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}: The \textbf{F-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat; \textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat; \textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met, \textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains; \textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct; and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.
 

### 2014-05-06 paper/paper.tex
Updating mir_eval formatting

@@
 
-\def\mireval{\texttt{mir\_eval}}
+\def\mireval{\texttt{mir\char`_eval}}
 
 % ------
-\title{mir\_eval}
+\title{\mireval{}}
 
@@
 Central to the field of MIR research is the evaluation of algorithms used to extract information from music data.
-We present mir\_eval, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
-In the present work, we enumerate the metrics implemented by mir\_eval and quantitatively compare each to an existing implementation.
-When the score reported by mir\_eval differs substantially from the reference, we detail the differences in implementation.
-We also provide a brief overview of mir\_eval's architecture, design, and intended use.
+We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
+In the present work, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to an existing implementation.
+When the score reported by \mireval{} differs substantially from the reference, we detail the differences in implementation.
+We also provide a brief overview of \mireval{}'s architecture, design, and intended use.
 \end{abstract}
@@
 
-Motivated by these criteria, we present \mireval, a software package which intends to provide an easy and standardized way to evaluate MIR systems.
-The present work first discusses the architecture and design of \mireval in Section \ref{sec:architecture}.
-In Section \ref{sec:tasks}, we describe all of the tasks covered by \mireval and the metrics included.
-In order to validate our implementation decisions, we compare \mireval to existing software in Section \ref{sec:comparison}.
+Motivated by these criteria, we present \mireval{}, a software package which intends to provide an easy and standardized way to evaluate MIR systems.
+The present work first discusses the architecture and design of \mireval{} in Section \ref{sec:architecture}.
+In Section \ref{sec:tasks}, we describe all of the tasks covered by \mireval{} and the metrics included.
+In order to validate our implementation decisions, we compare \mireval{} to existing software in Section \ref{sec:comparison}.
 Finally, we discuss and summarize our contributions in Section \ref{sec:discussion}.
 
-\section{mir\_eval's architecture}
+\section{\mireval{}'s architecture}
 \label{sec:architecture}
@@
 
-\section{Tasks included in mir\_eval}
+\section{Tasks included in \mireval{}}
 \label{sec:tasks}
@@
 
-mir\_eval includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}: The \textbf{F-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat; \textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat; \textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met, \textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains; \textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct; and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.
+\mireval{} includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}: The \textbf{F-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat; \textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat; \textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met, \textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains; \textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct; and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.
 
@@
 
-\mireval implements the following MIREX-compatible boundary detection metrics:
+\mireval{} implements the following MIREX-compatible boundary detection metrics:
 \begin{description}
@@
 
-For this reason, the melody evaluator in mir\_eval uses $1^{st}$-order (linear)
+For this reason, the melody evaluator in \mireval{} uses $1^{st}$-order (linear)
 interpolation by default in order to map the reference and estimate sequences
@@
 using $1^{st}$-order rather than $0^{th}$-order interpolation means the results
-returned by mir\_eval are lower-bounded by the MIREX results and are, in our
+returned by \mireval{} are lower-bounded by the MIREX results and are, in our
 view, more accurate.

### 2014-05-06 paper/paper.tex
One sentence per line

@@
 
-\mireval{} includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}: The \textbf{F-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat; \textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat; \textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met, \textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains; \textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct; and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.
+\mireval{} includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}:
+The \textbf{F-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat;
+\textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat;
+\textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met;
+\textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains;
+\textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct;
+and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.
 

### 2014-05-06 paper/paper.tex
Fixes overfull hboxes with texttt
Wording

@@
 \usepackage{booktabs}
+
+\usepackage{microtype}
 
@@
 Many tasks in the field of Music Information Retrieval (MIR) involve the development of systems which can automatically produce semantic information about a piece of music.
-The effectiveness of such a system is typically judged based on how similar it acts to a human \cite{downie2003toward}.
-A straightforward way to make this judgement would be for a human to study the output produced by the system and judge its correctness.
+The effectiveness of these systems is typically determined based on how similarly they act to a human listener \cite{downie2003toward}.
+A straightforward way to determine a system's effectiveness would be for a human to study the output produced by the system and judge its correctness.
 However, this process is inherently subjective and also extremely time-consuming when evaluating a system's output over a large corpus of music.
@@
 % MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, not used outside of MIREX, etc.
-For the past 10 years, the yearly Music Information Retrieval EXchange (MIREX) has provided setting in which different MIR algorithms may be compared against common datasets \cite{downie2008music}.
+For the past 10 years, the yearly Music Information Retrieval EXchange (MIREX) has provided setting in which different MIR algorithms are compared over common datasets \cite{downie2008music}.
 By providing a standardized shared-task setting to track progress, MIREX has proven to be critically useful in the evolution of MIR research.
@@
 
-Motivated by these criteria, we present \mireval{}, a software package which intends to provide an easy and standardized way to evaluate MIR systems.
+Following these criteria, we present \mireval{}, a software package which intends to provide an easy and standardized way to evaluate MIR systems.
 The present work first discusses the architecture and design of \mireval{} in Section \ref{sec:architecture}.

### 2014-05-06 paper/paper.tex
architecture section first draft

@@
 
+\usepackage{url}
 \usepackage{microtype}
@@
 
-% Task submodules, one function per metric
-% io submodule for loading in data
-% Evaluators
+\mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord recognition, pattern discovery, structural segmentation, melody extraction, onset detection, and source separation.
+Each task is given its own submodule (e.g. \mireval{}\texttt{.beat}), and each metric is defined as a separate function in each submodule (e.g. \mireval{}\texttt{.beat.f\char`_measure}).
+Each task submodule also includes common data pre-processing steps for the task.
+Every metric function includes detailed documentation, example usage, input validation, and references to the original paper which defined the metric.
+\mireval{} also includes a submodule \texttt{io} which provides convenience functions for loading in task-specific data from common file formats.
+For readability, all code follows the PEP8 style guide\cite{van2001pep}.
+\mireval{}'s only dependencies outside of the Python standard library are the free and open-source SciPy/Numpy\cite{jones2001scipy} and scikit-learn\cite{pedregosa2011scikit} Python libraries.
+
+In order to simplify the usage of \mireval{}, it is packaged with a set of ``evaluator'' scripts, one for each task.
+These scripts include all code necessary to load in data, pre-process it, and compute all metrics for a given task.
+The evaluators allow for \mireval{} to be called directly from the command line so that no knowledge of Python is necessary.
+They are also distributed as executables for Windows and Mac OS X, so that \mireval{} may be used with no dependencies installed.
 

### 2014-05-06 paper/paper.tex
fix mirex acronym, add couple of sentences to melody discussion about resampling

@@
 % MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, not used outside of MIREX, etc.
-For the past 10 years, the yearly Music Information Retrieval EXchange (MIREX) has provided setting in which different MIR algorithms are compared over common datasets \cite{downie2008music}.
+For the past 10 years, the yearly Music Information Retrieval Evaluation eXchange (MIREX) has provided setting in which different MIR algorithms are compared over common datasets \cite{downie2008music}.
 By providing a standardized shared-task setting to track progress, MIREX has proven to be critically useful in the evolution of MIR research.
@@
 returned by \mireval{} are lower-bounded by the MIREX results and are, in our
-view, more accurate.
+view, more accurate. By default, the estimate is resampled using the reference's
+time grid so that the reference can be used without any modification.
+Alternatively, the user can specify a hop size, in which case both
+reference and estimate are resampled onto the new time-grid defined by the hop
+size.
 

### 2014-05-07 paper/paper.tex
Comparison section rough draft

@@
 
-% Compared each mir_eval task to an existing implementation
-% Parameterized the same wherever possible
+In order to validate the design choices made in \mireval{}, it is useful to compare the scores it reports to those reported by an existing evaluation system.
+Beyond pinpointing intentional differences in implementation, this process can also help find and fix bugs in either \mireval{} or the system it is being compared to.
+
+For each task covered by \mireval{}, we obtained a collection of reference and estimated annotations and computed a score for each metric using \mireval{} and the evaluation system being compared to.
+In order to facilitate comparison, we ensured that all parameters and pre-processing used by \mireval{} were equivalent to the reference system unless otherwise explicitly noted.
+Then, for each reported score, we computed the relative change between the scores as their absolute difference divided by their mean, or
+$$
+\frac{|s_m - s_c|}{(s_m + s_c)/2}
+$$
+where $s_m$ is the score reported by \mireval{}, and $s_c$ is the score being compared to.
+We then computed the average relative change across all examples in our dataset for each score.
+
+The resulting average relative change for each metric is presented in Table \ref{tab:comparison}.
+For may of the metrics, the average relative change is close to a tenth of a percent, indicating that \mireval{} is equivalent up to rounding/precision errors.
+In the following sections, we enumerate the existing system being compared to, the collections over which these scores were computed, and any known implementation differences which account for the larger average relative changes.
 

### 2014-05-07 paper/paper.tex
Onset section formatting, and capital F measure
Adding data for pattern because it's not retrievable
COmparison section fleshing out including beat metrics

@@
 As is also done in beat tracking and segment boundary detection, the primary method used to evaluate onset detectors is to first determine which estimated onsets are ``correct'', where correctness is defined as being within a small window of a reference onset \cite{bock2012evaluating}.
-From this, \textbf{precision}, \textbf{recall}, and \textbf{f-measure} scores are computed.
+From this, \textbf{precision}, \textbf{recall}, and \textbf{F-measure} scores are computed.
 
-\subsection{Blind Source Separation}
+\subsection{Source Separation}
 
@@
 $$
-where $s_m$ is the score reported by \mireval{}, and $s_c$ is the score being compared to.
-We then computed the average relative change across all examples in our dataset for each score.
+where $s_m$ is the score reported by \mireval{} and $s_c$ is the score being compared to.
+We then computed the average relative change across all examples in the obtained dataset for each score.
+
+For the beat detection, chord recognition, structural segmentation, and onset detection tasks, MIREX releases the the output of submitted algorithms, the ground truth annotations, and the reported score for each example in each data set.
+We therefore can directly compare \mireval{} to MIREX for these tasks by collecting all reference and estimated annotations, computing each metric for each example, and comparing the result to the score reported by MIREX.
+We chose to compare against the results reported in MIREX 2013 for all tasks.
+
+In contrast to the tasks above, MIREX does not release ground truth annotations or algorithm output for the melody extraction and pattern discovery tasks.
+As a result, we compared \mireval{}'s output on smaller development datasets for these tasks.
+For melody extraction, the ADC2004 dataset used by MIREX is publicly available.
+We performed melody extraction using the ``SG2'' algorithm evaluated in 2011 \cite{salamon2011melody} and compared \mireval{}'s reported scores to those of MIREX.
+For pattern discovery, we used the development dataset released by Collins \cite{Collins2013} and used the algorithms submitted by Nieto and Farbood \cite{nieto2013discovery} for MIREX 2013 to produce estimated patterns.
+We evaluated the estimated patterns using the MATLAB code released by Collins \cite{Collins2013}.
+The number of algorithms, examples, and total number of scores for all tasks are summarized in Table \ref{tab:nexamples}.
 
 The resulting average relative change for each metric is presented in Table \ref{tab:comparison}.
-For may of the metrics, the average relative change is close to a tenth of a percent, indicating that \mireval{} is equivalent up to rounding/precision errors.
-In the following sections, we enumerate the existing system being compared to, the collections over which these scores were computed, and any known implementation differences which account for the larger average relative changes.
+For may of the metrics, the average relative change is less than a few tenths of a percent, indicating that \mireval{} is equivalent up to rounding/precision errors.
+In the following sections, we enumerate the known implementation differences which account for the larger average relative changes.
+
+\subsection{Non-greedy matching of events}
+
+Brian writes this section
+
+\subsection{McKinney's P-score}
+
+When computing McKinney's P-score \cite{davies2009evaluation}, the beat sequences are first converted to impulse trains sampled at a 10 millisecond resolution.
+Because this sampling involves quantizing the beat times to a 10ms grid, shifting both beat sequences by a constant offset can result in substantial changes in the P-score.
+As a result, In \mireval{}, we normalize the beat sequences by subtracting from each reference and estimated beat location the minimum beat location in either series.
+In this way, the smallest beat in the estimated and reference beat sequences is always $0$ and the metric remains the same even when both beat sequences have a constant offset applied.
+This is not done in MIREX (which uses the Beat Evaluation Toolbox \cite{davies2009evaluation}), and as a result, we observe a considerable average relative change for the P-score metric.
+
+\subsection{Information Gain}
+
+The Information Gain metric \cite{davies2009evaluation} involves the computation a histogram of the per-beat errors.
+The Beat Evaluation Toolbox uses a non-uniform histogram binning where the first and last bins are 1/2 of the width of the rest of the bins.
+It also uses one more bin than is specified by the user.
+\mireval{} uses a standard uniformly-binned histogram with as many bins as are specified by the user.
+As a result, the Information Gain score reported by \mireval{} differs substantially from that reported by MIREX.
 
@@
   \cmidrule(lr){4-10}
-  AMLc       & AMLt       & D (bits) & Pat & Pat & Pat & Pat & Pat & Pat & Pat \\
-  0.137\% &    0.139\% &   10.166\% &  ??? & ??? & ??? & ??? & ??? & ??? & ???\\
+  AMLc       & AMLt       & In. Gain & Pat & Pat & Pat & Pat & Pat & Pat & Pat \\
+  0.137\% &    0.139\% &   9.174\% &  ??? & ??? & ??? & ??? & ??? & ??? & ???\\
   \midrule
@@
 
+% Community development is crucial
+
 \bibliography{mir_eval}

### 2014-05-07 paper/paper.tex
dpwe rework of title, abstract, intro

@@
 % ------
-\title{\mireval{}}
+\title{\mireval{}: A Transparent Codebase for Evaluating MIR}
 
@@
 We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
-In the present work, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to an existing implementation.
-When the score reported by \mireval{} differs substantially from the reference, we detail the differences in implementation.
+In this paper, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to  existing implementations.
+When the scores reported by \mireval{} differ substantially from the reference, we diagnose the differences in implementation.
 We also provide a brief overview of \mireval{}'s architecture, design, and intended use.
@@
 
-Many tasks in the field of Music Information Retrieval (MIR) involve the development of systems which can automatically produce semantic information about a piece of music.
-The effectiveness of these systems is typically determined based on how similarly they act to a human listener \cite{downie2003toward}.
-A straightforward way to determine a system's effectiveness would be for a human to study the output produced by the system and judge its correctness.
-However, this process is inherently subjective and also extremely time-consuming when evaluating a system's output over a large corpus of music.
+Much of the research in Music Information Retrieval (MIR) involves the development of systems that process raw music data to produce semantic information.
+The goal of these systems is frequently defined as attempting to duplicate the performance of a human listener given the same task \cite{downie2003toward}.
+A natural way to determine a system's effectiveness might be for a human to study the output produced by the system and judge its correctness.
+However, this would yield only subjective ratings, and would also be extremely time-consuming when evaluating a system's output over a large corpus of music.
 
-As a result, metrics have been defined for each task which provide a well-defined way of computing a score which denotes the correctness of a system's output.
+Instead, objective metrics are developed to provide a well-defined way of computing a score which indicates each system's output's correctness.
 These metrics typically involve a heuristically-motivated comparison of the system's output to a reference which is known to be correct.
 Over time, certain metrics have become standard for each task, so that the performance of systems created by different researchers can be compared when they are evaluated over the same dataset \cite{downie2003toward}.
-Unfortunately, this comparison can be confounded by the fact that the actual implementation of the metric can affect the scores it produces.
+Unfortunately, this comparison can be confounded by small details of the implementations or procedures that can have disproportionate impacts on the resulting scores.
 
 % MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, not used outside of MIREX, etc.
-For the past 10 years, the yearly Music Information Retrieval Evaluation eXchange (MIREX) has provided setting in which different MIR algorithms are compared over common datasets \cite{downie2008music}.
-By providing a standardized shared-task setting to track progress, MIREX has proven to be critically useful in the evolution of MIR research.
-MIREX relies on the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
-The NEMA codebase includes multiple programming languages and dependencies (including proprietary ones, e.g. MATLAB) so compiling and running it for research uses is nontrivial.
-
-Due to its scale, characteristics, and intended use, the NEMA system is rarely used for evaluating MIR algorithms outside of the setting of MIREX \cite{downie2008music}.
-As a result, researchers typically create their own implementations of common metrics for evaluating their algorithms.
-These implementations are not standardized, and even worse, may contain bugs.
-Both of these factors can confound comparison of different systems.
+For the past 10 years, the yearly Music Information Retrieval Evaluation eXchange (MIREX) has been a forum for comparing MIR algorithms over common datasets \cite{downie2008music}.
+By providing a standardized shared-task setting, MIREX has become critically useful to track progress in MIR research.
+MIREX is built upon the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
+The NEMA codebase includes multiple programming languages and dependencies (some of which, e.g. Matlab, are proprietary) so compiling and running it at individual sites is nontrivial. 
+%
+%Due to its scale, characteristics, and intended use, 
+In consequence, the NEMA system is rarely used for evaluating MIR algorithms outside of the setting of MIREX \cite{downie2008music}.
+Instead, researchers typically create their own implementations of common metrics for evaluating their algorithms.
+These implementations are thus not standardized, and may contain differences in details, or even bugs, that confound comparisons.
 
 These factors motivate the development of a standardized software package which implements the most common metrics used to evaluate MIR systems.
-Such a package should be straightforward to use and well-documented so that it can be easily adopted and understood by MIR researchers.
-In addition, it should be community-developed and transparently implemented so that all design decisions are well-reasoned and easily understood.
+Such a package should be straightforward to use and well-documented so that it 
+presents a preferable alternative to in-house development for MIR researchers.
+In addition, it should be community-developed and transparently implemented so that all design decisions are easily understood and open to discussion and improvement.
 
 Following these criteria, we present \mireval{}, a software package which intends to provide an easy and standardized way to evaluate MIR systems.
-The present work first discusses the architecture and design of \mireval{} in Section \ref{sec:architecture}.
-In Section \ref{sec:tasks}, we describe all of the tasks covered by \mireval{} and the metrics included.
+This paper first discusses the architecture and design of \mireval{} in Section \ref{sec:architecture}, then, in Section \ref{sec:tasks}, describes all of the tasks covered by \mireval{} and the metrics included.
 In order to validate our implementation decisions, we compare \mireval{} to existing software in Section \ref{sec:comparison}.

### 2014-05-07 paper/paper.tex
Can't change title or abstract

@@
 % ------
-\title{\mireval{}: A Transparent Codebase for Evaluating MIR}
+\title{\mireval{}}
 
@@
 We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
-In this paper, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to  existing implementations.
-When the scores reported by \mireval{} differ substantially from the reference, we diagnose the differences in implementation.
+In the present work, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to an existing implementation.
+When the score reported by \mireval{} differs substantially from the reference, we detail the differences in implementation.
 We also provide a brief overview of \mireval{}'s architecture, design, and intended use.

### 2014-05-08 paper/paper.tex
Wording
Added chord comparison numbers as a comment

--- 2014-05-07 paper/paper.tex
@@
 
-\usepackage{url}
-\usepackage{microtype}
-
 \def\eg{\emph{e.g.}}
@@
 
-\def\mireval{\texttt{mir\char`_eval}}
+\def\mireval{\texttt{mir\_eval}}
 
 % ------
-\title{\mireval{}}
+\title{mir\_eval}
 
@@
 Central to the field of MIR research is the evaluation of algorithms used to extract information from music data.
-We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
-In the present work, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to an existing implementation.
-When the score reported by \mireval{} differs substantially from the reference, we detail the differences in implementation.
-We also provide a brief overview of \mireval{}'s architecture, design, and intended use.
+We present mir\_eval, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
+In the present work, we enumerate the metrics implemented by mir\_eval and quantitatively compare each to an existing implementation.
+When the score reported by mir\_eval differs substantially from the reference, we detail the differences in implementation.
+We also provide a brief overview of mir\_eval's architecture, design, and intended use.
 \end{abstract}
@@
 
-Many tasks in the field of Music Information Retrieval (MIR) involve the development of systems which can automatically produce semantic information about a piece of music.
-The effectiveness of these systems is typically determined based on how similarly they act to a human listener \cite{downie2003toward}.
-A straightforward way to determine a system's effectiveness would be for a human to study the output produced by the system and judge its correctness.
-However, this process is inherently subjective and also extremely time-consuming when evaluating a system's output over a large corpus of music.
+% MIR intends to act like humans
+% Human evaluation is costly
+% Metrics are used as a proxy
 
-As a result, metrics have been defined for each task which provide a well-defined way of computing a score which denotes the correctness of a system's output.
-These metrics typically involve a heuristically-motivated comparison of the system's output to a reference which is known to be correct.
-Over time, certain metrics have become standard for each task, so that the performance of systems created by different researchers can be compared when they are evaluated over the same dataset \cite{downie2003toward}.
-Unfortunately, this comparison can be confounded by the fact that the actual implementation of the metric can affect the scores it produces.
+% Evaluation should be easy and standardized
+% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, etc.
+% As a result many different implementations of metrics, and implementation matters
+% mir_eval as the antidote to the above
 
-% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, not used outside of MIREX, etc.
-For the past 10 years, the yearly Music Information Retrieval Evaluation eXchange (MIREX) has provided setting in which different MIR algorithms are compared over common datasets \cite{downie2008music}.
-By providing a standardized shared-task setting to track progress, MIREX has proven to be critically useful in the evolution of MIR research.
-MIREX relies on the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
-The NEMA codebase includes multiple programming languages and dependencies (including proprietary ones, e.g. MATLAB) so compiling and running it for research uses is nontrivial.
+\section{mir\_eval's architecture}
 
-Due to its scale, characteristics, and intended use, the NEMA system is rarely used for evaluating MIR algorithms outside of the setting of MIREX \cite{downie2008music}.
-As a result, researchers typically create their own implementations of common metrics for evaluating their algorithms.
-These implementations are not standardized, and even worse, may contain bugs.
-Both of these factors can confound comparison of different systems.
+% Task submodules, one function per metric
+% io submodule for loading in data
+% Evaluators
 
-These factors motivate the development of a standardized software package which implements the most common metrics used to evaluate MIR systems.
-Such a package should be straightforward to use and well-documented so that it can be easily adopted and understood by MIR researchers.
-In addition, it should be community-developed and transparently implemented so that all design decisions are well-reasoned and easily understood.
-
-Following these criteria, we present \mireval{}, a software package which intends to provide an easy and standardized way to evaluate MIR systems.
-The present work first discusses the architecture and design of \mireval{} in Section \ref{sec:architecture}.
-In Section \ref{sec:tasks}, we describe all of the tasks covered by \mireval{} and the metrics included.
-In order to validate our implementation decisions, we compare \mireval{} to existing software in Section \ref{sec:comparison}.
-Finally, we discuss and summarize our contributions in Section \ref{sec:discussion}.
-
-\section{\mireval{}'s architecture}
-\label{sec:architecture}
-
-\mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord recognition, pattern discovery, structural segmentation, melody extraction, onset detection, and source separation.
-Each task is given its own submodule (e.g. \mireval{}\texttt{.beat}), and each metric is defined as a separate function in each submodule (e.g. \mireval{}\texttt{.beat.f\char`_measure}).
-Each task submodule also includes common data pre-processing steps for the task.
-Every metric function includes detailed documentation, example usage, input validation, and references to the original paper which defined the metric.
-\mireval{} also includes a submodule \texttt{io} which provides convenience functions for loading in task-specific data from common file formats.
-For readability, all code follows the PEP8 style guide\cite{van2001pep}.
-\mireval{}'s only dependencies outside of the Python standard library are the free and open-source SciPy/Numpy\cite{jones2001scipy} and scikit-learn\cite{pedregosa2011scikit} Python libraries.
-
-In order to simplify the usage of \mireval{}, it is packaged with a set of ``evaluator'' scripts, one for each task.
-These scripts include all code necessary to load in data, pre-process it, and compute all metrics for a given task.
-The evaluators allow for \mireval{} to be called directly from the command line so that no knowledge of Python is necessary.
-They are also distributed as executables for Windows and Mac OS X, so that \mireval{} may be used with no dependencies installed.
-
-\section{Tasks included in \mireval{}}
-\label{sec:tasks}
+\section{Tasks included in mir\_eval}
 
@@
 
-\mireval{} includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}:
-The \textbf{F-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat;
-\textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat;
-\textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met;
-\textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains;
-\textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct;
-and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.
+mir\_eval includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}: The \textbf{f-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat; \textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat; \textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met, \textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains; \textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct; and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.
 
@@
 
-\mireval{} implements the following MIREX-compatible boundary detection metrics:
+\mireval implements the following MIREX-compatible boundary detection metrics:
 \begin{description}
@@
 
-For this reason, the melody evaluator in \mireval{} uses $1^{st}$-order (linear)
+For this reason, the melody evaluator in mir\_eval uses $1^{st}$-order (linear)
 interpolation by default in order to map the reference and estimate sequences
@@
 using $1^{st}$-order rather than $0^{th}$-order interpolation means the results
-returned by \mireval{} are lower-bounded by the MIREX results and are, in our
-view, more accurate. By default, the estimate is resampled using the reference's
-time grid so that the reference can be used without any modification.
-Alternatively, the user can specify a hop size, in which case both
-reference and estimate are resampled onto the new time-grid defined by the hop
-size.
+returned by mir\_eval are lower-bounded by the MIREX results and are, in our
+view, more accurate.
 
@@
 As is also done in beat tracking and segment boundary detection, the primary method used to evaluate onset detectors is to first determine which estimated onsets are ``correct'', where correctness is defined as being within a small window of a reference onset \cite{bock2012evaluating}.
-From this, \textbf{precision}, \textbf{recall}, and \textbf{F-measure} scores are computed.
+From this, \textbf{precision}, \textbf{recall}, and \textbf{f-measure} scores are computed.
 
-\subsection{Source Separation}
+\subsection{Blind Source Separation}
 
 \section{Comparison to Existing Implementations}
-\label{sec:comparison}
 
-In order to validate the design choices made in \mireval{}, it is useful to compare the scores it reports to those reported by an existing evaluation system.
-Beyond pinpointing intentional differences in implementation, this process can also help find and fix bugs in either \mireval{} or the system it is being compared to.
-
-For each task covered by \mireval{}, we obtained a collection of reference and estimated annotations and computed a score for each metric using \mireval{} and the evaluation system being compared to.
-In order to facilitate comparison, we ensured that all parameters and pre-processing used by \mireval{} were equivalent to the reference system unless otherwise explicitly noted.
-Then, for each reported score, we computed the relative change between the scores as their absolute difference divided by their mean, or
-$$
-\frac{|s_m - s_c|}{(s_m + s_c)/2}
-$$
-where $s_m$ is the score reported by \mireval{} and $s_c$ is the score being compared to.
-We then computed the average relative change across all examples in the obtained dataset for each score.
-
-For the beat detection, chord recognition, structural segmentation, and onset detection tasks, MIREX releases the the output of submitted algorithms, the ground truth annotations, and the reported score for each example in each data set.
-We therefore can directly compare \mireval{} to MIREX for these tasks by collecting all reference and estimated annotations, computing each metric for each example, and comparing the result to the score reported by MIREX.
-We chose to compare against the results reported in MIREX 2013 for all tasks.
-
-In contrast to the tasks above, MIREX does not release ground truth annotations or algorithm output for the melody extraction and pattern discovery tasks.
-As a result, we compared \mireval{}'s output on smaller development datasets for these tasks.
-For melody extraction, the ADC2004 dataset used by MIREX is publicly available.
-We performed melody extraction using the ``SG2'' algorithm evaluated in 2011 \cite{salamon2011melody} and compared \mireval{}'s reported scores to those of MIREX.
-For pattern discovery, we used the development dataset released by Collins \cite{Collins2013} and used the algorithms submitted by Nieto and Farbood \cite{nieto2013discovery} for MIREX 2013 to produce estimated patterns.
-We evaluated the estimated patterns using the MATLAB code released by Collins \cite{Collins2013}.
-The number of algorithms, examples, and total number of scores for all tasks are summarized in Table \ref{tab:nexamples}.
-
-The resulting average relative change for each metric is presented in Table \ref{tab:comparison}.
-For may of the metrics, the average relative change is less than a few tenths of a percent, indicating that \mireval{} is equivalent up to rounding/precision errors.
-In the following sections, we enumerate the known implementation differences which account for the larger average relative changes.
-
-\subsection{Non-greedy matching of events}
-
-Brian writes this section
-
-\subsection{McKinney's P-score}
-
-When computing McKinney's P-score \cite{davies2009evaluation}, the beat sequences are first converted to impulse trains sampled at a 10 millisecond resolution.
-Because this sampling involves quantizing the beat times to a 10ms grid, shifting both beat sequences by a constant offset can result in substantial changes in the P-score.
-As a result, In \mireval{}, we normalize the beat sequences by subtracting from each reference and estimated beat location the minimum beat location in either series.
-In this way, the smallest beat in the estimated and reference beat sequences is always $0$ and the metric remains the same even when both beat sequences have a constant offset applied.
-This is not done in MIREX (which uses the Beat Evaluation Toolbox \cite{davies2009evaluation}), and as a result, we observe a considerable average relative change for the P-score metric.
-
-\subsection{Information Gain}
-
-The Information Gain metric \cite{davies2009evaluation} involves the computation a histogram of the per-beat errors.
-The Beat Evaluation Toolbox uses a non-uniform histogram binning where the first and last bins are 1/2 of the width of the rest of the bins.
-It also uses one more bin than is specified by the user.
-\mireval{} uses a standard uniformly-binned histogram with as many bins as are specified by the user.
-As a result, the Information Gain score reported by \mireval{} differs substantially from that reported by MIREX.
+% Compared each mir_eval task to an existing implementation
+% Parameterized the same wherever possible
 
@@
 
-% Beat - 9 metrics
-% Chord - 5 metrics
-% Segmentation - 14 metrics
-% Melody - 5 metrics
-% Pattern - 21 metrics
-% Onset - 3 metrics
-% Source Separation - 3 metrics
-
 \begin{table*}[t]
   \centering
-\begin{tabular}{c c c c c c c c c c}
+\begin{tabular}{c c c c c c c c c}
 \toprule
- \multicolumn{5}{ c }{Chord} & \multicolumn{5}{ c }{Melody}\\
+ \multicolumn{9}{ c }{Beat Tracking} \\
+  \cmidrule(lr){1-9}
+ F-Measure  &  Cemgil   &   Goto    &    P-score & CMLc     &     CMLt       &   AMLc     &     AMLt    &      D (bits)\\
+ 0.00659 & 0.00035 & 0.00060  & 0.00877 & 0.00157 & 0.00135 & 0.00137&  0.00135 & 0.10566\\
+  \midrule
+ \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{4}{ c }{Something else}  \\
   \cmidrule(lr){1-5}
-  \cmidrule(lr){5-10}
- Root & M/m & M/m + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Raw Chroma & Voicing R & Voicing F-A\\
- ??? & ??? & ??? & ??? & ??? & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
+  \cmidrule(lr){6-9}
+ Root  &  Maj/Min   &   Maj/Min + Inv    &     Sevenths     &     Sevenths + Inv & CMLt      &   AMLc     &     AMLt    &      D (bits)\\
+ ??? & ??? & ???  & ??? & ??? & 0.00135 & 0.00137&  0.00135 & 0.10566\\
+% [ 0.00686523,  0.16348339,  1.00519802,  0.48286893,  0.89935441]
   \midrule
- \multicolumn{10}{ c }{Segmentation} \\
-  \cmidrule(lr){1-10}
-  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5       & F@3 \\
-3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\% &    0.393\% \\
-  \midrule
- \multicolumn{4}{ c }{Segmentation} & \multicolumn{6}{ c }{Beat}\\
-  \cmidrule(lr){1-4}
-  \cmidrule(lr){5-10}
-  P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt \\
-  0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% \\
-  \midrule
- \multicolumn{3}{ c }{Beat} & \multicolumn{7}{ c }{Pattern}\\
+ \multicolumn{3}{ c }{Onset Detection} & \multicolumn{6}{ c }{Blah}  \\
   \cmidrule(lr){1-3}
-  \cmidrule(lr){4-10}
-  AMLc       & AMLt       & In. Gain & Pat & Pat & Pat & Pat & Pat & Pat & Pat \\
-  0.137\% &    0.139\% &   9.174\% &  ??? & ??? & ??? & ??? & ??? & ??? & ???\\
-  \midrule
- \multicolumn{10}{ c }{Pattern}\\
-  \cmidrule(lr){1-10}
-  Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat\\
-  ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ???\\
-  \midrule
- \multicolumn{4}{ c }{Pattern}  & \multicolumn{3}{ c }{Onset}  & \multicolumn{3}{ c }{Source Separation}\\
-  \cmidrule(lr){1-4}
-  \cmidrule(lr){5-7}
-  \cmidrule(lr){8-10}
- Pat & Pat & Pat & Pat & F-measure  & Precision  & Recall & SDR & SIR & SAR \\
- ??? & ??? & ??? & ??? &    0.165\% &    0.165\% &    0.165\% & ??? & ??? & ??? \\
+  \cmidrule(lr){4-9}
+ F-Measure  &  Precision   &  Recall    &     McKinney P-s & CMLc     &     CMLt       &   AMLc     &     AMLt    &      D (bits)\\
+ 0.00203 & 0.00202 & 0.00203  & 0.00877 & 0.00157 & 0.00135 & 0.00137&  0.00135 & 0.10566\\
   \bottomrule
@@
 \section{Discussion}
-\label{sec:discussion}
-
-% Community development is crucial
 

### 2014-05-08 paper/paper.tex

--- 2014-05-07 paper/paper.tex
@@
   \cmidrule(lr){1-5}
+
   \cmidrule(lr){5-10}
  Root & M/m & M/m + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Raw Chroma & Voicing R & Voicing F-A\\
- ??? & ??? & ??? & ??? & ??? & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
+  0.007 & 0.1634 & 1.005 & 0.483 & 0.899 & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
   \midrule

### 2014-05-08 paper/paper.tex
Significant clean-up to the chord description section ... hopefully short enough now

@@
 
-Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord recognition is an ongoing topic of discussion.
+Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord recognition is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{Peeters2013}.
 %For example, ISMIR 2010 saw the fondly dubbed ``Utrecht Agreement on Chord Evaluation''\footnote{http://www.music-ir.org/mirex/wiki/The\_Utrecht\_Agreement\_on\_Chord\_Evaluation}, in which interested researchers met to discuss sane ways of quantifying the performance of automatic chord recognition systems.
-Several recent articles address issues and concerns with vocabularies, comparison semantics, and other lexicographical challenges unique to chord recognition \cite{}.
-Ultimately, the source of this difficulty stems from the inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{McVicar}.
-As a result, a consensus has yet to be reached regarding the single best approach to comparing two sequences of chord labels, and instead are often compared over a set of rules, e.g Major-Minor, Sevenths, with or without inversions, and so on.
+One source of difficulty stems from an inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{McVicar}.
+As a result, a consensus has yet to be reached regarding the single best approach to comparing two sequences of chord labels, and instead are often compared over a set of rules, i.e Root, Major-Minor, and Sevenths, with or without inversions.
 
-Thanks to the previous efforts of Harte \cite{}, text representations of chord labels adhere to a standardized format, consisting of a root, quality, extensions, and a bass note; of these, only the root is strictly required.
-However, in order to efficiently compare chords in a variety of different ways, it is helpful to first translate a given chord label $\mathcal{C}$ into a numerical representation, shown in Figure \ref{}.
-In this example, a $G:7(9)/5$ is mapped to split into 4 pieces of information: one, the root is mapped to an absolute pitch class $\mathcal{R}$, in $[0, 11]$, where $C\to0$, $C\sharp/D\flat\to1$, etc; two, the quality is mapped to a root-invariant 12-dimensional bit vector $\mathcal{Q}$ by setting the scale degrees of the quality; three, any extensions are applied (via addition or omission) to the quality bit vector as scale degrees in a single octave, resulting in pitch vector $\mathcal{P}$; and four, the bass interval (5) is translated to the relative scale degree in semitones $\mathcal{B}$.
-Note that the add-9 is rolled into a single octave as an add-2.
-This is a matter of convenience as extended chords (9's, 11's or 13's) are traditionally resolved to a single-octave equivalent, but the bit-vector representation could be easily expanded to represent such information.
+To efficiently compare chords, we first translate a given chord label $\mathcal{C}$ into a numerical representation, based on the syntax of \cite{Harte2010}.
+For example, $G:maj(6)/5$ is mapped to three pieces of information: one, the root (``G'') is mapped to an absolute pitch class $\mathcal{R}$, in $[0, 11]$, where $C\to0$, $C\sharp/D\flat\to1$, etc; two, the quality shorthand (``maj'') and scale degrees (``6'') are mapped to a root-invariant bit vector $\mathcal{S}$ of active semitones; and three, the bass interval (``5'') is translated to the relative scale degree in semitones $\mathcal{B}$.
+%Traditionally, extended chords (9's, 11's or 13's) are not considered in evaluation and instead resolved to the tetrad contained therein, e.g. $C:9 \to C:7$, etc. 
+%This semitone bit-vector representation can, however, be easily expanded to represent such information in the future.
 
-Having gone through this bit of effort, it is now straightforward to compare chords along the five rules used in MIREX 2013:
-\begin{enumerate}
-\item Root:
-	\begin{enumerate}
-	\item $\mathcal{R}_{est} == \mathcal{R}_{ref}$
-	\item $\forall \mathcal{Q}_{ref}$
-	\end{enumerate}
-\item Major-Minor: Rule 1.a, plus
-	\begin{enumerate}
-	\item $\mathcal{Q}_{est} == \mathcal{Q}_{ref}$
-	\item $\mathcal{Q}_{ref} \in \{Maj, min\}$ 
-	\end{enumerate}
-\item Major-Minor w/Inversions: Rule 2, plus
-	\begin{enumerate}
-	\item $\mathcal{B}_{ref} \in \mathcal{Q}_{ref}$
-	\end{enumerate}
-\item Sevenths: Rule 1.1, plus
-	\begin{enumerate}
-	\item $\mathcal{Q}_{est} == \mathcal{Q}_{ref} $
-	\item $ \mathcal{Q}_{ref} \in \{Maj, min, Maj7, min7, 7\}$ 
-	\end{enumerate}
-\item Sevenths w/Inversions: Rule 4, plus
-	\begin{enumerate}
-	\item $\mathcal{B}_{ref} \in \mathcal{Q}_{ref}$ 
-	\end{enumerate}
-\end{enumerate}
+Based on this representation, we can symbolically define our interpretation of the five rules used in MIREX 2013\footnote{http://www.music-ir.org/mirex/wiki/2013:Audio\_Chord\_Estimation} to compare an estimated chord $\mathcal{C}_{est}$ with a reference $\mathcal{C}_{ref}$.
+\textbf{Root} is given by $\mathcal{R}_{est} == \mathcal{R}_{ref}$, for all chords.
+\textbf{Major-Minor} includes \textbf{Root}, plus $\mathcal{S}_{est} == \mathcal{S}_{ref}$ subject to $\mathcal{S}_{ref} \in \{Maj, min\}$.
+\textbf{Major-Minor-Inv} includes \textbf{Major-minor}, plus $\mathcal{B}_{est} == \mathcal{B}_{ref}$ subject to $\mathcal{B}_{ref} \in \mathcal{S}_{ref}$.
+\textbf{Sevenths} follows \textbf{Major-minor}, but is instead subject to $\mathcal{S}_{ref} \in \{Maj, min, Maj7, min7, 7, minmaj7\}$.
+Finally, \textbf{Sevenths-Inv} includes \textbf{Sevenths}, plus $\mathcal{B}_{est} == \mathcal{B}_{ref}$ subject to $\mathcal{B}_{ref} \in \mathcal{S}_{ref}$.
+Before proceeding, we draw attention to the set-inclusion conditions above, e.g.
+``subject to...'', meaning that a comparison is \emph{ignored} during evaluation if the given criteria is not satisfied.
 
-Following recent trends in MIREX, an overall score is computed by weighting each comparison by the duration of its interval, over all intervals; stated another way, this is the piecewise continuous-time integral of the intersection of two chord sequences, $(\mathbf{C}_{ref}, \mathbf{C}_{est})$, expressed as follows:
+Scores are computed by weighting each comparison by the duration of its interval, over all intervals; stated another way, this is the piecewise continuous-time integral of the equivalence of two chord sequences, $(\mathbf{C}_{ref}, \mathbf{C}_{est})$, expressed as follows:
 
@@
 
-\noindent Here, this is achieved here by forming the union of the boundaries in each sequence, and summing the time intervals of the correct ranges.
-Note that equivalence is subject to one of the rules defined previously.
-
-Finally, the total score over a set of $N$ items is given by a discrete summation, where the importance of each score, $S_n$, is weighted by the duration, $T_n$, of each annotation:
+\noindent This is achieved by forming the union of the boundaries in each sequence, and summing the time intervals of the ``correct'' ranges. 
+In practice, a cumulative score, $S_{total}$, is tallied over a set of $N$ items, i.e.
+audio files, by discrete summation, where the importance of each score, $S_n$, is weighted by the duration, $T_n$, of each annotation:
 

### 2014-05-08 paper/paper.tex
Revision revisions

--- 2014-05-08 paper/paper.tex
@@
 We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
-In the present work, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to an existing implementation.
-When the score reported by \mireval{} differs substantially from the reference, we detail the differences in implementation.
+In this paper, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to  existing implementations.
+When the scores reported by \mireval{} differ substantially from the reference, we detail the differences in implementation.
 We also provide a brief overview of \mireval{}'s architecture, design, and intended use.
@@
 In consequence, the NEMA system is rarely used for evaluating MIR algorithms outside of the setting of MIREX \cite{downie2008music}.
-Instead, researchers typically create their own implementations of common metrics for evaluating their algorithms.
+Instead, researchers often create their own implementations of common metrics for evaluating their algorithms.
 These implementations are thus not standardized, and may contain differences in details, or even bugs, that confound comparisons.
@@
 These factors motivate the development of a standardized software package which implements the most common metrics used to evaluate MIR systems.
-Such a package should be straightforward to use and well-documented so that it 
-presents a preferable alternative to in-house development for MIR researchers.
+Such a package should be straightforward to use and well-documented so that it can be easily adopted by MIR researchers.
 In addition, it should be community-developed and transparently implemented so that all design decisions are easily understood and open to discussion and improvement.
@@
   \cmidrule(lr){1-5}
-
   \cmidrule(lr){5-10}
  Root & M/m & M/m + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Raw Chroma & Voicing R & Voicing F-A\\
-  0.007 & 0.1634 & 1.005 & 0.483 & 0.899 & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
+ ??? & ??? & ??? & ??? & ??? & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
   \midrule

### 2014-05-08 paper/paper.tex
Removing source separation and updating table

@@
 
-\mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord recognition, pattern discovery, structural segmentation, melody extraction, onset detection, and source separation.
+\mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord recognition, pattern discovery, structural segmentation, melody extraction, and onset detection.
 Each task is given its own submodule (e.g. \mireval{}\texttt{.beat}), and each metric is defined as a separate function in each submodule (e.g. \mireval{}\texttt{.beat.f\char`_measure}).
@@
 
-\subsection{Source Separation}
-
 \section{Comparison to Existing Implementations}
@@
 % Pattern: Compared against development set, MATLAB code
-% Source Separation: Compared against SiSEC dev sets
 % Onset: Compared against MIREX 2013
@@
 % Melody - 5 metrics
-% Pattern - 21 metrics
 % Onset - 3 metrics
-% Source Separation - 3 metrics
 
@@
   \centering
+\begin{tabular}{c c c c c c c c c}
+\toprule
+ \multicolumn{9}{ c }{Beat Detection} \\
+  \cmidrule(lr){1-9}
+F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt       & AMLc       & AMLt       & In. Gain   \\
+   0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% &    0.137\% &    0.139\% &    9.174\% \\
+  \midrule
+\end{tabular}
+\begin{tabular}{c c c c c c c c c}
+ \multicolumn{9}{ c }{Structural Segmentation} \\
+  \cmidrule(lr){1-9}
+  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5  \\
+3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\%  \\
+  \midrule
+\end{tabular}
+\begin{tabular}{c c c c c c c c}
+ \multicolumn{5}{ c }{Structural Segmentation (continued)} & \multicolumn{3}{ c }{Onset Detection}\\
+  \cmidrule(lr){1-5}
+  \cmidrule(lr){6-8}
+  F@3 &   P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-measure  & Precision  & Recall     \\
+ 0.393\%  & 0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.165\% &    0.165\% &    0.165\% \\
+  \midrule
+\end{tabular}
 \begin{tabular}{c c c c c c c c c c}
-\toprule
- \multicolumn{5}{ c }{Chord} & \multicolumn{5}{ c }{Melody}\\
+ \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{5}{ c }{Melody Extraction}\\
   \cmidrule(lr){1-5}
-  \cmidrule(lr){5-10}
- Root & M/m & M/m + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Raw Chroma & Voicing R & Voicing F-A\\
+  \cmidrule(lr){6-10}
+  Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Chroma & Voicing R & Voicing FA \\
   ??? & ??? & ??? & ??? & ??? & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
-  \midrule
- \multicolumn{10}{ c }{Segmentation} \\
-  \cmidrule(lr){1-10}
-  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5       & F@3 \\
-3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\% &    0.393\% \\
-  \midrule
- \multicolumn{4}{ c }{Segmentation} & \multicolumn{6}{ c }{Beat}\\
-  \cmidrule(lr){1-4}
-  \cmidrule(lr){5-10}
-  P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt \\
-  0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% \\
-  \midrule
- \multicolumn{3}{ c }{Beat} & \multicolumn{7}{ c }{Pattern}\\
-  \cmidrule(lr){1-3}
-  \cmidrule(lr){4-10}
-  AMLc       & AMLt       & In. Gain & Pat & Pat & Pat & Pat & Pat & Pat & Pat \\
-  0.137\% &    0.139\% &   9.174\% &  ??? & ??? & ??? & ??? & ??? & ??? & ???\\
-  \midrule
- \multicolumn{10}{ c }{Pattern}\\
-  \cmidrule(lr){1-10}
-  Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat\\
-  ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ???\\
-  \midrule
- \multicolumn{4}{ c }{Pattern}  & \multicolumn{3}{ c }{Onset}  & \multicolumn{3}{ c }{Source Separation}\\
-  \cmidrule(lr){1-4}
-  \cmidrule(lr){5-7}
-  \cmidrule(lr){8-10}
- Pat & Pat & Pat & Pat & F-measure  & Precision  & Recall & SDR & SIR & SAR \\
- ??? & ??? & ??? & ??? &    0.165\% &    0.165\% &    0.165\% & ??? & ??? & ??? \\
   \bottomrule
-
 \end{tabular}

### 2014-05-08 paper/paper.tex
chord stuff is mostly done, methinks

--- 2014-05-08 paper/paper.tex
@@
 
-\subsection{Chord Recognition}
+\subsection{Chord Estimation}
 
@@
 
-Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord recognition is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{Peeters2013}.
+Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord estimation (ACE) is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{Peeters2013}.
 %For example, ISMIR 2010 saw the fondly dubbed ``Utrecht Agreement on Chord Evaluation''\footnote{http://www.music-ir.org/mirex/wiki/The\_Utrecht\_Agreement\_on\_Chord\_Evaluation}, in which interested researchers met to discuss sane ways of quantifying the performance of automatic chord recognition systems.
@@
 
-Scores are computed by weighting each comparison by the duration of its interval, over all intervals; stated another way, this is the piecewise continuous-time integral of the equivalence of two chord sequences, $(\mathbf{C}_{ref}, \mathbf{C}_{est})$, expressed as follows:
+Track-wise scores, $S_n$, are computed by weighting each comparison by the duration of its interval, over all intervals in an audio file; stated another way, this is the piecewise continuous-time integral of the equivalence of two chord sequences, $(\mathbf{C}_{ref}, \mathbf{C}_{est})$, expressed as follows:
 
 \begin{equation}
-S(\mathbf{C}_{ref}, \mathbf{C}_{est}) = \frac{1}{T}\int_{t=0}^{T} \mathcal{C}_{ref}(t) == \mathcal{C}_{est}(t)
+S_n(\mathbf{C}_{ref}, \mathbf{C}_{est}) = \frac{1}{T}\int_{t=0}^{T} \mathcal{C}_{ref}(t) == \mathcal{C}_{est}(t)
 \end{equation}
@@
 \noindent This is achieved by forming the union of the boundaries in each sequence, and summing the time intervals of the ``correct'' ranges. 
-In practice, a cumulative score, $S_{total}$, is tallied over a set of $N$ items, i.e.
+The cumulative score, referred to as \emph{weighted chord symbol recall} (WCSR), is tallied over a set of $N$ items, i.e.
 audio files, by discrete summation, where the importance of each score, $S_n$, is weighted by the duration, $T_n$, of each annotation:
@@
 \begin{equation}
-S_{total} = \frac{\sum_{n=0}^{N} T_n*S_n}{\sum_{n=0}^{N} T_n}
+WCSR_{total} = \frac{\sum_{n=0}^{N} T_n*S_n}{\sum_{n=0}^{N} T_n}
 \end{equation}
@@
 
+\subsection{Weighted Chord Symbol Recall}
+For reference, we compare our chord evaluation against the results provided from MIREX 2013.
+Though the \textbf{Root} comparison falls well within our accuracy tolerance, the other four comparison rules exhibit non-negligible discrepancies that warrant justification.
+Based on our current understanding, implementation differences are caused by two main sources of ambiguity.
+%Some interval mappings aren't well-defined.
+First, we find some chord labels in the MIREX reference annotations lack well-defined, i.e. singular, mappings into a comparison space. 
+One such example is $D:maj(*1)/\#1$.
+While the quality shorthand indicates ``major'', the asterisk implies the root is omitted and thus it is unclear whether $D:maj(*1)/\#1==D:maj1$.
+%Some chords get dropped in different scenarios, and we can't replicate the logic. 
+Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX. 
+This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{table:comparisons}. 
+For example, it seems as though $Bb:maj(9)/9$ was \emph{not} excluded from the MIREX evaluation, contradicting the description provided online.
+This chord alone causes an observable difference between the results of our implementation and previously reported results.
+
 % Beat: Compared against MIREX 2013
-% Chord: Compared against ??
 % Segmentation: Compared against ??
@@
 \begin{tabular}{c c c c c c c c c c}
+
 \toprule
@@
  Root & M/m & M/m + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Raw Chroma & Voicing R & Voicing F-A\\
-  0.007 & 0.1634 & 1.005 & 0.483 & 0.899 & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
+  0.007\% & 0.1634\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
   \midrule
@@
 \end{tabular}
+\label{table:comparisons}
 \end{table*}
@@
 % Community development is crucial
+As seen in the case of evaluating chord estimation systems, it is our hope that an open-source, publicly refined implementation might help resolve independently performed evaluation in the future. 
+Furthermore, the difficulty faced in attempting to match the MIREX chord evaluation precisely clearly demonstrates the need for transparency and community involvement in comparative evaluation.
+%; and two, we are curious as to how reliability of independently reported results in the literature.
 

### 2014-05-08 paper/paper.tex
Slightly more vague but more correct description of what MATLAB is doing.  It's not possible to explain it exactly without a lot of space.

--- 2014-05-08 paper/paper.tex
@@
 The Information Gain metric \cite{davies2009evaluation} involves the computation a histogram of the per-beat errors.
-The Beat Evaluation Toolbox uses a non-uniform histogram binning where the first and last bins are 1/2 of the width of the rest of the bins.
-It also uses one more bin than is specified by the user.
-\mireval{} uses a standard uniformly-binned histogram with as many bins as are specified by the user.
+The Beat Evaluation Toolbox uses a non-uniform histogram binning where the first, second and last bins are smaller than the rest of the bins while \mireval{} uses a standard uniformly-binned histogram.
 As a result, the Information Gain score reported by \mireval{} differs substantially from that reported by MIREX.

### 2014-05-08 paper/paper.tex
Not including pattern in table

@@
 The resulting average relative change for each metric is presented in Table \ref{tab:comparison}.
-For may of the metrics, the average relative change is less than a few tenths of a percent, indicating that \mireval{} is equivalent up to rounding/precision errors.
+The average relative change for all of the pattern discovery metrics was 0, so they are not included in this table.
+For many of the other metrics, the average relative change was less than a few tenths of a percent, indicating that \mireval{} is equivalent up to rounding/precision errors.
 In the following sections, we enumerate the known implementation differences which account for the larger average relative changes.

### 2014-05-08 paper/paper.tex
Filling out comparison section with places for people to put results

@@
 
-Brian writes this section
+Brian writes this section, which covers the differences in beat.f\_measure, boundary.detection, and onset.f\_measure
 
@@
 
-% Beat: Compared against MIREX 2013
-% Chord: Compared against ??
-% Segmentation: Compared against ??
-% Melody: Compared against MIREX 2011, SG2 only
-% Pattern: Compared against development set, MATLAB code
-% Onset: Compared against MIREX 2013
+\subsection{Other segmentation differences}
 
-% Beat - 9 metrics
-% Chord - 5 metrics
-% Segmentation - 14 metrics
-% Melody - 5 metrics
-% Onset - 3 metrics
+Brian renames this section and writes it/splits it into different sections.
+
+\subsection{Chord stuff}
+
+Eric renames this section and writes it/splits it into different sections
+
+\subsection{Voicing False Alarm Rate}
+
+When a reference melody annotation contains no unvoiced frames, the voicing false alarm rate is not well defined.
+MIREX assigns a score of 1 in this case, while \mireval{} assigns a score of 0.
+%%%
+%%%
+%%%
+% WHY?
+%%%
+%%%
+%%%
+In the data set over which the average relative change for the melody metrics was computed, one reference annotation contained no unvoiced frames.
+This discrepancy caused a large inflation of the average relative change reported for the voicing false alarm rate.
 
 \begin{table*}[t]
+\label{tab:comparison}
   \centering

### 2014-05-08 paper/paper.tex
Shortening melody section and changing content to match other sections

@@
 \subsection{Melody Extraction}
-\subsubsection{Task definition}
-Melody extraction algorithms aim to produce a sequence of frequency values
-corresponding to the pitch of the dominant melody from a musical recording
-\cite{salamon:MelodyReview:IEEESPM13}. The estimated pitch is represented as a
-time series of fundamental frequency ($f_0$) values in Hz sampled on a fixed
-time grid (e.g.~every 10 ms). To evaluate the estimated sequence, a reference
-sequence is generated by running a pitch tracker on the monophonic melody track
-(requiring access to the multi-track recording session) and manually correcting
-any mistakes made by the pitch tracker. The estimate is then evaluated against
-the reference by comparing the two frequency sequences on a frame-by-frame
-basis, and computing five global measures, first used in the MIREX 2005 AME
-evaluation \cite{polinerMelodyEval}. The goal of these measures, defined below,
-is to assess the algorithm's performance on two subtasks of melody extraction:
-(1) pitch estimation, i.e.~how well the algorithm estimates the pitch of the
-melody, and (2) voicing detection, i.e.~how well the algorithm determines when
-the melody is present in a frame (a \textit{voiced} frame) or absent (an
-\textit{unvoiced} frame). To allow evaluation of these two subtasks
-independently, a melody extraction algorithm can provide a frequency estimate
-even for frames it has determined to be unvoiced.
-
-\subsubsection{Evaluation measures}
-The following definitions are taken from
-\cite{salamon:MelodyReview:IEEESPM13} with permission from the authors. Let the estimated melody pitch frequency
-vector be $\mathbf{f}$, and the true sequence (reference) be $\mathbf{f}^*$. Let
-us also define a voicing indicator vector $\mathbf{v}$, whose $\tau^\text{th}$
-element $v_\tau = 1$ when a melody pitch is detected, with corresponding ground
-truth $\mathbf{v}^*$.  We also define an ``unvoicing'' indicator $\bar{v}_\tau =
-1 - v_\tau$.  Recall that an algorithm may report an estimated melody pitch
-($f_\tau > 0$) even for times where it reports no voicing ($v_\tau = 0$).   
-Then the measures are:
-\begin{itemize}
-  \item \textbf{Voicing Recall Rate}: The proportion of frames labeled as
-  melody frames in the reference that are estimated as melody frames by the
-  algorithm.
-\begin{equation}
-\text{Rec}_\text{vx} = \frac{\sum_\tau v_\tau v^*_\tau}{\sum_\tau v^*_\tau}
-\end{equation}
-
-  \item \textbf{Voicing False Alarm Rate}: The proportion of frames
-  labeled as non-melody in the reference that are mistakenly estimated as
-  melody frames by the algorithm.
-\begin{equation}
-\text{FA}_\text{vx} = \frac{\sum_\tau v_\tau \bar{v}^*_\tau}{\sum_\tau \bar{v}^*_\tau}
-\end{equation}
-
-  \item \textbf{Raw Pitch Accuracy}: The proportion of melody frames in the
-  reference for which $f_\tau$ is considered
-  correct (i.e.~within half a semitone of the ground
-  truth $f^*_\tau$).
-\begin{equation}
-\text{Acc}_\text{pitch}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] }{\sum_\tau v^*_\tau}
-\end{equation}
-where $\mathcal{T}$ is a threshold function defined by:
-\begin{equation}
-\mathcal{T}[a] = \begin{cases}
-1 \quad \text{if } |a| < 0.5 \\
-0 \quad \text{if } |a| \ge 0.5
-\end{cases}
-\end{equation}
-and $\mathcal{M}$ maps a frequency in Hertz to a melodic 
-axis as a real-valued number of semitones above an arbitrary
-reference frequency $f_\text{ref}$:
-\begin{equation}
-\mathcal{M}(f) = 12 \log_2\left( \frac{f}{f_\text{ref}} \right)
-\end{equation}
-
-  \item \textbf{Raw Chroma Accuracy}: As raw pitch accuracy, except
-  that both the estimated and reference $f_0$ sequences are mapped onto a
-  single octave. This gives a measure of pitch accuracy which ignores octave
-  errors, a common error made by melody extraction systems:
-\begin{equation}
-\text{Acc}_\text{chroma}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\left<\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau)\right>_{12} \right] }{\sum_\tau v^*_\tau}
-\end{equation}
-Octave equivalence is achieved by taking the difference between the semitone-scale pitch 
-values modulo 12 (one octave), where
-\begin{equation}
-\left<a\right>_{12} = a - 12 \lfloor \frac{a}{12} + 0.5 \rfloor .
-\end{equation}
-
-  \item \textbf{Overall Accuracy}: this measure combines the performance of the
-  pitch estimation and voicing detection tasks to give an overall performance
-  score for the system. It is defined as the proportion of all frames
-   correctly estimated by the algorithm, where for non-melody
-  frames this means the algorithm labeled them as non-melody, and for melody
-  frames the algorithm both labeled them as melody frames and provided a correct
-  $f_0$ estimate for the melody (i.e.~within half a semitone of the
-  reference):
-
-\begin{equation}
-\text{Acc}_\text{ov} 
-= \frac{1}{L} \sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] + \bar{v}^*_\tau \bar{v}_\tau 
-\end{equation}
-where $L$ is the total number of frames.
-\end{itemize}
-
-The performance of an algorithm on an entire music collection for a given
-measure is obtained by averaging the per-song scores for that measure over
-all songs in the collection.
-
-\subsubsection{Discussion}
-
-In the measure definitions provided above, it is assumed that both the estimate
-and reference sequences are sampled using the same time grid (hop size). In
-practice, however, this is not always the case, since the time grid of the
-reference depends on the hop size used by the pitch tracker that produced
-it, and similarly the time grid of the estimate depends on the specific melody
-extraction algorithm that produced it. This means that the sequences must be
-resampled onto a common time-grid prior to the computation of the measures. For
-the MIREX AME task, any sequence (be it reference or estimate) that is not
-sampled using a 10 ms hop size is resampled using $0^{th}$-order interpolation,
-i.e.~each frequency value in the target sequence is set to its nearest
-neighbour (in time) from the source sequence. This kind of interpolation can
-potentially have a detrimental effect on the evaluation, depending on the
-difference between the source and target time grids. In particular, it can
-result in artificially low scores for sequences with rapidly changing pitch
-values, such as opera singing with deep vibrato.
-
-For this reason, the melody evaluator in \mireval{} uses $1^{st}$-order (linear)
-interpolation by default in order to map the reference and estimate sequences
-onto a common time-grid. Assuming the original timestamps of both sequences
-correspond to the \textit{center} of each analysis frame (as they should),
-using $1^{st}$-order rather than $0^{th}$-order interpolation means the results
-returned by \mireval{} are lower-bounded by the MIREX results and are, in our
-view, more accurate. By default, the estimate is resampled using the reference's
-time grid so that the reference can be used without any modification.
-Alternatively, the user can specify a hop size, in which case both
-reference and estimate are resampled onto the new time-grid defined by the hop
-size.
+Melody extraction algorithms aim to produce a sequence of frequency values corresponding to the pitch of the dominant melody from a musical recording \cite{salamon:MelodyReview:IEEESPM13}.
+Melody annotations are represented as time series of fundamental frequency ($f_0$) values in Hz sampled at discrete points (``frames'') in time.
+An estimated pitch series is evaluated against a reference by computing the following five measures defined in \cite{salamon:MelodyReview:IEEESPM13}, first used in the MIREX 2005 Automatic Melody Extraction evaluation \cite{polinerMelodyEval}:
+\begin{description}
+  \item[Voicing Recall Rate:] The proportion of frames labeled as melody frames in the reference that are estimated as melody frames by the algorithm.
+  \item[Voicing False Alarm Rate:] The proportion of frames labeled as non-melody in the reference that are mistakenly estimated as melody frames by the algorithm.
+  \item[Raw Pitch Accuracy:] The proportion of melody frames in the reference for which the frequency is considered correct (i.e.~within half a semitone of the reference frequency).
+  \item[Raw Chroma Accuracy:] As raw pitch accuracy, except that both the estimated and reference $f_0$ sequences are mapped onto a single octave.
+  \item[Overall Accuracy:] The proportion of all frames correctly estimated by the algorithm, where for non-melody frames this means the algorithm labeled them as non-melody, and for melody frames the algorithm both labeled them as melody frames and provided a correct $f_0$ estimate for the melody (i.e.~within half a semitone of the reference).
+\end{description}
+Prior to computing the measure definitions provided above, both the estimate and reference sequences must be sampled on the same timebase.
 

### 2014-05-08 paper/paper.tex
Segmentation section formatting

@@
 
-\subsection{Segmentation}
+\subsection{Structural Segmentation}
 
-Evaluation criteria for segmentation fall into two categories: boundary annotation, and structural annotation.
-\emph{Boundary annotation} is the task of predicting the times at which structural changes occur, such as when a \emph{verse} transitions to a \emph{refrain}.
-\emph{Structural annotation} is the task of assigning labels to detected segments.  
+Evaluation criteria for structural segmentation fall into two categories: boundary annotation and structural annotation.
+Boundary annotation is the task of predicting the times at which structural changes occur, such as when a verse transitions to a refrain.
+Structural annotation is the task of assigning labels to detected segments.
 The estimated labels may be arbitrary strings --- such as $A$, $B$, $C$, \etc{} --- and they need not describe functional concepts.
+In both tasks, we assume that annotations express a partitioning of the track into intervals.
 
-In both tasks, we assume that annotations express a partitioning of the track 
-into intervals ${(s_i, t_i)}_{i=1}^m$, where $s_0=0$ denotes the beginning of track, 
-$t_m$ denotes the end of the track, and $t_i = s_{i+1}$.
-Structural annotation additionally requires that each interval be assigned a label $y_i$.
-
-\mireval{} implements the following MIREX-compatible boundary detection metrics:
+\mireval{} implements the following boundary detection metrics:
 \begin{description}
-\item[Boundary detection:] precision, recall, and F-measure for detecting boundary
-events within a tolerance window $w\in \{0.5, 3\}$~\cite{turnbull2007supervised};
-\item[Boundary deviation:] median absolute time difference from a reference boundary
-to its nearest estimated boundary, and vice versa~\cite{turnbull2007supervised},
+\item[Boundary detection:] precision, recall, and F-measure scores where an estimated boundary is considered correct if it falls within a window around a reference boundary ~\cite{turnbull2007supervised};
+\item[Boundary deviation:] median absolute time difference from a reference boundary to its nearest estimated boundary, and vice versa~\cite{turnbull2007supervised},
 \end{description}
-and the following structure annotation metrics
+and the following structure annotation metrics:
 \begin{description}
-\item[Pairwise classification:] precision, recall, and F-measure for classifying pairs
-of sampled time instants as belonging to the same structural
-component~\cite{levy2008structural};
-\item[Rand index:\footnote{The MIREX results page refers to Rand index as ``random
-clustering index''.}] reference and estimated annotations are sampled uniformly
-throughout the track, and the induced clusterings are compared by the Rand index
-~\cite{rand1971objective};
-\item[Normalized conditional entropy:] reference and estimated labels are sampled
-uniformly, and interpreted as samples of random variables $Y_R, Y_E$, which are
-computed by estimating the conditional entropy of $Y_R$ given $Y_E$
-(\emph{under-segmentation}) and $Y_E$ given $Y_R$ 
-(\emph{over-segmentation})~\cite{lukashevich2008towards}.
+\item[Pairwise classification:] precision, recall, and F-measure for classifying pairs of sampled time instants as belonging to the same structural component~\cite{levy2008structural};
+\item[Rand index:] reference and estimated annotations are sampled uniformly throughout the track, and the induced clusterings are compared by the Rand index ~\cite{rand1971objective};
+\footnote{The MIREX results page refers to Rand index as ``random clustering index''.}
+\item[Normalized conditional entropy:] reference and estimated labels are sampled uniformly, and interpreted as samples of random variables $Y_R, Y_E$, which are computed by estimating the conditional entropy of $Y_R$ given $Y_E$ (\emph{under-segmentation}) and $Y_E$ given $Y_R$  (\emph{over-segmentation})~\cite{lukashevich2008towards}.
 \end{description}
-
-% \subsubsection{Boundary annotation}
-
-% Within boundary annotation, there are two categories of evaluation metrics: detection,
-% and deviation~\cite{turnbull2007supervised}.
-
-% \emph{Boundary detection} measures the precision, recall, and F-measure of boundary prediction within a window.
-% Let $B^R$ ($B^E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
-% a window, typically either $0.5$s or $3.0$s.  
-% A \emph{hit} is defined as a pair $b_e \in B^E$, $b_r \in B^R$ such that $|b_e - b_r|
-% \leq W$.
-
-% No estimated boundary is counted as a hit for more than one reference boundary, and vice versa.
-% This is accomplished by computing a maximum bipartite matching $H_W$ between $B^E$ and $B^R$ (subject to the window constraint $W$)
-% using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  This deviates from the greedy heuristic used in the MIREX
-% implementation, but it is guaranteed to produce a correct matching.  Precision and recall at window $W$ are defined as
-% \begin{align}
-% P_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^E|}\\
-% R_W(B^R, B^E) &\defeq \frac{|H_W|}{|B^R|},
-% \end{align}
-% and the corresponding F-measure is defined by taking their harmonic mean.
-
-% \emph{Boundary deviation} is comprised of two scores, which measure the median time between a reference boundary and its nearest corresponding estimated boundary, and vice versa.
-% These two metrics have previously been defined as \emph{true-to-predicted} (T-to-P) and \emph{predicted-to-true} (P-to-T), though in the terminology of this document, we use 
-% alternative naming of \emph{reference-to-estimated} (R-to-E) and \emph{estimated-to-reference} (E-to-R):
-% \begin{align}
-% \text{R-to-E}(B^R, B^E) &\defeq \displaystyle\median_{b_r \in B^R} \min_{b_e \in B^E} \left|b_r - b_e\right|\\
-% \text{E-to-R}(B^R, B^E) &\defeq \displaystyle\median_{b_e \in B^E} \min_{b_r \in B^R} \left|b_r - b_e\right|.
-% \end{align}
-
-% \subsubsection{Structural annotation}
-% Two standard methods of evaluating structural annotation accuracy are \emph{pairwise classification}~\cite{levy2008structural}
-% and conditional entropy~\cite{lukashevich2008towards}.  In both methods, a collection of samples are generated by sampling the
-% labels at time steps between $0$ and the track duration.  The $i$th sample is assigned a reference label $y_i^R$ and
-% and estimated label $y_i^E$.  Our implementation follows the MIREX guidelines, and generates samples at a default rate of 10Hz.
-
-% Reference and estimated annotations must span identical time durations for annotation metrics to be well-defined.
-% This is accomplished in our implementation by trimming or padding the estimated annotation to exactly match the start and end-times
-% reported in the reference annotation, and synthesizing unique labels if necessary.
-
-% Given the labels for the samples $\{(y_i^R, y_i^E)\}_{i=1}^n$, the \emph{pairwise classification} metrics are defined as precision,
-% recall, and F-measure of label agreement over all unique, distinct pairs $i \neq j$.  
-% Let $A_R = \{ \{i, j\} \given y_i^R = y_j^R\}$ denote the set of similarly labeled frames in the reference, with $A_E$ defined
-% analogously for the estimation.  Precision and recall are defined as
-% \begin{align}
-% P_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_E| }\\
-% R_\text{pair} &\defeq \frac{ |A_E \cap A_R| }{ |A_R| }.
-% \end{align}
-
-% \emph{Normalized conditional entropy} scores are computed by estimating the conditional entropy of the estimated label $y^E$ given
-% the reference label $y^R$ and vice versa.  Let $P$ denote the empirical joint distribution over reference and estimated labels:
-% \begin{align}
-% P_{ij} &\propto \left|\{t \given y_t^R = i \wedge y_t^E = j\}\right|.
-% \end{align}
-% Let $Y^R$ and $Y^E$ denote random variables corresponding to the reference and estimated label for an arbitrary sample.
-% The conditional entropies $H\left(Y^E \given Y^R\right)$ and $H\left(Y^R \given Y^E\right)$ are estimated from the 
-% empirical marginals ${p_i^R = \sum_j P_{ij}}$ and ${p_j^E = \sum_i P_{ij}}$ as described by 
-% Lukashevich~\cite{lukashevich2008towards}.
-
-% The final scores are defined as \emph{over-segmentation} ($S_\text{O}$) and \emph{under-segmentation} ($S_\text{U}$):
-% \begin{align}
-% S_\text{O} &\defeq 1 - \frac{H(E \given R)}{\log_2 |\ell^E|}\\
-% S_\text{U} &\defeq 1 - \frac{H(R \given E)}{\log_2 |\ell^R|},
-% \end{align}
-% where $\ell^R$ and $\ell^E$ denote the sets of unique label values given in the reference and estimation.
 

### 2014-05-08 paper/paper.tex
Full width table
Moving table up
Wording in pattern section

@@
 \usepackage{microtype}
+\usepackage{tabularx}
 
@@
 
-This task aims to evaluate algorithms that identify musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
-Given the novelty of this task \footnote{The first year to appear on MIREX was 2013.}, the evaluation metrics are likely to be modified in further editions.
-Nonetheless, Collins put together all the previously existent metrics and a few new ones for this task in its first appearance in MIREX\cite{Collins2013}, which resulted in 19 different scores, each one (except for the two that evaluate the algorithm execution time) implemented in MIR-eval and described below:
+Pattern discovery involves the identification of musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
+The metrics used to evaluation pattern discovery systems attempt to quantify the ability of the algorithm to not only determine the presents pattern in a piece, but also to find all of their occurrences.
+Given the novelty of this task (the first year it appeared in MIREX was 2013), the evaluation metrics are likely to be modified in further editions.
+Nonetheless, Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013}, which resulted in 19 different scores, each one implemented in \mireval{} and described below:
 
-\begin{itemize}
-    \item
-      \textbf{Standard F-measure, Precision, and Recall (F$_1$, P, R)}: This metric, composed of three scores, checks if the prototype patterns of the reference match possible key-transposed patterns in the prototype patterns of the estimations.
-      Since the sizes of these prototypes must be equal, this metric is quite restrictive and it tends to be 0 most of the time (see 2013 MIREX results).
-    \item
-      \textbf{Establishment F-measure, Precision, and Recall (F1$_{est}$, P$_{est}$, R$_{est}$)}: These scores evaluate the amount of patterns that were successfully identified by the estimated results, no matter how many occurrences they found.
-      In other words, this metric captures the ability of the algorithm to \textit{establish} that the estimated patterns are actually contained in the reference annotation.
-    \item 
-      \textbf{Occurrence F-measure, Precision, and Recall (F1$_{occ}$, P$_{occ}$, R$_{occ}$)}: Independently of how many patterns were correctly established, we may also want to know how well the algorithm finds all their respective occurrences throughout the piece.
+\begin{description}
+\item[Standard F-measure, Precision, and Recall:] An estimated pattern is considered correct only if it matches (up to translation) a reference prototype pattern.
+\item[Establishment F-measure, Precision, and Recall:] Computes the number of reference patterns that were successfully found, no matter how many occurrences were found.
+      In other words, these metrics capture the ability of the algorithm to \textit{establish} the patterns in a piece.
+\item[Occurrence F-measure, Precision, and Recall:] Measures whether an algorithm is able to retrieve all occurrences of a pattern.
       This metric aims to quantize this \textit{occurrence} retrieval quality of the algorithm.
-      This metric has a tolerance parameter $c$ to allow differences when evaluating the similarity between occurrences, and in MIREX they use $c=.75$ and $c=.5$.
-    \item
-      \textbf{Three-layer F-measure, Precision, and Recall (TLF$_1$, P$_3$, R$_3$)}: These scores can be seen as an improved version of the standard metrics.
-      They capture both the establishment of the patterns and the occurrence retrieval in a single set of scores, being more permissive than the standard evaluation.
-    \item
-      \textbf{First $N$ patterns metrics (FFTP$_{est}$, FFP)}: This includes the first $N$ patterns target proportion establishment recall, and the first $N$ patterns three-layer precision. 
-      By analyzing the first $N$ patterns only, we evaluate the ability of the algorithm of sorting the identified patterns based on their relevance. 
-      In MIREX, $N=5$.
-
-\end{itemize}
+\item[Three-layer F-measure, Precision, and Recall:] These metrics capture both the establishment of the patterns and the occurrence retrieval in a single set of scores.
+\item[First $N$ patterns metrics:] The target proportion establishment recall and three-layer precision analyzing the first $N$ patterns only, which measures the ability of the algorithm to sort the identified patterns based on their relevance.
+\end{description}
 
@@
 
+\begin{table*}[htb]
+\label{tab:comparison}
+  \centering
+\begin{tabularx}{\linewidth}{c *{8}{>{\centering\arraybackslash}X}}
+\toprule
+ \multicolumn{9}{ c }{Beat Detection} \\
+  \cmidrule(lr){1-9}
+F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt       & AMLc       & AMLt       & In. Gain   \\
+   0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% &    0.137\% &    0.139\% &    9.174\% \\
+  \midrule
+\end{tabularx}
+\begin{tabularx}{\linewidth}{c c c c c *{4}{>{\centering\arraybackslash}X}}
+ \multicolumn{9}{ c }{Structural Segmentation} \\
+  \cmidrule(lr){1-9}
+  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5  \\
+3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\%  \\
+  \midrule
+\end{tabularx}
+\begin{tabularx}{\linewidth}{*{8}{>{\centering\arraybackslash}X}}
+ \multicolumn{5}{ c }{Structural Segmentation (continued)} & \multicolumn{3}{ c }{Onset Detection}\\
+  \cmidrule(lr){1-5}
+  \cmidrule(lr){6-8}
+  F@3 &   P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-measure  & Precision  & Recall     \\
+ 0.393\%  & 0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.165\% &    0.165\% &    0.165\% \\
+  \midrule
+\end{tabularx}
+\begin{tabularx}{\linewidth}{*{2}{>{\centering\arraybackslash}X} c c c c c c c c}
+ \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{5}{ c }{Melody Extraction}\\
+  \cmidrule(lr){1-5}
+  \cmidrule(lr){6-10}
+  Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Chroma & Voicing R & Voicing FA \\
+  ??? & ??? & ??? & ??? & ??? & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
+  \bottomrule
+\end{tabularx}
+\end{table*}
+
 \subsection{Non-greedy matching of events}
@@
 
-\begin{table*}[t]
-\label{tab:comparison}
-  \centering
-\begin{tabular}{c c c c c c c c c}
-\toprule
- \multicolumn{9}{ c }{Beat Detection} \\
-  \cmidrule(lr){1-9}
-F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt       & AMLc       & AMLt       & In. Gain   \\
-   0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% &    0.137\% &    0.139\% &    9.174\% \\
-  \midrule
-\end{tabular}
-\begin{tabular}{c c c c c c c c c}
- \multicolumn{9}{ c }{Structural Segmentation} \\
-  \cmidrule(lr){1-9}
-  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5  \\
-3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\%  \\
-  \midrule
-\end{tabular}
-\begin{tabular}{c c c c c c c c}
- \multicolumn{5}{ c }{Structural Segmentation (continued)} & \multicolumn{3}{ c }{Onset Detection}\\
-  \cmidrule(lr){1-5}
-  \cmidrule(lr){6-8}
-  F@3 &   P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-measure  & Precision  & Recall     \\
- 0.393\%  & 0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.165\% &    0.165\% &    0.165\% \\
-  \midrule
-\end{tabular}
-\begin{tabular}{c c c c c c c c c c}
- \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{5}{ c }{Melody Extraction}\\
-  \cmidrule(lr){1-5}
-  \cmidrule(lr){6-10}
-  Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Chroma & Voicing R & Voicing FA \\
-  ??? & ??? & ??? & ??? & ??? & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
-  \bottomrule
-\end{tabular}
-\end{table*}
-
 \section{Discussion}

### 2014-05-08 paper/paper.tex

@@
 
-Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord recognition is an ongoing topic of discussion.
+Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord estimation (ACE) is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{Peeters2013}.
 %For example, ISMIR 2010 saw the fondly dubbed ``Utrecht Agreement on Chord Evaluation''\footnote{http://www.music-ir.org/mirex/wiki/The\_Utrecht\_Agreement\_on\_Chord\_Evaluation}, in which interested researchers met to discuss sane ways of quantifying the performance of automatic chord recognition systems.
-Several recent articles address issues and concerns with vocabularies, comparison semantics, and other lexicographical challenges unique to chord recognition \cite{}.
-Ultimately, the source of this difficulty stems from the inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{McVicar}.
-As a result, a consensus has yet to be reached regarding the single best approach to comparing two sequences of chord labels, and instead are often compared over a set of rules, e.g Major-Minor, Sevenths, with or without inversions, and so on.
+One source of difficulty stems from an inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{McVicar}.
+As a result, a consensus has yet to be reached regarding the single best approach to comparing two sequences of chord labels, and instead are often compared over a set of rules, i.e Root, Major-Minor, and Sevenths, with or without inversions.
 
-Thanks to the previous efforts of Harte \cite{}, text representations of chord labels adhere to a standardized format, consisting of a root, quality, extensions, and a bass note; of these, only the root is strictly required.
-However, in order to efficiently compare chords in a variety of different ways, it is helpful to first translate a given chord label $\mathcal{C}$ into a numerical representation, shown in Figure \ref{}.
-In this example, a $G:7(9)/5$ is mapped to split into 4 pieces of information: one, the root is mapped to an absolute pitch class $\mathcal{R}$, in $[0, 11]$, where $C\to0$, $C\sharp/D\flat\to1$, etc; two, the quality is mapped to a root-invariant 12-dimensional bit vector $\mathcal{Q}$ by setting the scale degrees of the quality; three, any extensions are applied (via addition or omission) to the quality bit vector as scale degrees in a single octave, resulting in pitch vector $\mathcal{P}$; and four, the bass interval (5) is translated to the relative scale degree in semitones $\mathcal{B}$.
-Note that the add-9 is rolled into a single octave as an add-2.
-This is a matter of convenience as extended chords (9's, 11's or 13's) are traditionally resolved to a single-octave equivalent, but the bit-vector representation could be easily expanded to represent such information.
+To efficiently compare chords, we first translate a given chord label $\mathcal{C}$ into a numerical representation, based on the syntax of \cite{Harte2010}.
+For example, $G:maj(6)/5$ is mapped to three pieces of information: one, the root (``G'') is mapped to an absolute pitch class $\mathcal{R}$, in $[0, 11]$, where $C\to0$, $C\sharp/D\flat\to1$, etc; two, the quality shorthand (``maj'') and scale degrees (``6'') are mapped to a root-invariant bit vector $\mathcal{S}$ of active semitones; and three, the bass interval (``5'') is translated to the relative scale degree in semitones $\mathcal{B}$.
+%Traditionally, extended chords (9's, 11's or 13's) are not considered in evaluation and instead resolved to the tetrad contained therein, e.g. $C:9 \to C:7$, etc. 
+%This semitone bit-vector representation can, however, be easily expanded to represent such information in the future.
 
-Having gone through this bit of effort, it is now straightforward to compare chords along the five rules used in MIREX 2013:
-\begin{enumerate}
-\item Root:
-	\begin{enumerate}
-	\item $\mathcal{R}_{est} == \mathcal{R}_{ref}$
-	\item $\forall \mathcal{Q}_{ref}$
-	\end{enumerate}
-\item Major-Minor: Rule 1.a, plus
-	\begin{enumerate}
-	\item $\mathcal{Q}_{est} == \mathcal{Q}_{ref}$
-	\item $\mathcal{Q}_{ref} \in \{Maj, min\}$ 
-	\end{enumerate}
-\item Major-Minor w/Inversions: Rule 2, plus
-	\begin{enumerate}
-	\item $\mathcal{B}_{ref} \in \mathcal{Q}_{ref}$
-	\end{enumerate}
-\item Sevenths: Rule 1.1, plus
-	\begin{enumerate}
-	\item $\mathcal{Q}_{est} == \mathcal{Q}_{ref} $
-	\item $ \mathcal{Q}_{ref} \in \{Maj, min, Maj7, min7, 7\}$ 
-	\end{enumerate}
-\item Sevenths w/Inversions: Rule 4, plus
-	\begin{enumerate}
-	\item $\mathcal{B}_{ref} \in \mathcal{Q}_{ref}$ 
-	\end{enumerate}
-\end{enumerate}
+Based on this representation, we can symbolically define our interpretation of the five rules used in MIREX 2013\footnote{http://www.music-ir.org/mirex/wiki/2013:Audio\_Chord\_Estimation} to compare an estimated chord $\mathcal{C}_{est}$ with a reference $\mathcal{C}_{ref}$.
+\textbf{Root} is given by $\mathcal{R}_{est} == \mathcal{R}_{ref}$, for all chords.
+\textbf{Major-Minor} includes \textbf{Root}, plus $\mathcal{S}_{est} == \mathcal{S}_{ref}$ subject to $\mathcal{S}_{ref} \in \{Maj, min\}$.
+\textbf{Major-Minor-Inv} includes \textbf{Major-minor}, plus $\mathcal{B}_{est} == \mathcal{B}_{ref}$ subject to $\mathcal{B}_{ref} \in \mathcal{S}_{ref}$.
+\textbf{Sevenths} follows \textbf{Major-minor}, but is instead subject to $\mathcal{S}_{ref} \in \{Maj, min, Maj7, min7, 7, minmaj7\}$.
+Finally, \textbf{Sevenths-Inv} includes \textbf{Sevenths}, plus $\mathcal{B}_{est} == \mathcal{B}_{ref}$ subject to $\mathcal{B}_{ref} \in \mathcal{S}_{ref}$.
+Before proceeding, we draw attention to the set-inclusion conditions above, e.g.
+``subject to...'', meaning that a comparison is \emph{ignored} during evaluation if the given criteria is not satisfied.
 
-Following recent trends in MIREX, an overall score is computed by weighting each comparison by the duration of its interval, over all intervals; stated another way, this is the piecewise continuous-time integral of the intersection of two chord sequences, $(\mathbf{C}_{ref}, \mathbf{C}_{est})$, expressed as follows:
+Track-wise scores, $S_n$, are computed by weighting each comparison by the duration of its interval, over all intervals in an audio file; stated another way, this is the piecewise continuous-time integral of the equivalence of two chord sequences, $(\mathbf{C}_{ref}, \mathbf{C}_{est})$, expressed as follows:
 
 \begin{equation}
-S(\mathbf{C}_{ref}, \mathbf{C}_{est}) = \frac{1}{T}\int_{t=0}^{T} \mathcal{C}_{ref}(t) == \mathcal{C}_{est}(t)
+S_n(\mathbf{C}_{ref}, \mathbf{C}_{est}) = \frac{1}{T}\int_{t=0}^{T} \mathcal{C}_{ref}(t) == \mathcal{C}_{est}(t)
 \end{equation}
 
-\noindent Here, this is achieved here by forming the union of the boundaries in each sequence, and summing the time intervals of the correct ranges.
-Note that equivalence is subject to one of the rules defined previously.
-
-Finally, the total score over a set of $N$ items is given by a discrete summation, where the importance of each score, $S_n$, is weighted by the duration, $T_n$, of each annotation:
+\noindent This is achieved by forming the union of the boundaries in each sequence, and summing the time intervals of the ``correct'' ranges. 
+The cumulative score, referred to as \emph{weighted chord symbol recall} (WCSR), is tallied over a set of $N$ items, i.e.
+audio files, by discrete summation, where the importance of each score, $S_n$, is weighted by the duration, $T_n$, of each annotation:
 
 \begin{equation}
-S_{total} = \frac{\sum_{n=0}^{N} T_n*S_n}{\sum_{n=0}^{N} T_n}
+WCSR_{total} = \frac{\sum_{n=0}^{N} T_n*S_n}{\sum_{n=0}^{N} T_n}
 \end{equation}
@@
   Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Chroma & Voicing R & Voicing FA \\
-  ??? & ??? & ??? & ??? & ??? & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
+ 0.007\% & 0.1634\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
   \bottomrule
@@
 
+\subsection{Weighted Chord Symbol Recall}
+For reference, we compare our chord evaluation against the results provided from MIREX 2013.
+Though the \textbf{Root} comparison falls well within our accuracy tolerance, the other four comparison rules exhibit non-negligible discrepancies that warrant justification.
+Based on our current understanding, implementation differences are caused by two main sources of ambiguity.
+%Some interval mappings aren't well-defined.
+First, we find some chord labels in the MIREX reference annotations lack well-defined, i.e. singular, mappings into a comparison space. 
+One such example is $D:maj(*1)/\#1$.
+While the quality shorthand indicates ``major'', the asterisk implies the root is omitted and thus it is unclear whether $D:maj(*1)/\#1==D:maj1$.
+%Some chords get dropped in different scenarios, and we can't replicate the logic. 
+Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX. 
+This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{table:comparisons}. 
+For example, it seems as though $Bb:maj(9)/9$ was \emph{not} excluded from the MIREX evaluation, contradicting the description provided online.
+This chord alone causes an observable difference between the results of our implementation and previously reported results.
+
+% Beat: Compared against MIREX 2013
+% Segmentation: Compared against ??
+% Melody: Compared against MIREX 2011, SG2 only
+% Pattern: Compared against development set, MATLAB code
+% Source Separation: Compared against SiSEC dev sets
+% Onset: Compared against MIREX 2013
+
+% Beat - 9 metrics
+% Chord - 5 metrics
+% Segmentation - 14 metrics
+% Melody - 5 metrics
+% Pattern - 21 metrics
+% Onset - 3 metrics
+% Source Separation - 3 metrics
+
+\begin{table*}[t]
+  \centering
+\begin{tabular}{c c c c c c c c c c}
+
+\toprule
+ \multicolumn{5}{ c }{Chord} & \multicolumn{5}{ c }{Melody}\\
+  \cmidrule(lr){1-5}
+
+  \cmidrule(lr){5-10}
+ Root & M/m & M/m + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Raw Chroma & Voicing R & Voicing F-A\\
+  0.007\% & 0.1634\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
+  \midrule
+ \multicolumn{10}{ c }{Segmentation} \\
+  \cmidrule(lr){1-10}
+  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5       & F@3 \\
+3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\% &    0.393\% \\
+  \midrule
+ \multicolumn{4}{ c }{Segmentation} & \multicolumn{6}{ c }{Beat}\\
+  \cmidrule(lr){1-4}
+  \cmidrule(lr){5-10}
+  P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt \\
+  0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% \\
+  \midrule
+ \multicolumn{3}{ c }{Beat} & \multicolumn{7}{ c }{Pattern}\\
+  \cmidrule(lr){1-3}
+  \cmidrule(lr){4-10}
+  AMLc       & AMLt       & In. Gain & Pat & Pat & Pat & Pat & Pat & Pat & Pat \\
+  0.137\% &    0.139\% &   9.174\% &  ??? & ??? & ??? & ??? & ??? & ??? & ???\\
+  \midrule
+ \multicolumn{10}{ c }{Pattern}\\
+  \cmidrule(lr){1-10}
+  Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat\\
+  ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ???\\
+  \midrule
+ \multicolumn{4}{ c }{Pattern}  & \multicolumn{3}{ c }{Onset}  & \multicolumn{3}{ c }{Source Separation}\\
+  \cmidrule(lr){1-4}
+  \cmidrule(lr){5-7}
+  \cmidrule(lr){8-10}
+ Pat & Pat & Pat & Pat & F-measure  & Precision  & Recall & SDR & SIR & SAR \\
+ ??? & ??? & ??? & ??? &    0.165\% &    0.165\% &    0.165\% & ??? & ??? & ??? \\
+  \bottomrule
+
+\end{tabular}
+\label{table:comparisons}
+\end{table*}
+>>>>>>> 63bc147b652a8ff4fcd68d1cd3b1f2b0889cb07b
+
 \section{Discussion}

### 2014-05-08 paper/paper.tex
Fixing table
Somehow the old table found it's way back in.  Also adding in rough draft of segment diff section

@@
 \end{tabularx}
-\begin{tabularx}{\linewidth}{*{2}{>{\centering\arraybackslash}X} c c c c c c c c}
+\begin{tabularx}{\linewidth}{*{2}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c c}
  \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{5}{ c }{Melody Extraction}\\
@@
 
-Brian writes this section, which covers the differences in beat.f\_measure, boundary.detection, and onset.f\_measure
+In the computation of the F-measure, precision and recall metrics for the beat tracking, boundary detection, and onset detection tasks, an estimated event is considered correct (a ``hit'') if it falls within a small window of a reference event.
+No estimated boundary is counted as a hit for more than one reference boundary, and vice versa.
+In MIREX, this assignment is done in a greedy fashion, however in \mireval{} we use an optimal matching strategy.
+This is accomplished by computing a maximum bipartite matching between the estimated events and the reference events (subject to the window constraint) using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.
+This explains the observed discrepancy between \mireval{} and MIREX for each of these metrics.
+In all cases where the metric differs, \mireval{} reports a higher score, indicating that the greedy matching strategy was suboptimal.
+
+\subsection{Segment Boundary Deviation}
+
+% Because when numpy computes the median of an even number of numbers, it computes the mean of the two middle values.
+
+\subsection{Segment Frame Clustering}
+
+% Frame sampling - MIREX does two different things, we do one thing consistently
+% For Rand index and pairwise classification, MIREX uses a fixed sampling but at different rates.
+% In the conditional entropy scores, it uses a fixed number of samples.
+% In \mireval{}, we use the same fixed sampling rate for all metrics.
+
+% In MIREX, the range over which frames are sampled depends on both the reference and the estimate intervals.
+% In \mireval{}, the sampling is always done with respect to the reference to ensure fair comparison across multiple estimates for the same reference.
+
+% This additionally requires that estimated intervals are adjusted to span the exact duration specified by the reference intervals.
+% In \mireval{}, this is done by adding synthetic intervals when the estimated intervals do not span the reference intervals or otherwise trimming estimated intervals.
+
+%this affects___
+
+\subsection{Segment Normalized Conditional Entropy Scores}
+
+% When adding intervals, we ensure that the labels do not conflict with existing labels in the estimated annotation.
+% This has the effect of changing the normalization constant in the normalized conditional entropy scores.
+
+% When there's only one label, the normalized conditional entropy scores are not well defined.
+% In MIREX, they are assigned a score of 1 in this case; in \mireval{} we assign a score of 0.
 
@@
 
-\subsection{Other segmentation differences}
-
-Brian renames this section and writes it/splits it into different sections.
-
-\subsection{Chord stuff}
-
-Eric renames this section and writes it/splits it into different sections
-
 \subsection{Voicing False Alarm Rate}
@@
 In the data set over which the average relative change for the melody metrics was computed, one reference annotation contained no unvoiced frames.
-This discrepancy caused a large inflation of the average relative change reported for the voicing false alarm rate.
+This discrepancy caused a large inflation of the average relative change reported for the voicing false alarm rate due to the small number of examples in our dataset.
 
@@
 
-% Beat: Compared against MIREX 2013
-% Segmentation: Compared against ??
-% Melody: Compared against MIREX 2011, SG2 only
-% Pattern: Compared against development set, MATLAB code
-% Source Separation: Compared against SiSEC dev sets
-% Onset: Compared against MIREX 2013
-
-% Beat - 9 metrics
-% Chord - 5 metrics
-% Segmentation - 14 metrics
-% Melody - 5 metrics
-% Pattern - 21 metrics
-% Onset - 3 metrics
-% Source Separation - 3 metrics
-
-\begin{table*}[t]
-  \centering
-\begin{tabular}{c c c c c c c c c c}
-
-\toprule
- \multicolumn{5}{ c }{Chord} & \multicolumn{5}{ c }{Melody}\\
-  \cmidrule(lr){1-5}
-
-  \cmidrule(lr){5-10}
- Root & M/m & M/m + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Raw Chroma & Voicing R & Voicing F-A\\
-  0.007\% & 0.1634\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
-  \midrule
- \multicolumn{10}{ c }{Segmentation} \\
-  \cmidrule(lr){1-10}
-  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5       & F@3 \\
-3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\% &    0.393\% \\
-  \midrule
- \multicolumn{4}{ c }{Segmentation} & \multicolumn{6}{ c }{Beat}\\
-  \cmidrule(lr){1-4}
-  \cmidrule(lr){5-10}
-  P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt \\
-  0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% \\
-  \midrule
- \multicolumn{3}{ c }{Beat} & \multicolumn{7}{ c }{Pattern}\\
-  \cmidrule(lr){1-3}
-  \cmidrule(lr){4-10}
-  AMLc       & AMLt       & In. Gain & Pat & Pat & Pat & Pat & Pat & Pat & Pat \\
-  0.137\% &    0.139\% &   9.174\% &  ??? & ??? & ??? & ??? & ??? & ??? & ???\\
-  \midrule
- \multicolumn{10}{ c }{Pattern}\\
-  \cmidrule(lr){1-10}
-  Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat\\
-  ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ???\\
-  \midrule
- \multicolumn{4}{ c }{Pattern}  & \multicolumn{3}{ c }{Onset}  & \multicolumn{3}{ c }{Source Separation}\\
-  \cmidrule(lr){1-4}
-  \cmidrule(lr){5-7}
-  \cmidrule(lr){8-10}
- Pat & Pat & Pat & Pat & F-measure  & Precision  & Recall & SDR & SIR & SAR \\
- ??? & ??? & ??? & ??? &    0.165\% &    0.165\% &    0.165\% & ??? & ??? & ??? \\
-  \bottomrule
-
-\end{tabular}
-\label{table:comparisons}
-\end{table*}
->>>>>>> 63bc147b652a8ff4fcd68d1cd3b1f2b0889cb07b
-
 \section{Discussion}

### 2014-05-08 paper/paper.tex
Bad ref
Chord rec -> chord est

@@
 
-\mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord recognition, pattern discovery, structural segmentation, melody extraction, and onset detection.
+\mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord estimation, pattern discovery, structural segmentation, melody extraction, and onset detection.
 Each task is given its own submodule (e.g. \mireval{}\texttt{.beat}), and each metric is defined as a separate function in each submodule (e.g. \mireval{}\texttt{.beat.f\char`_measure}).
@@
 Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord estimation (ACE) is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{Peeters2013}.
-%For example, ISMIR 2010 saw the fondly dubbed ``Utrecht Agreement on Chord Evaluation''\footnote{http://www.music-ir.org/mirex/wiki/The\_Utrecht\_Agreement\_on\_Chord\_Evaluation}, in which interested researchers met to discuss sane ways of quantifying the performance of automatic chord recognition systems.
+%For example, ISMIR 2010 saw the fondly dubbed ``Utrecht Agreement on Chord Evaluation''\footnote{http://www.music-ir.org/mirex/wiki/The\_Utrecht\_Agreement\_on\_Chord\_Evaluation}, in which interested researchers met to discuss sane ways of quantifying the performance of automatic chord estimation systems.
 One source of difficulty stems from an inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{McVicar}.
@@
 
-For the beat detection, chord recognition, structural segmentation, and onset detection tasks, MIREX releases the the output of submitted algorithms, the ground truth annotations, and the reported score for each example in each data set.
+For the beat detection, chord estimation, structural segmentation, and onset detection tasks, MIREX releases the the output of submitted algorithms, the ground truth annotations, and the reported score for each example in each data set.
 We therefore can directly compare \mireval{} to MIREX for these tasks by collecting all reference and estimated annotations, computing each metric for each example, and comparing the result to the score reported by MIREX.
@@
 \begin{tabularx}{\linewidth}{*{2}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c c}
- \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{5}{ c }{Melody Extraction}\\
+ \multicolumn{5}{ c }{Chord Estimation} & \multicolumn{5}{ c }{Melody Extraction}\\
   \cmidrule(lr){1-5}
@@
 Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX. 
-This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{table:comparisons}. 
+This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{tab:comparison}. 
 For example, it seems as though $Bb:maj(9)/9$ was \emph{not} excluded from the MIREX evaluation, contradicting the description provided online.

### 2014-05-08 paper/paper.tex
Adding table
Voicing explanation

@@
 
+\begin{table}[htb]
+\label{tab:nexamples}
+  \centering
+\begin{tabularx}{\columnwidth}{l c c c}
+\toprule
+Task & Algorithms & Examples & Scores\\
+\midrule
+Beat Detection & 20 & 679 & 13580\\
+Segmentation & 8 & 1397 & 11176 \\
+Onset Detection & 11 & 85 & 935 \\
+Chord Estimation & 12 & 217 & 2604 \\
+Melody & 1 & 20 & 20 \\
+Pattern Discovery & 4 & 5 & 20 \\
+\bottomrule
+\end{tabularx}
+\end{table}
+
 The resulting average relative change for each metric is presented in Table \ref{tab:comparison}.
@@
 When a reference melody annotation contains no unvoiced frames, the voicing false alarm rate is not well defined.
-MIREX assigns a score of 1 in this case, while \mireval{} assigns a score of 0.
-%%%
-%%%
-%%%
-% WHY?
-%%%
-%%%
-%%%
+MIREX assigns a score of 1 in this case, while \mireval{} assigns a score of 0 because, intuitively, no reference unvoiced frames could be estimated, so no false alarms should be reported.
 In the data set over which the average relative change for the melody metrics was computed, one reference annotation contained no unvoiced frames.

### 2014-05-08 paper/paper.tex
Minor edits

@@
+% Add table captions
+% Add conclusion
+% Fill in missing segmentation explanations
+
 % -----------------------------------------------
@@
 \begin{table}[htb]
-\label{tab:nexamples}
   \centering
-\begin{tabularx}{\columnwidth}{l c c c}
+\begin{tabularx}{\columnwidth}{l r r r}
 \toprule
@@
 \end{tabularx}
+ \label{tab:nexamples}
 \end{table}
@@
 \begin{table*}[htb]
-\label{tab:comparison}
   \centering
@@
   \cmidrule(lr){1-9}
-F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt       & AMLc       & AMLt       & In. Gain   \\
+F-measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt       & AMLc       & AMLt       & In. Gain   \\
    0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% &    0.137\% &    0.139\% &    9.174\% \\
@@
   \cmidrule(lr){6-10}
-  Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Chroma & Voicing R & Voicing FA \\
- 0.007\% & 0.1634\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
+  Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw pitch & Chroma & Voicing R & Voicing FA \\
+ 0.007\% & 0.163\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
   \bottomrule
 \end{tabularx}
+\label{tab:comparison}
 \end{table*}
@@
 In the computation of the F-measure, precision and recall metrics for the beat tracking, boundary detection, and onset detection tasks, an estimated event is considered correct (a ``hit'') if it falls within a small window of a reference event.
-No estimated boundary is counted as a hit for more than one reference boundary, and vice versa.
+No estimated event is counted as a hit for more than one reference event, and vice versa.
 In MIREX, this assignment is done in a greedy fashion, however in \mireval{} we use an optimal matching strategy.
@@
 The Information Gain metric \cite{davies2009evaluation} involves the computation a histogram of the per-beat errors.
-The Beat Evaluation Toolbox uses a non-uniform histogram binning where the first, second and last bins are smaller than the rest of the bins while \mireval{} uses a standard uniformly-binned histogram.
+The Beat Evaluation Toolbox (and therefore MIREX) uses a non-uniform histogram binning where the first, second and last bins are smaller than the rest of the bins while \mireval{} uses a standard uniformly-binned histogram.
 As a result, the Information Gain score reported by \mireval{} differs substantially from that reported by MIREX.

### 2014-05-08 paper/paper.tex
Table captions
Filling in structure differences

@@
-% Add table captions
 % Add conclusion
 % Fill in missing segmentation explanations 
+% Switch chord footnote to ref
 
@@
 \end{tabularx}
+ \caption{Number of scores collected for each task for comparison against \mireval{}.}
  \label{tab:nexamples}
@@
 \end{tabularx}
+ \caption{Average relative change for every metric in \mireval{} when compared to a pre-existing implementation.}
 \label{tab:comparison}
@@
 In all cases where the metric differs, \mireval{} reports a higher score, indicating that the greedy matching strategy was suboptimal.
-
-\subsection{Segment Boundary Deviation}
-
-% Because when numpy computes the median of an even number of numbers, it computes the mean of the two middle values.
-
-\subsection{Segment Frame Clustering}
-
-% Frame sampling - MIREX does two different things, we do one thing consistently
-% For Rand index and pairwise classification, MIREX uses a fixed sampling but at different rates.
-% In the conditional entropy scores, it uses a fixed number of samples.
-% In \mireval{}, we use the same fixed sampling rate for all metrics.
-
-% In MIREX, the range over which frames are sampled depends on both the reference and the estimate intervals.
-% In \mireval{}, the sampling is always done with respect to the reference to ensure fair comparison across multiple estimates for the same reference.
-
-% This additionally requires that estimated intervals are adjusted to span the exact duration specified by the reference intervals.
-% In \mireval{}, this is done by adding synthetic intervals when the estimated intervals do not span the reference intervals or otherwise trimming estimated intervals.
-
-%this affects___
-
-\subsection{Segment Normalized Conditional Entropy Scores}
-
-% When adding intervals, we ensure that the labels do not conflict with existing labels in the estimated annotation.
-% This has the effect of changing the normalization constant in the normalized conditional entropy scores.
-
-% When there's only one label, the normalized conditional entropy scores are not well defined.
-% In MIREX, they are assigned a score of 1 in this case; in \mireval{} we assign a score of 0.
 
@@
 
-\subsection{Voicing False Alarm Rate}
+\subsection{Segment Boundary Deviation}
+
+When computing the median of the absolute time differences for the boundary deviation metrics, there are often an even number of reference or estimated segment boundaries, resulting in an even number of differences to compute the median over.
+In this case, there is no ``middle'' element to choose as the median.
+\mireval{} follows the typical convention of computing the mean of the two middle elements in lieu of the median for even-length sequences, while MIREX chooses the larger of the two middle elements.
+This accounts for the discrepancy in the reference-to-estimated and estimated-to-reference boundary deviation metrics.
+
+\subsection{Interval Sampling for Structure Metrics}
+
+When computing the structure annotation metrics (pairwise precision, recall, and F-measure, Rand index, and normalized conditional entropy over- and under-segmentation scores), the reference and estimated labels must be sampled to a common timebase.
+In MIREX, a fixed sampling grid is used for the Rand index and pairwise classification metrics, but a different sampling rate is used for each, while a fixed number of samples is used for the conditional entropy scores.
+In \mireval{}, the same fixed sampling rate of 100 milliseconds is used for all structure annotation metrics, as specified in \cite{willis2013mirex}.
+
+Furthermore, the start and end time over which the intervals are sampled depends on both the reference and estimated intervals while \mireval{}, always samples with respect to the reference to ensure fair comparison across multiple estimates.
+This additionally requires that estimated intervals are adjusted to span the exact duration specified by the reference intervals.
+This is done by adding synthetic intervals when the estimated intervals do not span the reference intervals or otherwise trimming estimated intervals.
+These differences account for the average relative changes for the structure annotation metrics.
+
+\subsection{Segment Normalized Conditional Entropy Scores}
+
+When adding intervals to the estimated annotation as described above, \mireval{} ensures that the labels do not conflict with existing labels.
+This has the effect of changing the normalization constant in the normalized conditional entropy scores.
+Furthermore, when there's only one label, the normalized conditional entropy scores are not well defined.
+MIREX assigns a score of 1 in this case; in \mireval{} we assign a score of 0.
+This results in a larger average change for these two metrics.
+
+\subsection{Melody Voicing False Alarm Rate}
 

### 2014-05-08 paper/paper.tex
Better goto description
Flattening descriptions

@@
 \mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord estimation, pattern discovery, structural segmentation, melody extraction, and onset detection.
-Each task is given its own submodule (e.g. \mireval{}\texttt{.beat}), and each metric is defined as a separate function in each submodule (e.g. \mireval{}\texttt{.beat.f\char`_measure}).
+Each task is given its own submodule, and each metric is defined as a separate function in each submodule.
 Each task submodule also includes common data pre-processing steps for the task.
@@
 \textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat;
-\textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met;
+\textbf{Goto's score}, a binary score which is 1 when at least 25\% of the estimated beat sequence closely matches the reference beat sequence;
 \textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains;
 \textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct;
-and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.
+and finally the \textbf{information gain} of the normalized beat error histogram to a uniform distribution.
 
@@
 Given the novelty of this task (the first year it appeared in MIREX was 2013), the evaluation metrics are likely to be modified in further editions.
-Nonetheless, Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013}, which resulted in 19 different scores, each one implemented in \mireval{} and described below:
-
-\begin{description}
-\item[Standard F-measure, Precision, and Recall:] An estimated pattern is considered correct only if it matches (up to translation) a reference prototype pattern.
-\item[Establishment F-measure, Precision, and Recall:] Computes the number of reference patterns that were successfully found, no matter how many occurrences were found.
-      In other words, these metrics capture the ability of the algorithm to \textit{establish} the patterns in a piece.
-\item[Occurrence F-measure, Precision, and Recall:] Measures whether an algorithm is able to retrieve all occurrences of a pattern.
-      This metric aims to quantize this \textit{occurrence} retrieval quality of the algorithm.
-\item[Three-layer F-measure, Precision, and Recall:] These metrics capture both the establishment of the patterns and the occurrence retrieval in a single set of scores.
-\item[First $N$ patterns metrics:] The target proportion establishment recall and three-layer precision analyzing the first $N$ patterns only, which measures the ability of the algorithm to sort the identified patterns based on their relevance.
-\end{description}
+Nonetheless, Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013}, which resulted in 19 different scores, each one implemented in \mireval{}:
+\textbf{Standard F-measure, Precision, and Recall}, where an estimated pattern is considered correct only if it matches (up to translation) a reference prototype pattern;
+\textbf{Establishment F-measure, Precision, and Recall}, which computes the number of reference patterns that were successfully found, no matter how many occurrences were found;
+\textbf{Occurrence F-measure, Precision, and Recall}, which measures whether an algorithm is able to retrieve all occurrences of a pattern;
+\textbf{Three-layer F-measure, Precision, and Recall}, which capture both the establishment of the patterns and the occurrence retrieval in a single set of scores;
+and the \textbf{First $N$ patterns metrics}, where the target proportion establishment recall and three-layer precision analyzing the first $N$ patterns only, which measures the ability of the algorithm to sort the identified patterns based on their relevance.
 
@@
 \mireval{} implements the following boundary detection metrics:
-\begin{description}
-\item[Boundary detection:] precision, recall, and F-measure scores where an estimated boundary is considered correct if it falls within a window around a reference boundary ~\cite{turnbull2007supervised};
-\item[Boundary deviation:] median absolute time difference from a reference boundary to its nearest estimated boundary, and vice versa~\cite{turnbull2007supervised},
-\end{description}
-and the following structure annotation metrics:
-\begin{description}
-\item[Pairwise classification:] precision, recall, and F-measure for classifying pairs of sampled time instants as belonging to the same structural component~\cite{levy2008structural};
-\item[Rand index:] reference and estimated annotations are sampled uniformly throughout the track, and the induced clusterings are compared by the Rand index ~\cite{rand1971objective};
-\footnote{The MIREX results page refers to Rand index as ``random clustering index''.}
-\item[Normalized conditional entropy:] reference and estimated labels are sampled uniformly, and interpreted as samples of random variables $Y_R, Y_E$, which are computed by estimating the conditional entropy of $Y_R$ given $Y_E$ (\emph{under-segmentation}) and $Y_E$ given $Y_R$  (\emph{over-segmentation})~\cite{lukashevich2008towards}.
-\end{description}
+\textbf{Boundary detection precision, recall, and F-measure scores} where an estimated boundary is considered correct if it falls within a window around a reference boundary \cite{turnbull2007supervised};
+\textbf{Boundary deviation} which computes median absolute time difference from a reference boundary to its nearest estimated boundary, and vice versa \cite{turnbull2007supervised}
+The following structure annotation metrics are also included:
+\textbf{Pairwise classification precision, recall, and F-measure scores} for classifying pairs of sampled time instants as belonging to the same structural component~\cite{levy2008structural};
+\textbf{Rand index}\footnote{The MIREX results page refers to Rand index as ``random clustering index''.} which clusters reference and estimated annotations and compares themby the Rand index ~\cite{rand1971objective};
+and the \textbf{Normalized conditional entropy} where sampled reference and estimated labels are interpreted as samples of random variables $Y_R, Y_E$ from which the conditional entropy of $Y_R$ given $Y_E$ (\emph{under-segmentation}) and $Y_E$ given $Y_R$  (\emph{over-segmentation}) are estimated \cite{lukashevich2008towards}.
 
 \subsection{Melody Extraction}
+
 Melody extraction algorithms aim to produce a sequence of frequency values corresponding to the pitch of the dominant melody from a musical recording \cite{salamon:MelodyReview:IEEESPM13}.
@@
 An estimated pitch series is evaluated against a reference by computing the following five measures defined in \cite{salamon:MelodyReview:IEEESPM13}, first used in the MIREX 2005 Automatic Melody Extraction evaluation \cite{polinerMelodyEval}:
-\begin{description}
-  \item[Voicing Recall Rate:] The proportion of frames labeled as melody frames in the reference that are estimated as melody frames by the algorithm.
-  \item[Voicing False Alarm Rate:] The proportion of frames labeled as non-melody in the reference that are mistakenly estimated as melody frames by the algorithm.
-  \item[Raw Pitch Accuracy:] The proportion of melody frames in the reference for which the frequency is considered correct (i.e.~within half a semitone of the reference frequency).
-  \item[Raw Chroma Accuracy:] As raw pitch accuracy, except that both the estimated and reference $f_0$ sequences are mapped onto a single octave.
-  \item[Overall Accuracy:] The proportion of all frames correctly estimated by the algorithm, where for non-melody frames this means the algorithm labeled them as non-melody, and for melody frames the algorithm both labeled them as melody frames and provided a correct $f_0$ estimate for the melody (i.e.~within half a semitone of the reference).
-\end{description}
+\textbf{Voicing Recall Rate} which computes the proportion of frames labeled as melody frames in the reference that are estimated as melody frames by the algorithm;
+\textbf{Voicing False Alarm Rate} which computes the proportion of frames labeled as non-melody in the reference that are mistakenly estimated as melody frames by the algorithm;
+\textbf{Raw Pitch Accuracy} which computes the proportion of melody frames in the reference for which the frequency is considered correct (i.e.~within half a semitone of the reference frequency);
+\textbf{Raw Chroma Accuracy} where the estimated and reference $f_0$ sequences are mapped onto a single octave before computing the raw pitch accuracy;
+and the \textbf{Overall Accuracy}, which computes the proportion of all frames correctly estimated by the algorithm, including whether non-melody frames where labeled by the algorithm as non-melody.
 Prior to computing the measure definitions provided above, both the estimate and reference sequences must be sampled on the same timebase.

### 2014-05-08 paper/paper.tex
Conclusion

@@
-% Add conclusion
-% Fill in missing segmentation explanations 
 % Switch chord footnote to ref
@@
 
-% Community development is crucial
-As seen in the case of evaluating chord estimation systems, it is our hope that an open-source, publicly refined implementation might help resolve independently performed evaluation in the future. 
-Furthermore, the difficulty faced in attempting to match the MIREX chord evaluation precisely clearly demonstrates the need for transparency and community involvement in comparative evaluation.
-%; and two, we are curious as to how reliability of independently reported results in the literature.
+The results in Section \ref{sec:comparison} clearly demonstrate that differences in implementation can lead to substantial differences in reported scores.
+This underlines the need for transparency and community involvement in comparative evaluation.
+The primary motivation behind developing \mireval{} is to establish an open-source, publicly refined implementation of the most common MIR metrics.
+By encouraging MIR researchers to use the same easily understandable evaluation codebase, we can ensure that different systems are being compared fairly.
+
+While we have given thorough consideration to the design choices made in \mireval{}, we recognize that standards may change over time and that new metrics may be proposed.
+Towards this end, \mireval{} is hosted on Github\footnote{URL redacted}, which provides a straightforward way of proposing changes to the codebase using the Pull Request feature.
+With active community participation, we believe that \mireval{} can ensure that MIR research converges on a standard methodology for evaluation.
 

### 2014-05-09 paper/paper.tex
Better section title
Swapped ref by jsalamon's suggestion

@@
 For melody extraction, the ADC2004 dataset used by MIREX is publicly available.
-We performed melody extraction using the ``SG2'' algorithm evaluated in 2011 \cite{salamon2011melody} and compared \mireval{}'s reported scores to those of MIREX.
+We performed melody extraction using the ``SG2'' algorithm evaluated in 2011 \cite{salamon:MelodyExraction:TASLP:12} and compared \mireval{}'s reported scores to those of MIREX.
 For pattern discovery, we used the development dataset released by Collins \cite{Collins2013} and used the algorithms submitted by Nieto and Farbood \cite{nieto2013discovery} for MIREX 2013 to produce estimated patterns.
@@
 
-\section{Discussion}
+\section{Towards Transparency and Community Involvement}
 \label{sec:discussion}

### 2014-05-09 paper/paper.tex
Removing redundancy

@@
 Nonetheless, Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013}, which resulted in 19 different scores, each one implemented in \mireval{}:
-\textbf{Standard F-measure, Precision, and Recall}, where an estimated pattern is considered correct only if it matches (up to translation) a reference prototype pattern;
+\textbf{Standard F-measure, Precision, and Recall}, where an estimated prototype pattern is considered correct only if it matches (up to translation) a reference prototype pattern;
 \textbf{Establishment F-measure, Precision, and Recall}, which computes the number of reference patterns that were successfully found, no matter how many occurrences were found;
@@
 \subsection{Weighted Chord Symbol Recall}
-For reference, we compare our chord evaluation against the results provided from MIREX 2013.
-Though the \textbf{Root} comparison falls well within our accuracy tolerance, the other four comparison rules exhibit non-negligible discrepancies that warrant justification.
-Based on our current understanding, implementation differences are caused by two main sources of ambiguity.
+The non-negligible average relative changes seen in the chord metrics are caused by two main sources of ambiguity.
 %Some interval mappings aren't well-defined.

### 2014-05-09 paper/paper.tex
Switching footnote to ref and adding ref to comparison

@@
 
-Based on this representation, we can symbolically define our interpretation of the five rules used in MIREX 2013\footnote{http://www.music-ir.org/mirex/wiki/2013:Audio\_Chord\_Estimation} to compare an estimated chord $\mathcal{C}_{est}$ with a reference $\mathcal{C}_{ref}$.
+Based on this representation, we can symbolically define our interpretation of the five rules used in MIREX 2013\cite{choi2013mirex} to compare an estimated chord $\mathcal{C}_{est}$ with a reference $\mathcal{C}_{ref}$.
 \textbf{Root} is given by $\mathcal{R}_{est} == \mathcal{R}_{ref}$, for all chords.
@@
 %Some chords get dropped in different scenarios, and we can't replicate the logic. 
-Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX. 
+Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX \cite{choi2013mirex}.
 This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{tab:comparison}. 

### 2014-05-09 paper/paper.tex
Switching to texttt chord labels to follow McVicar and Harte

@@
 To efficiently compare chords, we first translate a given chord label $\mathcal{C}$ into a numerical representation, based on the syntax of \cite{Harte2010}.
-For example, $G:maj(6)/5$ is mapped to three pieces of information: one, the root (``G'') is mapped to an absolute pitch class $\mathcal{R}$, in $[0, 11]$, where $C\to0$, $C\sharp/D\flat\to1$, etc; two, the quality shorthand (``maj'') and scale degrees (``6'') are mapped to a root-invariant bit vector $\mathcal{S}$ of active semitones; and three, the bass interval (``5'') is translated to the relative scale degree in semitones $\mathcal{B}$.
+For example, the chord label \texttt{G:maj(6)/5} is mapped to three pieces of information: one, the root (``G'') is mapped to an absolute pitch class $\mathcal{R}$, in $[0, 11]$, where C $\to0$, C$\sharp$/D$\flat$ $\to1$, etc; two, the quality shorthand (``maj'') and scale degrees (``6'') are mapped to a root-invariant bit vector $\mathcal{S}$ of active semitones; and three, the bass interval (``5'') is translated to the relative scale degree in semitones $\mathcal{B}$.
 %Traditionally, extended chords (9's, 11's or 13's) are not considered in evaluation and instead resolved to the tetrad contained therein, e.g. $C:9 \to C:7$, etc. 
@@
 First, we find some chord labels in the MIREX reference annotations lack well-defined, i.e. singular, mappings into a comparison space. 
-One such example is $D:maj(*1)/\#1$.
-While the quality shorthand indicates ``major'', the asterisk implies the root is omitted and thus it is unclear whether $D:maj(*1)/\#1==D:maj1$.
+One such example is \texttt{D:maj(*1)/\#1}.
+While the quality shorthand indicates ``major'', the asterisk implies the root is omitted and thus it is unclear whether \texttt{D:maj(*1)/\#1} is equivalent to \texttt{D:maj1}.
 %Some chords get dropped in different scenarios, and we can't replicate the logic. 
@@
 This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{tab:comparison}. 
-For example, it seems as though $Bb:maj(9)/9$ was \emph{not} excluded from the MIREX evaluation, contradicting the description provided online.
+For example, it seems as though \texttt{Bb:maj(9)/9} was \emph{not} excluded from the MIREX evaluation, contradicting the description provided online.
 This chord alone causes an observable difference between the results of our implementation and previously reported results.

### 2014-05-09 paper/paper.tex
Moving cite'

@@
 %Some chords get dropped in different scenarios, and we can't replicate the logic. 
-Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX \cite{choi2013mirex}.
+Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX.
 This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{tab:comparison}. 
-For example, it seems as though \texttt{Bb:maj(9)/9} was \emph{not} excluded from the MIREX evaluation, contradicting the description provided online.
-This chord alone causes an observable difference between the results of our implementation and previously reported results.
+For example, it seems as though \texttt{Bb:maj(9)/9} was \emph{not} excluded from the MIREX evaluation, contradicting the description provided by the task specification \cite{choi2013mirex}.
+This chord alone causes an observable difference between \mireval{} and MIREX's results.
 

### 2014-05-09 paper/paper.tex
Moving footnote

@@
 While we have given thorough consideration to the design choices made in \mireval{}, we recognize that standards may change over time and that new metrics may be proposed.
-Towards this end, \mireval{} is hosted on Github\footnote{URL redacted}, which provides a straightforward way of proposing changes to the codebase using the Pull Request feature.
+Towards this end, \mireval{} is hosted on Github,\footnote{URL redacted} which provides a straightforward way of proposing changes to the codebase using the Pull Request feature.
 With active community participation, we believe that \mireval{} can ensure that MIR research converges on a standard methodology for evaluation.

### 2014-05-09 paper/paper.tex
adding missing refs

@@
 
-Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord estimation (ACE) is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{Peeters2013}.
+Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord estimation (ACE) is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{pauwels2013evaluating}.
 %For example, ISMIR 2010 saw the fondly dubbed ``Utrecht Agreement on Chord Evaluation''\footnote{http://www.music-ir.org/mirex/wiki/The\_Utrecht\_Agreement\_on\_Chord\_Evaluation}, in which interested researchers met to discuss sane ways of quantifying the performance of automatic chord estimation systems.
-One source of difficulty stems from an inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{McVicar}.
+One source of difficulty stems from an inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{ni2013understanding}.
 As a result, a consensus has yet to be reached regarding the single best approach to comparing two sequences of chord labels, and instead are often compared over a set of rules, i.e Root, Major-Minor, and Sevenths, with or without inversions.
 
-To efficiently compare chords, we first translate a given chord label $\mathcal{C}$ into a numerical representation, based on the syntax of \cite{Harte2010}.
+To efficiently compare chords, we first translate a given chord label $\mathcal{C}$ into a numerical representation, based on the syntax of \cite{harte2010towards}.
 For example, the chord label \texttt{G:maj(6)/5} is mapped to three pieces of information: one, the root (``G'') is mapped to an absolute pitch class $\mathcal{R}$, in $[0, 11]$, where C $\to0$, C$\sharp$/D$\flat$ $\to1$, etc; two, the quality shorthand (``maj'') and scale degrees (``6'') are mapped to a root-invariant bit vector $\mathcal{S}$ of active semitones; and three, the bass interval (``5'') is translated to the relative scale degree in semitones $\mathcal{B}$.

### 2014-05-09 paper/paper.tex
Revising chord section

@@
 
-% relevant papers
-% - pauwels & peeters
-% - matthais
-% - harte
-% - mirex 
-% - Utrecht agreement
-
-Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord estimation (ACE) is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{pauwels2013evaluating}.
-%For example, ISMIR 2010 saw the fondly dubbed ``Utrecht Agreement on Chord Evaluation''\footnote{http://www.music-ir.org/mirex/wiki/The\_Utrecht\_Agreement\_on\_Chord\_Evaluation}, in which interested researchers met to discuss sane ways of quantifying the performance of automatic chord estimation systems.
+Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord estimation is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{pauwels2013evaluating}.
 One source of difficulty stems from an inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{ni2013understanding}.
@@
 
-To efficiently compare chords, we first translate a given chord label $\mathcal{C}$ into a numerical representation, based on the syntax of \cite{harte2010towards}.
-For example, the chord label \texttt{G:maj(6)/5} is mapped to three pieces of information: one, the root (``G'') is mapped to an absolute pitch class $\mathcal{R}$, in $[0, 11]$, where C $\to0$, C$\sharp$/D$\flat$ $\to1$, etc; two, the quality shorthand (``maj'') and scale degrees (``6'') are mapped to a root-invariant bit vector $\mathcal{S}$ of active semitones; and three, the bass interval (``5'') is translated to the relative scale degree in semitones $\mathcal{B}$.
-%Traditionally, extended chords (9's, 11's or 13's) are not considered in evaluation and instead resolved to the tetrad contained therein, e.g. $C:9 \to C:7$, etc. 
-%This semitone bit-vector representation can, however, be easily expanded to represent such information in the future.
+To efficiently compare chords, we first separate a given chord label into a its constituent parts, based on the syntax of \cite{harte2010towards}.
+For example, the chord label \texttt{G:maj(6)/5} is mapped to three pieces of information: the root (``G''), the root-invariant active semitones as determined by the quality shorthand (``maj'') and scale degrees (``6''), and the bass interval (``5'').
 
-Based on this representation, we can symbolically define our interpretation of the five rules used in MIREX 2013\cite{choi2013mirex} to compare an estimated chord $\mathcal{C}_{est}$ with a reference $\mathcal{C}_{ref}$.
-\textbf{Root} is given by $\mathcal{R}_{est} == \mathcal{R}_{ref}$, for all chords.
-\textbf{Major-Minor} includes \textbf{Root}, plus $\mathcal{S}_{est} == \mathcal{S}_{ref}$ subject to $\mathcal{S}_{ref} \in \{Maj, min\}$.
-\textbf{Major-Minor-Inv} includes \textbf{Major-minor}, plus $\mathcal{B}_{est} == \mathcal{B}_{ref}$ subject to $\mathcal{B}_{ref} \in \mathcal{S}_{ref}$.
-\textbf{Sevenths} follows \textbf{Major-minor}, but is instead subject to $\mathcal{S}_{ref} \in \{Maj, min, Maj7, min7, 7, minmaj7\}$.
-Finally, \textbf{Sevenths-Inv} includes \textbf{Sevenths}, plus $\mathcal{B}_{est} == \mathcal{B}_{ref}$ subject to $\mathcal{B}_{ref} \in \mathcal{S}_{ref}$.
-Before proceeding, we draw attention to the set-inclusion conditions above, e.g.
-``subject to...'', meaning that a comparison is \emph{ignored} during evaluation if the given criteria is not satisfied.
+Based on this representation, we can define our interpretation of the five rules used in MIREX 2013\cite{choi2013mirex} to compare an estimated chord label with a reference by the following rules:
+\textbf{Root} requires only that the roots are equivalent;
+\textbf{Major-Minor} includes Root, and further requires that the active semitones are equivalent subject to the reference chord quality being Maj or min;
+\textbf{Sevenths} follows Major-minor, but is instead subject to the reference chord quality being one of Maj, min, Maj7, min7, 7, or minmaj7;
+and finally, \textbf{Major-Minor-Inv} and \textbf{Sevenths-Inv} include Major-Minor and Sevenths respectively, but further require that the bass intervals are equivalent subject to the reference bass interval being an active semitone.
+The ``subject to...'' conditions above indicate that a comparison is \emph{ignored} during evaluation if the given criteria is not satisfied.
 
-Track-wise scores, $S_n$, are computed by weighting each comparison by the duration of its interval, over all intervals in an audio file; stated another way, this is the piecewise continuous-time integral of the equivalence of two chord sequences, $(\mathbf{C}_{ref}, \mathbf{C}_{est})$, expressed as follows:
-
-\begin{equation}
-S_n(\mathbf{C}_{ref}, \mathbf{C}_{est}) = \frac{1}{T}\int_{t=0}^{T} \mathcal{C}_{ref}(t) == \mathcal{C}_{est}(t)
-\end{equation}
-
-\noindent This is achieved by forming the union of the boundaries in each sequence, and summing the time intervals of the ``correct'' ranges. 
-The cumulative score, referred to as \emph{weighted chord symbol recall} (WCSR), is tallied over a set of $N$ items, i.e.
-audio files, by discrete summation, where the importance of each score, $S_n$, is weighted by the duration, $T_n$, of each annotation:
-
-\begin{equation}
-WCSR_{total} = \frac{\sum_{n=0}^{N} T_n*S_n}{\sum_{n=0}^{N} T_n}
-\end{equation}
+Track-wise scores are computed by weighting each comparison by the duration of its interval, over all intervals in an audio file; stated another way, this is the piecewise continuous-time integral of the equivalence of two chord sequences.
+This is achieved by forming the union of the boundaries in each sequence, sampling the labels, and summing the time intervals of the ``correct'' ranges. 
+The cumulative score, referred to as \emph{weighted chord symbol recall} (WCSR), is tallied over a set audio files, by discrete summation, where the importance of each score is weighted by the duration of each annotation \cite{choi2013mirex}.
 
@@
 Given the novelty of this task (the first year it appeared in MIREX was 2013), the evaluation metrics are likely to be modified in further editions.
+
 Nonetheless, Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013}, which resulted in 19 different scores, each one implemented in \mireval{}:

### 2014-05-09 paper/paper.tex
Removing spurious comments
Final craffel proofread

@@
-% Switch chord footnote to ref
-
 % -----------------------------------------------
@@
 
-% ------
 \title{\mireval{}}
 
-% Single address
-% To use with only one author or several with the same address
-% ---------------
-%\oneauthor
-% {Names should be omitted for double-blind reviewing}
-% {Affiliations should be omitted for double-blind reviewing}
-
-% Two addresses
-% --------------
-%\twoauthors
-%  {First author} {School \\ Department}
-%  {Second author} {Company \\ Address}
-
-% Three addresses
-% --------------
 \threeauthors
@@
 %\author[1]{Brian McFee}
+%\author[2]{Eric J. Humphrey}
 %\author[2]{Justin Salamon}
-%\author[2]{Eric J. Humphrey}
 %\author[2]{Oriol Nieto}
@@
 %\affil[2]{Music and Audio Research Lab\\New York University, New York}
-
-% Four addresses
-% --------------
-%\fourauthors
-%  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
-%  {Second author}{Affiliation2 \\ {\tt author2@ismir.edu}}
-%  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}
-%  {Fourth author} {Affiliation4 \\ {\tt author4@ismir.edu}}
 
@@
 \textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct;
-and finally the \textbf{information gain} of the normalized beat error histogram to a uniform distribution.
+and finally the \textbf{Information Gain} of a normalized beat error histogram over a uniform distribution.
 
@@
 
-Based on this representation, we can define our interpretation of the five rules used in MIREX 2013\cite{choi2013mirex} to compare an estimated chord label with a reference by the following rules:
+Based on this representation, we can compare an estimated chord label with a reference by the following rules as used in MIREX 2013\cite{choi2013mirex}:
 \textbf{Root} requires only that the roots are equivalent;
@@
 This is achieved by forming the union of the boundaries in each sequence, sampling the labels, and summing the time intervals of the ``correct'' ranges. 
-The cumulative score, referred to as \emph{weighted chord symbol recall} (WCSR), is tallied over a set audio files, by discrete summation, where the importance of each score is weighted by the duration of each annotation \cite{choi2013mirex}.
+The cumulative score, referred to as \emph{weighted chord symbol recall}, is tallied over a set audio files by discrete summation, where the importance of each score is weighted by the duration of each annotation \cite{choi2013mirex}.
 
@@
 \textbf{Three-layer F-measure, Precision, and Recall}, which capture both the establishment of the patterns and the occurrence retrieval in a single set of scores;
-and the \textbf{First $N$ patterns metrics}, where the target proportion establishment recall and three-layer precision analyzing the first $N$ patterns only, which measures the ability of the algorithm to sort the identified patterns based on their relevance.
+and the \textbf{First $N$ patterns metrics}, which computes the target proportion establishment recall and three-layer precision for the first $N$ patterns only in order to measure the ability of the algorithm to sort the identified patterns based on their relevance.
 
@@
 \mireval{} implements the following boundary detection metrics:
-\textbf{Boundary detection precision, recall, and F-measure scores} where an estimated boundary is considered correct if it falls within a window around a reference boundary \cite{turnbull2007supervised};
-\textbf{Boundary deviation} which computes median absolute time difference from a reference boundary to its nearest estimated boundary, and vice versa \cite{turnbull2007supervised}
+\textbf{Boundary Detection Precision, Recall, and F-measure Scores} where an estimated boundary is considered correct if it falls within a window around a reference boundary \cite{turnbull2007supervised};
+and \textbf{Boundary Deviation} which computes median absolute time difference from a reference boundary to its nearest estimated boundary, and vice versa \cite{turnbull2007supervised}.
 The following structure annotation metrics are also included:
-\textbf{Pairwise classification precision, recall, and F-measure scores} for classifying pairs of sampled time instants as belonging to the same structural component~\cite{levy2008structural};
-\textbf{Rand index}\footnote{The MIREX results page refers to Rand index as ``random clustering index''.} which clusters reference and estimated annotations and compares themby the Rand index ~\cite{rand1971objective};
-and the \textbf{Normalized conditional entropy} where sampled reference and estimated labels are interpreted as samples of random variables $Y_R, Y_E$ from which the conditional entropy of $Y_R$ given $Y_E$ (\emph{under-segmentation}) and $Y_E$ given $Y_R$  (\emph{over-segmentation}) are estimated \cite{lukashevich2008towards}.
+\textbf{Pairwise Classification Precision, Recall, and F-measure Scores} for classifying pairs of sampled time instants as belonging to the same structural component~\cite{levy2008structural};
+\textbf{Rand Index}\footnote{The MIREX results page refers to Rand Index as ``random clustering index''.} which clusters reference and estimated annotations and compares them by the Rand Index \cite{rand1971objective};
+and the \textbf{Normalized Conditional Entropy} where sampled reference and estimated labels are interpreted as samples of random variables $Y_R, Y_E$ from which the conditional entropy of $Y_R$ given $Y_E$ (\textbf{Under-Segmentation}) and $Y_E$ given $Y_R$  (\textbf{Over-Segmentation}) are estimated \cite{lukashevich2008towards}.
 
@@
 and the \textbf{Overall Accuracy}, which computes the proportion of all frames correctly estimated by the algorithm, including whether non-melody frames where labeled by the algorithm as non-melody.
-Prior to computing the measure definitions provided above, both the estimate and reference sequences must be sampled on the same timebase.
+Prior to computing these metrics, both the estimate and reference sequences must be sampled on the same timebase.
 
@@
 As is also done in beat tracking and segment boundary detection, the primary method used to evaluate onset detectors is to first determine which estimated onsets are ``correct'', where correctness is defined as being within a small window of a reference onset \cite{bock2012evaluating}.
-From this, \textbf{precision}, \textbf{recall}, and \textbf{F-measure} scores are computed.
+From this, \textbf{Precision}, \textbf{Recall}, and \textbf{F-measure} scores are computed.
 
@@
 \end{tabularx}
- \caption{Average relative change for every metric in \mireval{} when compared to a pre-existing implementation.}
+ \caption{Average relative change for every metric in \mireval{} when compared to a pre-existing implementation.
+The average relative change for all pattern discovery metrics was 0, so they are not shown here.}
 \label{tab:comparison}
@@
 
-In the computation of the F-measure, precision and recall metrics for the beat tracking, boundary detection, and onset detection tasks, an estimated event is considered correct (a ``hit'') if it falls within a small window of a reference event.
+In the computation of the F-measure, Precision and Recall metrics for the beat tracking, boundary detection, and onset detection tasks, an estimated event is considered correct (a ``hit'') if it falls within a small window of a reference event.
 No estimated event is counted as a hit for more than one reference event, and vice versa.
@@
 When computing McKinney's P-score \cite{davies2009evaluation}, the beat sequences are first converted to impulse trains sampled at a 10 millisecond resolution.
-Because this sampling involves quantizing the beat times to a 10ms grid, shifting both beat sequences by a constant offset can result in substantial changes in the P-score.
-As a result, In \mireval{}, we normalize the beat sequences by subtracting from each reference and estimated beat location the minimum beat location in either series.
+Because this sampling involves quantizing the beat times, shifting both beat sequences by a constant offset can result in substantial changes in the P-score.
+As a result, in \mireval{}, we normalize the beat sequences by subtracting from each reference and estimated beat location the minimum beat location in either series.
 In this way, the smallest beat in the estimated and reference beat sequences is always $0$ and the metric remains the same even when both beat sequences have a constant offset applied.
@@
 
-When computing the structure annotation metrics (pairwise precision, recall, and F-measure, Rand index, and normalized conditional entropy over- and under-segmentation scores), the reference and estimated labels must be sampled to a common timebase.
-In MIREX, a fixed sampling grid is used for the Rand index and pairwise classification metrics, but a different sampling rate is used for each, while a fixed number of samples is used for the conditional entropy scores.
+When computing the structure annotation metrics (Pairwise Precision, Recall, and F-measure, Rand Index, and Normalized Conditional Entropy Over- and Under-Segmentation Scores), the reference and estimated labels must be sampled to a common timebase.
+In MIREX, a fixed sampling grid is used for the Rand Index and pairwise classification metrics, but a different sampling rate is used for each, while a fixed number of samples is used for the conditional entropy scores.
 In \mireval{}, the same fixed sampling rate of 100 milliseconds is used for all structure annotation metrics, as specified in \cite{willis2013mirex}.
 
-Furthermore, the start and end time over which the intervals are sampled depends on both the reference and estimated intervals while \mireval{}, always samples with respect to the reference to ensure fair comparison across multiple estimates.
+Furthermore, the start and end time over which the intervals are sampled depends on both the reference and estimated intervals while \mireval{} always samples with respect to the reference to ensure fair comparison across multiple estimates.
 This additionally requires that estimated intervals are adjusted to span the exact duration specified by the reference intervals.
@@
 
-\subsection{Segment Normalized Conditional Entropy Scores}
+\subsection{Segment Normalized Conditional Entropy}
 
 When adding intervals to the estimated annotation as described above, \mireval{} ensures that the labels do not conflict with existing labels.
-This has the effect of changing the normalization constant in the normalized conditional entropy scores.
-Furthermore, when there's only one label, the normalized conditional entropy scores are not well defined.
+This has the effect of changing the normalization constant in the Normalized Conditional Entropy scores.
+Furthermore, when there's only one label, the Normalized Conditional Entropy scores are not well defined.
 MIREX assigns a score of 1 in this case; in \mireval{} we assign a score of 0.
@@
 
-When a reference melody annotation contains no unvoiced frames, the voicing false alarm rate is not well defined.
+When a reference melody annotation contains no unvoiced frames, the Voicing False Alarm Rate is not well defined.
 MIREX assigns a score of 1 in this case, while \mireval{} assigns a score of 0 because, intuitively, no reference unvoiced frames could be estimated, so no false alarms should be reported.
 In the data set over which the average relative change for the melody metrics was computed, one reference annotation contained no unvoiced frames.
-This discrepancy caused a large inflation of the average relative change reported for the voicing false alarm rate due to the small number of examples in our dataset.
+This discrepancy caused a large inflation of the average relative change reported for the Voicing False Alarm Rate due to the small number of examples in our dataset.
 
@@
 This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{tab:comparison}. 
-For example, it seems as though \texttt{Bb:maj(9)/9} was \emph{not} excluded from the MIREX evaluation, contradicting the description provided by the task specification \cite{choi2013mirex}.
+For example, \texttt{Bb:maj(9)/9} was \emph{not} excluded from the MIREX evaluation, contradicting the description provided by the task specification \cite{choi2013mirex}.
 This chord alone causes an observable difference between \mireval{} and MIREX's results.

### 2014-05-09 paper/paper.tex
Acknowledgements
Fixed year of Nieto's article, and fixed a minor typo in the patterns discovery section

@@
 Pattern discovery involves the identification of musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
-The metrics used to evaluation pattern discovery systems attempt to quantify the ability of the algorithm to not only determine the presents pattern in a piece, but also to find all of their occurrences.
+The metrics used to evaluation pattern discovery systems attempt to quantify the ability of the algorithm to not only determine the present patterns in a piece, but also to find all of their occurrences.
 Given the novelty of this task (the first year it appeared in MIREX was 2013), the evaluation metrics are likely to be modified in further editions.
@@
 
+\section{Acknowledgements}
+
+The authors would like to thank (name redacted) for helpful advice about comparing chord labels.
+
 \bibliography{mir_eval}

### 2014-07-02 paper/paper.tex
Changing authors and title

--- 2014-05-09 paper/paper.tex
@@
 \usepackage{braket}
-%\usepackage{authblk}
+\usepackage{authblk}
 \usepackage{booktabs}
@@
 
-\title{\mireval{}}
+\title{\mireval{}: A Transparent Implementation of Common MIR Metrics}
 
-\threeauthors
-  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
-  {Second author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
-  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}
+%\threeauthors
+%  {First author} {Affiliation1 \\ {\tt author1@ismir.edu}}
+%  {Second author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
+%  {Third author} {Affiliation3 \\ {\tt author3@ismir.edu}}
 
-%\author[1]{Colin Raffel}
-%\author[1]{Brian McFee}
-%\author[2]{Eric J. Humphrey}
-%\author[2]{Justin Salamon}
-%\author[2]{Oriol Nieto}
-%\author[1]{Dawen Liang}
-%\author[1]{Daniel P. W. Ellis}
-%\affil[1]{LabROSA, Dept. of Electrical Engineering\\Columbia University, New York}
-%\affil[2]{Music and Audio Research Lab\\New York University, New York}
+\author[1]{Colin Raffel}
+\author[1]{Brian McFee}
+\author[2]{Eric J. Humphrey}
+\author[2]{Justin Salamon}
+\author[2]{Oriol Nieto}
+\author[1]{Dawen Liang}
+\author[1]{Daniel P. W. Ellis}
+\affil[1]{LabROSA, Dept. of Electrical Engineering\\Columbia University, New York}
+\affil[2]{Music and Audio Research Lab\\New York University, New York}
 

### 2014-07-02 paper/paper.tex
Reviewer comments and i.e. -> ie{}, etc -> etc{}, e.g. -> eg{}

@@
 MIREX is built upon the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
-The NEMA codebase includes multiple programming languages and dependencies (some of which, e.g. Matlab, are proprietary) so compiling and running it at individual sites is nontrivial. 
+The NEMA codebase includes multiple programming languages and dependencies (some of which, \eg{} Matlab, are proprietary) so compiling and running it at individual sites is nontrivial. 
 %
@@
 Every metric function includes detailed documentation, example usage, input validation, and references to the original paper which defined the metric.
-\mireval{} also includes a submodule \texttt{io} which provides convenience functions for loading in task-specific data from common file formats.
+\mireval{} also includes a submodule \texttt{io} which provides convenience functions for loading in task-specific data from common file formats (\eg{} comma/tab separated values, \texttt{.lab} files \cite{harte2010towards}, \etc{}).
 For readability, all code follows the PEP8 style guide\cite{van2001pep}.
@@
 \label{sec:tasks}
+
+In this section, we enumerate the tasks and metrics implemented in \mireval{}.
+Due to space constraints, we only give high-level descriptions for each metric; for exact definitions see the references provided.
 
@@
 
-Pattern discovery involves the identification of musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
+Pattern discovery involves the identification of musical patterns (\ie{} short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
 The metrics used to evaluation pattern discovery systems attempt to quantify the ability of the algorithm to not only determine the present patterns in a piece, but also to find all of their occurrences.
@@
 \textbf{Voicing False Alarm Rate} which computes the proportion of frames labeled as non-melody in the reference that are mistakenly estimated as melody frames by the algorithm;
-\textbf{Raw Pitch Accuracy} which computes the proportion of melody frames in the reference for which the frequency is considered correct (i.e.~within half a semitone of the reference frequency);
+\textbf{Raw Pitch Accuracy} which computes the proportion of melody frames in the reference for which the frequency is considered correct (\ie{} within half a semitone of the reference frequency);
 \textbf{Raw Chroma Accuracy} where the estimated and reference $f_0$ sequences are mapped onto a single octave before computing the raw pitch accuracy;
@@
 For the beat detection, chord estimation, structural segmentation, and onset detection tasks, MIREX releases the the output of submitted algorithms, the ground truth annotations, and the reported score for each example in each data set.
-We therefore can directly compare \mireval{} to MIREX for these tasks by collecting all reference and estimated annotations, computing each metric for each example, and comparing the result to the score reported by MIREX.
+We therefore can directly compare \mireval{} to MIREX for these tasks by collecting all reference and estimated annotations, computing each metric for each example using identical pre-processing and parameters as appropriate, and comparing the result to the score reported by MIREX.
 We chose to compare against the results reported in MIREX 2013 for all tasks.
@@
 %Some interval mappings aren't well-defined.
-First, we find some chord labels in the MIREX reference annotations lack well-defined, i.e. singular, mappings into a comparison space. 
+First, we find some chord labels in the MIREX reference annotations lack well-defined, \ie{} singular, mappings into a comparison space. 
 One such example is \texttt{D:maj(*1)/\#1}.
@@
 
-While we have given thorough consideration to the design choices made in \mireval{}, we recognize that standards may change over time and that new metrics may be proposed.
-Towards this end, \mireval{} is hosted on Github,\footnote{URL redacted} which provides a straightforward way of proposing changes to the codebase using the Pull Request feature.
+While we have given thorough consideration to the design choices made in \mireval{}, we recognize that standards change over time, new metrics are proposed each year, and that only a subset of MIR tasks are currently implemented in \mireval{}.
+Towards this end, \mireval{} is hosted on Github,\footnote{URL redacted} which provides a straightforward way of proposing changes and additions to the codebase using the Pull Request feature.
 With active community participation, we believe that \mireval{} can ensure that MIR research converges on a standard methodology for evaluation.

### 2014-07-02 paper/paper.tex
Unredacting

@@
 While we have given thorough consideration to the design choices made in \mireval{}, we recognize that standards change over time, new metrics are proposed each year, and that only a subset of MIR tasks are currently implemented in \mireval{}.
-Towards this end, \mireval{} is hosted on Github,\footnote{URL redacted} which provides a straightforward way of proposing changes and additions to the codebase using the Pull Request feature.
+Towards this end, \mireval{} is hosted on Github,\footnote{\url{http://github.com/craffel/mir_eval}} which provides a straightforward way of proposing changes and additions to the codebase using the Pull Request feature.
 With active community participation, we believe that \mireval{} can ensure that MIR research converges on a standard methodology for evaluation.
@@
 
-The authors would like to thank (name redacted) for helpful advice about comparing chord labels.
+The authors would like to thank Matthew McVicar for helpful advice about comparing chord labels.
 

### 2014-07-02 paper/paper.tex
Camera-ready edits

@@
 For the past 10 years, the yearly Music Information Retrieval Evaluation eXchange (MIREX) has been a forum for comparing MIR algorithms over common datasets \cite{downie2008music}.
-By providing a standardized shared-task setting, MIREX has become critically useful to track progress in MIR research.
+By providing a standardized shared-task setting, MIREX has become critically useful for tracking progress in MIR research.
 MIREX is built upon the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
@@
 
-\mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord estimation, pattern discovery, structural segmentation, melody extraction, and onset detection.
+\mireval{} is a Python library which currently includes metrics for the following tasks: Beat detection, chord estimation, pattern discovery, structural segmentation, melody extraction, and onset detection.
 Each task is given its own submodule, and each metric is defined as a separate function in each submodule.
@@
 For readability, all code follows the PEP8 style guide\cite{van2001pep}.
-\mireval{}'s only dependencies outside of the Python standard library are the free and open-source SciPy/Numpy\cite{jones2001scipy} and scikit-learn\cite{pedregosa2011scikit} Python libraries.
+\mireval{}'s only dependencies outside of the Python standard library are the free and open-source \texttt{SciPy}/\texttt{Numpy}\cite{jones2001scipy} and \texttt{scikit-learn}\cite{pedregosa2011scikit} Python libraries.
 
@@
 As a result, most metrics for evaluating the performance of beat tracking systems involve computing the error between the estimated beat times and some reference list of beat locations.
-Many metrics additionally compare the beat sequences at different metric levels in order to deal with the ambiguity of tempo \cite{levy2011improving}.
+Many metrics additionally compare the beat sequences at different metric levels in order to deal with the ambiguity of tempo \cite{davies2009evaluation}.
 
@@
 
-Track-wise scores are computed by weighting each comparison by the duration of its interval, over all intervals in an audio file; stated another way, this is the piecewise continuous-time integral of the equivalence of two chord sequences.
+Track-wise scores are computed by weighting each comparison by the duration of its interval, over all intervals in an audio file.
 This is achieved by forming the union of the boundaries in each sequence, sampling the labels, and summing the time intervals of the ``correct'' ranges. 
@@
 The metrics used to evaluation pattern discovery systems attempt to quantify the ability of the algorithm to not only determine the present patterns in a piece, but also to find all of their occurrences.
-Given the novelty of this task (the first year it appeared in MIREX was 2013), the evaluation metrics are likely to be modified in further editions.
 
-Nonetheless, Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013}, which resulted in 19 different scores, each one implemented in \mireval{}:
+Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013} which resulted in 19 different scores, each one implemented in \mireval{}:
 \textbf{Standard F-measure, Precision, and Recall}, where an estimated prototype pattern is considered correct only if it matches (up to translation) a reference prototype pattern;
@@
 Melody extraction algorithms aim to produce a sequence of frequency values corresponding to the pitch of the dominant melody from a musical recording \cite{salamon:MelodyReview:IEEESPM13}.
-Melody annotations are represented as time series of fundamental frequency ($f_0$) values in Hz sampled at discrete points (``frames'') in time.
-An estimated pitch series is evaluated against a reference by computing the following five measures defined in \cite{salamon:MelodyReview:IEEESPM13}, first used in the MIREX 2005 Automatic Melody Extraction evaluation \cite{polinerMelodyEval}:
+An estimated pitch series is evaluated against a reference by computing the following five measures defined in \cite{salamon:MelodyReview:IEEESPM13}, first used in MIREX 2005 \cite{polinerMelodyEval}:
 \textbf{Voicing Recall Rate} which computes the proportion of frames labeled as melody frames in the reference that are estimated as melody frames by the algorithm;
@@
 and the \textbf{Overall Accuracy}, which computes the proportion of all frames correctly estimated by the algorithm, including whether non-melody frames where labeled by the algorithm as non-melody.
-Prior to computing these metrics, both the estimate and reference sequences must be sampled on the same timebase.
+Prior to computing these metrics, both the estimate and reference sequences must be sampled onto the same timebase.
 
@@
 
-For each task covered by \mireval{}, we obtained a collection of reference and estimated annotations and computed a score for each metric using \mireval{} and the evaluation system being compared to.
+For each task covered by \mireval{}, we obtained a collection of reference and estimated annotations and computed or obtained a score for each metric using \mireval{} and the evaluation system being compared to.
 In order to facilitate comparison, we ensured that all parameters and pre-processing used by \mireval{} were equivalent to the reference system unless otherwise explicitly noted.
@@
 where $s_m$ is the score reported by \mireval{} and $s_c$ is the score being compared to.
-We then computed the average relative change across all examples in the obtained dataset for each score.
+Finally, we computed the average relative change across all examples in the obtained dataset for each score.
 
@@
 
-In contrast to the tasks above, MIREX does not release ground truth annotations or algorithm output for the melody extraction and pattern discovery tasks.
+In contrast to the tasks listed above, MIREX does not release ground truth annotations or algorithm output for the melody extraction and pattern discovery tasks.
 As a result, we compared \mireval{}'s output on smaller development datasets for these tasks.
@@
 
-Furthermore, the start and end time over which the intervals are sampled depends on both the reference and estimated intervals while \mireval{} always samples with respect to the reference to ensure fair comparison across multiple estimates.
+Furthermore, in MIREX the start and end time over which the intervals are sampled depends on both the reference and estimated intervals while \mireval{} always samples with respect to the reference to ensure fair comparison across multiple estimates.
 This additionally requires that estimated intervals are adjusted to span the exact duration specified by the reference intervals.
@@
 Furthermore, when there's only one label, the Normalized Conditional Entropy scores are not well defined.
-MIREX assigns a score of 1 in this case; in \mireval{} we assign a score of 0.
+MIREX assigns a score of 1 in this case; \mireval{} assigns a score of 0.
 This results in a larger average change for these two metrics.
@@
 The results in Section \ref{sec:comparison} clearly demonstrate that differences in implementation can lead to substantial differences in reported scores.
-This underlines the need for transparency and community involvement in comparative evaluation.
+This corroborates the need for transparency and community involvement in comparative evaluation.
 The primary motivation behind developing \mireval{} is to establish an open-source, publicly refined implementation of the most common MIR metrics.

### 2014-07-04 paper/paper.tex
Added dpwe NSF acknowledgement.
added cusp affiliation
New ISMIR paper template ughhh
Update paper.tex
put line break in title; added in part to NSF support claim

@@
 % -----------------------------------------------
-% Template for ISMIR 2014
-% (based on earlier ISMIR templates)
+% Template for ISMIR Papers
+% 2014 version, based on previous ISMIR templates
 % -----------------------------------------------
@@
 \documentclass{article}
-\usepackage{ismir2014,amsmath,cite}
+\usepackage{ismir,amsmath,cite}
 \usepackage{graphicx}
@@
 
-\title{\mireval{}: A Transparent Implementation of Common MIR Metrics}
+\title{\mireval{}:\\
+A Transparent Implementation of Common MIR Metrics}
 
@@
 \author[2]{Eric J. Humphrey}
-\author[2]{Justin Salamon}
+\author[2,3]{Justin Salamon}
 \author[2]{Oriol Nieto}
@@
 \affil[2]{Music and Audio Research Lab\\New York University, New York}
+\affil[3]{Center for Urban Science and Progress\\New York University, New York}
+
+\def\authorname{Colin Raffel, Brian McFee, Eric J. Humphrey, Justin Salamon, Oriol Nieto, Dawen Liang, Daniel P. W. Ellis}
 
@@
 
-The authors would like to thank Matthew McVicar for helpful advice about comparing chord labels.
+The authors would like to thank Matthew McVicar for helpful advice about comparing chord labels.  Support provided in part by NSF grant IIS-1117015.
 

### 2014-07-05 paper/paper.tex
Added a thank you note to Tom Collins
added cjs affil, mellon funding, spellcheck

@@
 \author[1]{Colin Raffel}
-\author[1]{Brian McFee}
+\author[1,4]{Brian McFee}
 \author[2]{Eric J. Humphrey}
@@
 \affil[1]{LabROSA, Dept. of Electrical Engineering\\Columbia University, New York}
+\affil[4]{Center for Jazz Studies\\Columbia University, New York}
 \affil[2]{Music and Audio Research Lab\\New York University, New York}
@@
 MIREX is built upon the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
-The NEMA codebase includes multiple programming languages and dependencies (some of which, \eg{} Matlab, are proprietary) so compiling and running it at individual sites is nontrivial. 
+The NEMA code-base includes multiple programming languages and dependencies (some of which, \eg{} Matlab, are proprietary) so compiling and running it at individual sites is nontrivial. 
 %
@@
 and the \textbf{Overall Accuracy}, which computes the proportion of all frames correctly estimated by the algorithm, including whether non-melody frames where labeled by the algorithm as non-melody.
-Prior to computing these metrics, both the estimate and reference sequences must be sampled onto the same timebase.
+Prior to computing these metrics, both the estimate and reference sequences must be sampled onto the same time-base.
 
@@
 
-When computing the structure annotation metrics (Pairwise Precision, Recall, and F-measure, Rand Index, and Normalized Conditional Entropy Over- and Under-Segmentation Scores), the reference and estimated labels must be sampled to a common timebase.
+When computing the structure annotation metrics (Pairwise Precision, Recall, and F-measure, Rand Index, and Normalized Conditional Entropy Over- and Under-Segmentation Scores), the reference and estimated labels must be sampled to a common time-base.
 In MIREX, a fixed sampling grid is used for the Rand Index and pairwise classification metrics, but a different sampling rate is used for each, while a fixed number of samples is used for the conditional entropy scores.
@@
 The primary motivation behind developing \mireval{} is to establish an open-source, publicly refined implementation of the most common MIR metrics.
-By encouraging MIR researchers to use the same easily understandable evaluation codebase, we can ensure that different systems are being compared fairly.
+By encouraging MIR researchers to use the same easily understandable evaluation code-base, we can ensure that different systems are being compared fairly.
 
 While we have given thorough consideration to the design choices made in \mireval{}, we recognize that standards change over time, new metrics are proposed each year, and that only a subset of MIR tasks are currently implemented in \mireval{}.
-Towards this end, \mireval{} is hosted on Github,\footnote{\url{http://github.com/craffel/mir_eval}} which provides a straightforward way of proposing changes and additions to the codebase using the Pull Request feature.
+Towards this end, \mireval{} is hosted on Github,\footnote{\url{http://github.com/craffel/mir_eval}} which provides a straightforward way of proposing changes and additions to the code-base using the Pull Request feature.
 With active community participation, we believe that \mireval{} can ensure that MIR research converges on a standard methodology for evaluation.
@@
 
-The authors would like to thank Matthew McVicar for helpful advice about comparing chord labels.  Support provided in part by NSF grant IIS-1117015.
+The authors would like to thank Matthew McVicar for helpful advice about comparing chord labels and Tom Collins
+for sharing his MATLAB implementation to evaluate musical patterns. Support provided in part by The Andrew~W.~Mellon Foundation, and NSF grant IIS-1117015.
 

### 2014-07-05 paper/paper.tex
fixed some tex spacing errors

@@
 \author[1]{Daniel P. W. Ellis}
-\affil[1]{LabROSA, Dept. of Electrical Engineering\\Columbia University, New York}
+\affil[1]{LabROSA, Dept.~of Electrical Engineering\\Columbia University, New York}
 \affil[4]{Center for Jazz Studies\\Columbia University, New York}
@@
 Much of the research in Music Information Retrieval (MIR) involves the development of systems that process raw music data to produce semantic information.
-The goal of these systems is frequently defined as attempting to duplicate the performance of a human listener given the same task \cite{downie2003toward}.
+The goal of these systems is frequently defined as attempting to duplicate the
+performance of a human listener given the same task~\cite{downie2003toward}.
 A natural way to determine a system's effectiveness might be for a human to study the output produced by the system and judge its correctness.
@@
 These metrics typically involve a heuristically-motivated comparison of the system's output to a reference which is known to be correct.
-Over time, certain metrics have become standard for each task, so that the performance of systems created by different researchers can be compared when they are evaluated over the same dataset \cite{downie2003toward}.
+Over time, certain metrics have become standard for each task, so that the performance
+of systems created by different researchers can be compared when they are evaluated
+over the same dataset~\cite{downie2003toward}.
 Unfortunately, this comparison can be confounded by small details of the implementations or procedures that can have disproportionate impacts on the resulting scores.
@@
 % MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, not used outside of MIREX, etc.
-For the past 10 years, the yearly Music Information Retrieval Evaluation eXchange (MIREX) has been a forum for comparing MIR algorithms over common datasets \cite{downie2008music}.
+For the past 10 years, the yearly Music Information Retrieval Evaluation eXchange
+(MIREX) has been a forum for comparing MIR algorithms over common datasets~\cite{downie2008music}.
 By providing a standardized shared-task setting, MIREX has become critically useful for tracking progress in MIR research.
-MIREX is built upon the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
+MIREX is built upon the Networked Environment for Music Analysis (NEMA)~\cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
 The NEMA code-base includes multiple programming languages and dependencies (some of which, \eg{} Matlab, are proprietary) so compiling and running it at individual sites is nontrivial. 
@@
 %Due to its scale, characteristics, and intended use, 
-In consequence, the NEMA system is rarely used for evaluating MIR algorithms outside of the setting of MIREX \cite{downie2008music}.
+In consequence, the NEMA system is rarely used for evaluating MIR algorithms outside of
+the setting of MIREX~\cite{downie2008music}.
 Instead, researchers often create their own implementations of common metrics for evaluating their algorithms.
@@
 Following these criteria, we present \mireval{}, a software package which intends to provide an easy and standardized way to evaluate MIR systems.
-This paper first discusses the architecture and design of \mireval{} in Section \ref{sec:architecture}, then, in Section \ref{sec:tasks}, describes all of the tasks covered by \mireval{} and the metrics included.
-In order to validate our implementation decisions, we compare \mireval{} to existing software in Section \ref{sec:comparison}.
-Finally, we discuss and summarize our contributions in Section \ref{sec:discussion}.
+This paper first discusses the architecture and design of \mireval{} in Section
+\ref{sec:architecture}, then, in Section~\ref{sec:tasks}, describes all of the tasks covered by \mireval{} and the metrics included.
+In order to validate our implementation decisions, we compare \mireval{} to existing
+software in Section~\ref{sec:comparison}.
+Finally, we discuss and summarize our contributions in Section~\ref{sec:discussion}.
 
@@
 Every metric function includes detailed documentation, example usage, input validation, and references to the original paper which defined the metric.
-\mireval{} also includes a submodule \texttt{io} which provides convenience functions for loading in task-specific data from common file formats (\eg{} comma/tab separated values, \texttt{.lab} files \cite{harte2010towards}, \etc{}).
+\mireval{} also includes a submodule \texttt{io} which provides convenience functions
+for loading in task-specific data from common file formats (\eg{} comma/tab separated
+    values, \texttt{.lab} files~\cite{harte2010towards}, \etc{}).
 For readability, all code follows the PEP8 style guide\cite{van2001pep}.
@@
 As a result, most metrics for evaluating the performance of beat tracking systems involve computing the error between the estimated beat times and some reference list of beat locations.
-Many metrics additionally compare the beat sequences at different metric levels in order to deal with the ambiguity of tempo \cite{davies2009evaluation}.
+Many metrics additionally compare the beat sequences at different metric levels in
+order to deal with the ambiguity of tempo~\cite{davies2009evaluation}.
 
-\mireval{} includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}:
+\mireval{} includes the following metrics for beat tracking, which are defined in
+detail in~\cite{davies2009evaluation}:
 The \textbf{F-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat;
@@
 
-Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for automatic chord estimation is an ongoing topic of discussion, due to issues with vocabularies, comparison semantics, and other lexicographical challenges unique to the task \cite{pauwels2013evaluating}.
-One source of difficulty stems from an inherent subjectivity in ``spelling'' a chord name and the level of detail a human observer can provide in a reference annotation \cite{ni2013understanding}.
+Despite being one of the oldest MIREX tasks, evaluation methodology and metrics for
+automatic chord estimation is an ongoing topic of discussion, due to issues with
+vocabularies, comparison semantics, and other lexicographical challenges unique to the
+task~\cite{pauwels2013evaluating}.
+One source of difficulty stems from an inherent subjectivity in ``spelling'' a chord
+name and the level of detail a human observer can provide in a reference annotation~\cite{ni2013understanding}.
 As a result, a consensus has yet to be reached regarding the single best approach to comparing two sequences of chord labels, and instead are often compared over a set of rules, i.e Root, Major-Minor, and Sevenths, with or without inversions.
 
-To efficiently compare chords, we first separate a given chord label into a its constituent parts, based on the syntax of \cite{harte2010towards}.
+To efficiently compare chords, we first separate a given chord label into a its
+constituent parts, based on the syntax of~\cite{harte2010towards}.
 For example, the chord label \texttt{G:maj(6)/5} is mapped to three pieces of information: the root (``G''), the root-invariant active semitones as determined by the quality shorthand (``maj'') and scale degrees (``6''), and the bass interval (``5'').
@@
 and finally, \textbf{Major-Minor-Inv} and \textbf{Sevenths-Inv} include Major-Minor and Sevenths respectively, but further require that the bass intervals are equivalent subject to the reference bass interval being an active semitone.
-The ``subject to...'' conditions above indicate that a comparison is \emph{ignored} during evaluation if the given criteria is not satisfied.
+The ``subject to\ldots'' conditions above indicate that a comparison is \emph{ignored} during evaluation if the given criteria is not satisfied.
 
@@
 This is achieved by forming the union of the boundaries in each sequence, sampling the labels, and summing the time intervals of the ``correct'' ranges. 
-The cumulative score, referred to as \emph{weighted chord symbol recall}, is tallied over a set audio files by discrete summation, where the importance of each score is weighted by the duration of each annotation \cite{choi2013mirex}.
+The cumulative score, referred to as \emph{weighted chord symbol recall}, is tallied
+over a set audio files by discrete summation, where the importance of each score is
+weighted by the duration of each annotation~\cite{choi2013mirex}.
 
@@
 
-Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013} which resulted in 19 different scores, each one implemented in \mireval{}:
+Collins compiled all previously existent metrics and proposed novel ones~\cite{Collins2013} which resulted in 19 different scores, each one implemented in \mireval{}:
 \textbf{Standard F-measure, Precision, and Recall}, where an estimated prototype pattern is considered correct only if it matches (up to translation) a reference prototype pattern;
@@
 \mireval{} implements the following boundary detection metrics:
-\textbf{Boundary Detection Precision, Recall, and F-measure Scores} where an estimated boundary is considered correct if it falls within a window around a reference boundary \cite{turnbull2007supervised};
-and \textbf{Boundary Deviation} which computes median absolute time difference from a reference boundary to its nearest estimated boundary, and vice versa \cite{turnbull2007supervised}.
+\textbf{Boundary Detection Precision, Recall, and F-measure Scores} where an estimated
+boundary is considered correct if it falls within a window around a reference boundary~\cite{turnbull2007supervised};
+and \textbf{Boundary Deviation} which computes median absolute time difference from a
+reference boundary to its nearest estimated boundary, and vice versa~\cite{turnbull2007supervised}.
 The following structure annotation metrics are also included:
 \textbf{Pairwise Classification Precision, Recall, and F-measure Scores} for classifying pairs of sampled time instants as belonging to the same structural component~\cite{levy2008structural};
-\textbf{Rand Index}\footnote{The MIREX results page refers to Rand Index as ``random clustering index''.} which clusters reference and estimated annotations and compares them by the Rand Index \cite{rand1971objective};
-and the \textbf{Normalized Conditional Entropy} where sampled reference and estimated labels are interpreted as samples of random variables $Y_R, Y_E$ from which the conditional entropy of $Y_R$ given $Y_E$ (\textbf{Under-Segmentation}) and $Y_E$ given $Y_R$  (\textbf{Over-Segmentation}) are estimated \cite{lukashevich2008towards}.
+\textbf{Rand Index}\footnote{The MIREX results page refers to Rand Index as ``random
+clustering index''.} which clusters reference and estimated annotations and compares
+them by the Rand Index~\cite{rand1971objective};
+and the \textbf{Normalized Conditional Entropy} where sampled reference and estimated
+labels are interpreted as samples of random variables $Y_R, Y_E$ from which the
+conditional entropy of $Y_R$ given $Y_E$ (\textbf{Under-Segmentation}) and $Y_E$ given
+$Y_R$  (\textbf{Over-Segmentation}) are estimated~\cite{lukashevich2008towards}.
 
@@
 
-Melody extraction algorithms aim to produce a sequence of frequency values corresponding to the pitch of the dominant melody from a musical recording \cite{salamon:MelodyReview:IEEESPM13}.
-An estimated pitch series is evaluated against a reference by computing the following five measures defined in \cite{salamon:MelodyReview:IEEESPM13}, first used in MIREX 2005 \cite{polinerMelodyEval}:
+Melody extraction algorithms aim to produce a sequence of frequency values
+corresponding to the pitch of the dominant melody from a musical recording~\cite{salamon:MelodyReview:IEEESPM13}.
+An estimated pitch series is evaluated against a reference by computing the following
+five measures defined in~\cite{salamon:MelodyReview:IEEESPM13}, first used in MIREX
+2005~\cite{polinerMelodyEval}:
 \textbf{Voicing Recall Rate} which computes the proportion of frames labeled as melody frames in the reference that are estimated as melody frames by the algorithm;
@@
 The goal of an onset detection algorithm is to automatically determine when notes are played in a piece of music.
-As is also done in beat tracking and segment boundary detection, the primary method used to evaluate onset detectors is to first determine which estimated onsets are ``correct'', where correctness is defined as being within a small window of a reference onset \cite{bock2012evaluating}.
+As is also done in beat tracking and segment boundary detection, the primary method
+used to evaluate onset detectors is to first determine which estimated onsets are
+``correct'', where correctness is defined as being within a small window of a reference
+onset~\cite{bock2012evaluating}.
 From this, \textbf{Precision}, \textbf{Recall}, and \textbf{F-measure} scores are computed.
@@
 For melody extraction, the ADC2004 dataset used by MIREX is publicly available.
-We performed melody extraction using the ``SG2'' algorithm evaluated in 2011 \cite{salamon:MelodyExraction:TASLP:12} and compared \mireval{}'s reported scores to those of MIREX.
-For pattern discovery, we used the development dataset released by Collins \cite{Collins2013} and used the algorithms submitted by Nieto and Farbood \cite{nieto2013discovery} for MIREX 2013 to produce estimated patterns.
-We evaluated the estimated patterns using the MATLAB code released by Collins \cite{Collins2013}.
-The number of algorithms, examples, and total number of scores for all tasks are summarized in Table \ref{tab:nexamples}.
+We performed melody extraction using the ``SG2'' algorithm evaluated in 2011~\cite{salamon:MelodyExraction:TASLP:12} and compared \mireval{}'s reported scores to those of MIREX. 
+For pattern discovery, we used the development dataset released by
+Collins~\cite{Collins2013} and used the algorithms submitted by Nieto and Farbood~\cite{nieto2013discovery} for MIREX 2013 to produce estimated patterns.
+We evaluated the estimated patterns using the MATLAB code released by Collins~\cite{Collins2013}.
+The number of algorithms, examples, and total number of scores for all tasks are
+summarized in Table~\ref{tab:nexamples}.
 
@@
 
-The resulting average relative change for each metric is presented in Table \ref{tab:comparison}.
+The resulting average relative change for each metric is presented in Table~\ref{tab:comparison}.
 The average relative change for all of the pattern discovery metrics was 0, so they are not included in this table.
@@
 
-When computing McKinney's P-score \cite{davies2009evaluation}, the beat sequences are first converted to impulse trains sampled at a 10 millisecond resolution.
+When computing McKinney's P-score~\cite{davies2009evaluation}, the beat sequences are first converted to impulse trains sampled at a 10 millisecond resolution.
 Because this sampling involves quantizing the beat times, shifting both beat sequences by a constant offset can result in substantial changes in the P-score.
@@
 In this way, the smallest beat in the estimated and reference beat sequences is always $0$ and the metric remains the same even when both beat sequences have a constant offset applied.
-This is not done in MIREX (which uses the Beat Evaluation Toolbox \cite{davies2009evaluation}), and as a result, we observe a considerable average relative change for the P-score metric.
+This is not done in MIREX (which uses the Beat Evaluation Toolbox~\cite{davies2009evaluation}), and as a result, we observe a considerable average relative change for the P-score metric.
 
@@
 
-The Information Gain metric \cite{davies2009evaluation} involves the computation a histogram of the per-beat errors.
+The Information Gain metric~\cite{davies2009evaluation} involves the computation a histogram of the per-beat errors.
 The Beat Evaluation Toolbox (and therefore MIREX) uses a non-uniform histogram binning where the first, second and last bins are smaller than the rest of the bins while \mireval{} uses a standard uniformly-binned histogram.
@@
 In MIREX, a fixed sampling grid is used for the Rand Index and pairwise classification metrics, but a different sampling rate is used for each, while a fixed number of samples is used for the conditional entropy scores.
-In \mireval{}, the same fixed sampling rate of 100 milliseconds is used for all structure annotation metrics, as specified in \cite{willis2013mirex}.
+In \mireval{}, the same fixed sampling rate of 100 milliseconds is used for all
+structure annotation metrics, as specified in~\cite{willis2013mirex}.
 
@@
 Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX.
-This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{tab:comparison}. 
-For example, \texttt{Bb:maj(9)/9} was \emph{not} excluded from the MIREX evaluation, contradicting the description provided by the task specification \cite{choi2013mirex}.
+This has proven to be particularly difficult in the two inversion rules, and manifests
+in Table~\ref{tab:comparison}. 
+For example, \texttt{Bb:maj(9)/9} was \emph{not} excluded from the MIREX evaluation,
+contradicting the description provided by the task specification~\cite{choi2013mirex}.
 This chord alone causes an observable difference between \mireval{} and MIREX's results.
@@
 
-The results in Section \ref{sec:comparison} clearly demonstrate that differences in implementation can lead to substantial differences in reported scores.
+The results in Section~\ref{sec:comparison} clearly demonstrate that differences in implementation can lead to substantial differences in reported scores.
 This corroborates the need for transparency and community involvement in comparative evaluation.

### 2014-07-07 paper/paper.tex
Spelling correction corrections

@@
 MIREX is built upon the Networked Environment for Music Analysis (NEMA)~\cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
-The NEMA code-base includes multiple programming languages and dependencies (some of which, \eg{} Matlab, are proprietary) so compiling and running it at individual sites is nontrivial. 
+The NEMA codebase includes multiple programming languages and dependencies (some of which, \eg{} Matlab, are proprietary) so compiling and running it at individual sites is nontrivial.
 %
@@
 and the \textbf{Overall Accuracy}, which computes the proportion of all frames correctly estimated by the algorithm, including whether non-melody frames where labeled by the algorithm as non-melody.
-Prior to computing these metrics, both the estimate and reference sequences must be sampled onto the same time-base.
+Prior to computing these metrics, both the estimate and reference sequences must be sampled onto the same time base.
 
@@
 
-When computing the structure annotation metrics (Pairwise Precision, Recall, and F-measure, Rand Index, and Normalized Conditional Entropy Over- and Under-Segmentation Scores), the reference and estimated labels must be sampled to a common time-base.
+When computing the structure annotation metrics (Pairwise Precision, Recall, and F-measure, Rand Index, and Normalized Conditional Entropy Over- and Under-Segmentation Scores), the reference and estimated labels must be sampled to a common time base.
 In MIREX, a fixed sampling grid is used for the Rand Index and pairwise classification metrics, but a different sampling rate is used for each, while a fixed number of samples is used for the conditional entropy scores.
@@
 The primary motivation behind developing \mireval{} is to establish an open-source, publicly refined implementation of the most common MIR metrics.
-By encouraging MIR researchers to use the same easily understandable evaluation code-base, we can ensure that different systems are being compared fairly.
+By encouraging MIR researchers to use the same easily understandable evaluation codebase, we can ensure that different systems are being compared fairly.
 
 While we have given thorough consideration to the design choices made in \mireval{}, we recognize that standards change over time, new metrics are proposed each year, and that only a subset of MIR tasks are currently implemented in \mireval{}.
-Towards this end, \mireval{} is hosted on Github,\footnote{\url{http://github.com/craffel/mir_eval}} which provides a straightforward way of proposing changes and additions to the code-base using the Pull Request feature.
+Towards this end, \mireval{} is hosted on Github,\footnote{\url{http://github.com/craffel/mir_eval}} which provides a straightforward way of proposing changes and additions to the codebase using the Pull Request feature.
 With active community participation, we believe that \mireval{} can ensure that MIR research converges on a standard methodology for evaluation.

### 2014-07-11 paper/paper.tex
fixed affiliation numbering, back down to 6 pages

@@
 \author[1]{Colin Raffel}
-\author[1,4]{Brian McFee}
-\author[2]{Eric J. Humphrey}
-\author[2,3]{Justin Salamon}
-\author[2]{Oriol Nieto}
+\author[1,2]{Brian McFee}
+\author[3]{Eric J. Humphrey}
+\author[3,4]{Justin Salamon}
+\author[3]{Oriol Nieto}
 \author[1]{Dawen Liang}
@@
 \affil[1]{LabROSA, Dept.~of Electrical Engineering\\Columbia University, New York}
-\affil[4]{Center for Jazz Studies\\Columbia University, New York}
-\affil[2]{Music and Audio Research Lab\\New York University, New York}
-\affil[3]{Center for Urban Science and Progress\\New York University, New York}
+\affil[2]{Center for Jazz Studies\\Columbia University, New York}
+\affil[3]{Music and Audio Research Lab\\New York University, New York}
+\affil[4]{Center for Urban Science and Progress\\New York University, New York}
 
@@
 For readability, all code follows the PEP8 style guide\cite{van2001pep}.
-\mireval{}'s only dependencies outside of the Python standard library are the free and open-source \texttt{SciPy}/\texttt{Numpy}\cite{jones2001scipy} and \texttt{scikit-learn}\cite{pedregosa2011scikit} Python libraries.
+\mireval{}'s only dependencies outside of the Python standard library are the free and open-source \texttt{SciPy}/\texttt{Numpy}\cite{jones2001scipy} and \texttt{scikit-learn}\cite{pedregosa2011scikit} libraries.
 

### 2014-07-15 paper/paper.tex
Added EJH funding ack

@@
 
-The authors would like to thank Matthew McVicar for helpful advice about comparing chord labels and Tom Collins
-for sharing his MATLAB implementation to evaluate musical patterns. Support provided in part by The Andrew~W.~Mellon Foundation, and NSF grant IIS-1117015.
+The authors would like to thank Matthew McVicar for helpful advice on comparing chord labels and Tom Collins
+for sharing his MATLAB implementation to evaluate musical patterns. 
+Support provided in part by The Andrew~W.~Mellon Foundation and the National Science Foundation, under grants IIS-0844654 and IIS-1117015.
 

### 2014-07-16 paper/paper.tex
Author edits thanks to @ejhumphrey
Camera ready

@@
 
+\renewcommand\Authfont{\bfseries}
+
 \title{\mireval{}:\\
@@
 
-\author[1]{Colin Raffel}
+\author[1,*]{Colin Raffel}
 \author[1,2]{Brian McFee}
@@
 \author[3]{Oriol Nieto}
-\author[1]{Dawen Liang}
+\author[1]{\authorcr Dawen Liang}
 \author[1]{Daniel P. W. Ellis}
@@
 \maketitle
+
+\let\oldthefootnote\thefootnote
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+\footnotetext[1]{Please direct correspondence to \url{craffel@gmail.com}}
+\let\thefootnote\oldthefootnote
+
 %
@@
 \textbf{Standard F-measure, Precision, and Recall}, where an estimated prototype pattern is considered correct only if it matches (up to translation) a reference prototype pattern;
-\textbf{Establishment F-measure, Precision, and Recall}, which computes the number of reference patterns that were successfully found, no matter how many occurrences were found;
-\textbf{Occurrence F-measure, Precision, and Recall}, which measures whether an algorithm is able to retrieve all occurrences of a pattern;
+\textbf{Establishment F-measure, Precision, and Recall}, which compute the number of reference patterns that were successfully found, no matter how many occurrences were found;
+\textbf{Occurrence F-measure, Precision, and Recall}, which measure whether an algorithm is able to retrieve all occurrences of a pattern;
 \textbf{Three-layer F-measure, Precision, and Recall}, which capture both the establishment of the patterns and the occurrence retrieval in a single set of scores;
-and the \textbf{First $N$ patterns metrics}, which computes the target proportion establishment recall and three-layer precision for the first $N$ patterns only in order to measure the ability of the algorithm to sort the identified patterns based on their relevance.
+and the \textbf{First $N$ patterns metrics}, which compute the target proportion establishment recall and three-layer precision for the first $N$ patterns only in order to measure the ability of the algorithm to sort the identified patterns based on their relevance.
 
@@
 
-The Information Gain metric~\cite{davies2009evaluation} involves the computation a histogram of the per-beat errors.
+The Information Gain metric~\cite{davies2009evaluation} involves the computation of a histogram of the per-beat errors.
 The Beat Evaluation Toolbox (and therefore MIREX) uses a non-uniform histogram binning where the first, second and last bins are smaller than the rest of the bins while \mireval{} uses a standard uniformly-binned histogram.

### 2014-10-12 paper/poster.tex
Poster

\documentclass[paperwidth=120cm,paperheight=150cm,portrait,fontscale=.22,margin=5cm,lmargin=.2cm,rmargin=.2cm]{baposter}

\usepackage{minted}
\definecolor{mintedbg}{rgb}{0.95,0.95,0.95}

\usepackage{upquote}
\AtBeginDocument{%
\def\PYZsq{\textquotesingle}%
}

\definecolor{bordercol}{RGB}{40,40,40}
\definecolor{headercol1}{RGB}{235,218,229}
\definecolor{headercol2}{RGB}{80,80,80}
\definecolor{headerfontcol}{RGB}{0,0,0}
\definecolor{boxcolor}{RGB}{255,235,205}

\renewcommand{\familydefault}{\sfdefault}

\def\mireval{\texttt{mir\char`_eval}}

\usepackage{tabularx}
\usepackage{booktabs}

\begin{document}

\begin{poster}{
  background=plain,
  bgColorOne=white,
  headerheight=0.1\textheight,
  eyecatcher=true,
  columns=2,
  borderColor=bordercol,
  headerColorOne=headercol1,
  headerColorTwo=headercol1,
  headerFontColor=headerfontcol,
  headerfont=\textmd,
  boxColorOne=boxcolor,
  linewidth=0.5pt,
  borderColor=black,
  headerborder=none,
  textborder=none,
}
{\includegraphics[height=8em]{labrosa-new-nobg.pdf}}
{\textmd{MIR\char`_EVAL:$\;$A$\;$TRANPARENT$\;$IMPLEMENTATION\\OF$\;$COMMON$\;$MIR$\;$METRICS}}
{Colin Raffel, Brian McFee, Eric J. Humphrey, Justin Salamon, Oriol Nieto, Dawen Liang,\\[.2em] and Daniel P. W. Ellis\\[.2em]}
{\includegraphics[height=6em]{marl-logo.pdf}}

\begin{posterbox}[column=0]{Abstract}
We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
We performed a quantitative comparison of \mireval{} to existing evaluation systems to explore differences in implementation.
\end{posterbox}

\begin{posterbox}[column=0,below=auto]{Design}

\mireval{} is a Python library which currently includes metrics for the following tasks: \textbf{Beat detection, chord estimation, pattern discovery, structural segmentation, melody extraction}, and \textbf{onset detection}.
Each task is given its own submodule, and each metric is defined as a separate function in each submodule.
Each task submodule also includes common data pre-processing steps for the task.
Every metric function includes detailed documentation, example usage, input validation, and references to the original paper which defined the metric.
\mireval{} also includes a submodule \texttt{io} which provides convenience functions for loading in task-specific data from common file formats.
In order to simplify the usage of \mireval{}, it is packaged with a set of ``evaluator'' scripts, one for each task.
These scripts include all code necessary to load in data, pre-process it, and compute all metrics for a given task.
The evaluators allow for \mireval{} to be called directly from the command line so that no knowledge of Python is necessary.

\end{posterbox}

\begin{posterbox}[column=1]{Comparison to Existing Implementations}

In order to validate the design choices made in \mireval{}, we compared the scores it produces to those reported by the evaluation systems used in MIREX.
Beyond pinpointing intentional differences in implementation, this process can also help find and fix bugs in either \mireval{} or the system it is being compared to.
For each task covered by \mireval{}, we obtained a collection of reference and estimated annotations and computed or obtained a score for each metric using \mireval{} and the evaluation system being compared to.
Then, for each reported score, we computed the relative change between the scores as their absolute difference divided by their mean.
Finally, we computed the average relative change across all examples in the obtained dataset for each score.
The number of algorithms, examples, and total number of scores for all tasks are summarized in the following table.

\begin{center}
\begin{tabular}{l r r r}
\toprule
Task & Algorithms & Examples & Scores\\
\midrule
Beat Detection & 20 & 679 & 13580\\
Segmentation & 8 & 1397 & 11176 \\
Onset Detection & 11 & 85 & 935 \\
Chord Estimation & 12 & 217 & 2604 \\
Melody & 1 & 20 & 20 \\
Pattern Discovery & 4 & 5 & 20 \\
\bottomrule
\end{tabular}
\end{center}

\vspace{-2.5mm}

\end{posterbox}

\begin{posterbox}[column=0,below=auto,span=2]{Average Relative Difference of \mireval{} vs. MIREX}

\begin{center}
\begin{tabularx}{.95\linewidth}{*{9}{>{\centering\arraybackslash}X}}
%\toprule
 \multicolumn{9}{ c }{\textbf{Beat Detection}} \\
  \cmidrule(lr){1-9}
F-measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt       & AMLc       & AMLt       & In. Gain   \\
   0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% &    0.137\% &    0.139\% &    9.174\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{.95\linewidth}{*{9}{>{\centering\arraybackslash}X}}
 \multicolumn{9}{ c }{\textbf{Structural Segmentation}} \\
  \cmidrule(lr){1-9}
  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5  \\
3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\%  \\
  \midrule
\end{tabularx}
\begin{tabularx}{.95\linewidth}{*{8}{>{\centering\arraybackslash}X}}
 \multicolumn{5}{ c }{\textbf{Structural Segmentation (continued)}} & \multicolumn{3}{ c }{\textbf{Onset Detection}}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-8}
  F@3 &   P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-measure  & Precision  & Recall     \\
 0.393\%  & 0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.165\% &    0.165\% &    0.165\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{.95\linewidth}{*{2}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c c}
 \multicolumn{5}{ c }{\textbf{Chord Estimation}} & \multicolumn{5}{ c }{\textbf{Melody Extraction}}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-10}
  Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw pitch & Chroma & Voicing R & Voicing FA \\
 0.007\% & 0.163\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
%\bottomrule
\end{tabularx}
\end{center}

\end{posterbox}

\begin{posterbox}[column=0,below=auto,span=2,boxColorOne=white]{}

\begin{minted}[bgcolor=mintedbg, frame=single, framerule=0pt, fontsize=\large]{python}
import mir_eval
# Load in beat annotations
reference_beats = mir_eval.io.load_events('reference_beats.txt')
estimated_beats = mir_eval.io.load_events('estimated_beats.txt')
# scores will be a dictionary where the key is the metric name and the value is the score achieved
scores = mir_eval.beat.evaluate(reference_beats, estimated_beats)
# evaluate() will pass keyword args to the metric functions
scores = mir_eval.beat.evaluate(reference_beats, estimated_beats, f_measure_threshold=0.05)
# You can also perform pre-processing and compute each metric manually
reference_beats = mir_eval.beat.trim_beats(reference_beats)
estimated_beats = mir_eval.beat.trim_beats(estimated_beats)
f_score = mir_eval.beat.f_measure(reference_beats, estimated_beats, f_measure_threshold=0.05)
\end{minted}

$\;$\\[-1em]

\begin{minted}[bgcolor=mintedbg, frame=single, framerule=0pt, fontsize=\large]{c}
> ./onset_eval.py reference_onsets.txt estimated_onsets.txt -o output.json
reference_onsets.txt vs. estimated_onsets.txt
  F-measure : 0.531
  Precision : 0.481
     Recall : 0.591
Saving results to:  output.json
\end{minted}

\centering\huge
\texttt{http://www.github.com/craffel/mir\_eval}

\end{posterbox}

\end{poster}

\end{document}

### 2014-10-12 paper/poster.tex
Final poster

@@
 
-\begin{posterbox}[column=0]{Abstract}
+\begin{posterbox}[name=abstract,column=0]{Abstract}
 We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
@@
 
-\begin{posterbox}[column=0,below=auto]{Design}
+\begin{posterbox}[name=design,column=0,below=abstract]{Design}
 
@@
 
-\begin{posterbox}[column=1]{Comparison to Existing Implementations}
+\begin{posterbox}[name=comparison,column=1]{Comparison to Existing Implementations}
 
@@
 
-\begin{posterbox}[column=0,below=auto,span=2]{Average Relative Difference of \mireval{} vs. MIREX}
+\begin{posterbox}[name=average,column=0,below=design,span=2]{Average Relative Difference of \mireval{} vs. MIREX}
 
@@
 
-\begin{posterbox}[column=0,below=auto,span=2,boxColorOne=white]{}
+\begin{posterbox}[name=python,column=0,below=average]{Using \mireval{} in Python}
 
-\begin{minted}[bgcolor=mintedbg, frame=single, framerule=0pt, fontsize=\large]{python}
+\begin{minted}[bgcolor=boxcolor, frame=single, framerule=0pt]{python}
 import mir_eval
 # Load in beat annotations
-reference_beats = mir_eval.io.load_events('reference_beats.txt')
-estimated_beats = mir_eval.io.load_events('estimated_beats.txt')
-# scores will be a dictionary where the key is the metric name and the value is the score achieved
+reference_beats = mir_eval.io.load_events('ref_beats.txt')
+estimated_beats = mir_eval.io.load_events('est_beats.txt')
+# scores will be a dictionary where the key is the metric name
+# and the value is the score achieved
 scores = mir_eval.beat.evaluate(reference_beats, estimated_beats)
 # evaluate() will pass keyword args to the metric functions
-scores = mir_eval.beat.evaluate(reference_beats, estimated_beats, f_measure_threshold=0.05)
-# You can also perform pre-processing and compute each metric manually
+scores = mir_eval.beat.evaluate(reference_beats, estimated_beats,
+                                f_measure_threshold=0.05,
+                                cemgil_sigma=0.02)
+# You can also perform pre-processing and compute metrics manually
 reference_beats = mir_eval.beat.trim_beats(reference_beats)
 estimated_beats = mir_eval.beat.trim_beats(estimated_beats)
-f_score = mir_eval.beat.f_measure(reference_beats, estimated_beats, f_measure_threshold=0.05)
+f_meas = mir_eval.beat.f_measure(reference_beats, estimated_beats,
+                                 f_measure_threshold=0.05)
+cemgil = mir_eval.beat.cemgil(reference_beats, estimated_beats,
+                              cemgil_sigma=0.02)
 \end{minted}
 
-$\;$\\[-1em]
+\end{posterbox}
 
-\begin{minted}[bgcolor=mintedbg, frame=single, framerule=0pt, fontsize=\large]{c}
-> ./onset_eval.py reference_onsets.txt estimated_onsets.txt -o output.json
-reference_onsets.txt vs. estimated_onsets.txt
-  F-measure : 0.531
-  Precision : 0.481
-     Recall : 0.591
-Saving results to:  output.json
+\begin{posterbox}[name=evaluator,column=1,below=average]{Using the evaluator scripts}
+
+\begin{minted}[bgcolor=boxcolor, frame=single, framerule=0pt]{bash}
+> ./onset_eval.py ref_beats.txt est_beats.txt -o scores.json
+
+  ref_beats.txt vs. est_beats.txt
+                          F-measure : 0.622
+                             Cemgil : 0.362676699474
+           Cemgil Best Metric Level : 0.362676699474
+                               Goto : 0.000
+                            P-score : 0.828185328185
+    Correct Metric Level Continuous : 0.0328185328185
+         Correct Metric Level Total : 0.65444015444
+        Any Metric Level Continuous : 0.0328185328185
+             Any Metric Level Total : 0.65444015444
+                   Information gain : 0.20492902479
+  Saving results to:  scores.json
+
+> cat scores.json
+
+  {"F-measure": 0.6216216216216, "Cemgil": 0.36267669947376, ...
 \end{minted}
+
+\end{posterbox}
+
+\begin{posterbox}[name=url,column=0,below=python,span=2,boxColorOne=white]{}
 

### 2014-10-12 paper/craze.tex
Poster craze

\documentclass[paperwidth=120cm,paperheight=90cm,portrait,fontscale=.22,margin=5cm,lmargin=.2cm,rmargin=.2cm]{baposter}

\usepackage{minted}
\definecolor{mintedbg}{rgb}{0.95,0.95,0.95}

\usepackage{upquote}
\AtBeginDocument{%
\def\PYZsq{\textquotesingle}%
}

\definecolor{bordercol}{RGB}{40,40,40}
\definecolor{headercol1}{RGB}{235,218,229}
\definecolor{headercol2}{RGB}{80,80,80}
\definecolor{headerfontcol}{RGB}{0,0,0}
\definecolor{boxcolor}{RGB}{255,235,205}

\renewcommand{\familydefault}{\sfdefault}

\def\mireval{\texttt{mir\char`_eval}}

\usepackage{tabularx}
\usepackage{booktabs}

\begin{document}

\begin{poster}{
  background=plain,
  bgColorOne=white,
  headerheight=0.18\textheight,
  eyecatcher=true,
  columns=1,
  borderColor=bordercol,
  headerColorOne=headercol1,
  headerColorTwo=headercol1,
  headerFontColor=headerfontcol,
  headerfont=\textmd,
  boxColorOne=white,
  linewidth=0.5pt,
  borderColor=black,
  headerborder=none,
  textborder=none,
}
{\includegraphics[height=8em]{labrosa-new-nobg.pdf}}
{\textmd{MIR\char`_EVAL:$\;$A$\;$TRANPARENT$\;$IMPLEMENTATION\\OF$\;$COMMON$\;$MIR$\;$METRICS}}
{Colin Raffel, Brian McFee, Eric J. Humphrey, Justin Salamon, Oriol Nieto, Dawen Liang,\\[.2em] and Daniel P. W. Ellis\\[.2em]}
{\includegraphics[height=6em]{marl-logo.pdf}}

\begin{posterbox}[]{}
\Huge
\mireval{} is a Python module which includes metrics for the following tasks: \textbf{Beat detection, chord estimation, pattern discovery, structural segmentation, melody extraction}, and \textbf{onset detection}.
It's easy to use in Python:
\end{posterbox}

\begin{posterbox}[below=auto]{}

\begin{minted}[bgcolor=boxcolor, frame=single, framerule=0pt, fontsize=\Large]{python}
import mir_eval
# Load in beat annotations
reference_beats = mir_eval.io.load_events('ref_beats.txt')
estimated_beats = mir_eval.io.load_events('est_beats.txt')
# scores will be a dictionary where the key is the metric name and the value is the score achieved
scores = mir_eval.beat.evaluate(reference_beats, estimated_beats)
\end{minted}

\end{posterbox}

\begin{posterbox}[below=auto]{}
\Huge
or without Python, using the included evaluator scripts:
\end{posterbox}

\begin{posterbox}[name=evaluator,below=auto]{}

\begin{minted}[bgcolor=boxcolor, frame=single, framerule=0pt, fontsize=\Large]{bash}
> ./beat_eval.py ref_beats.txt est_beats.txt -o scores.json
> cat scores.json
  {"F-measure": 0.6216216216216, "Cemgil": 0.36267669947376, "Cemgil Best Metric Level": ...
\end{minted}

\end{posterbox}

\begin{posterbox}[below=auto]{}
\Huge
We also quantitatively compared it to MIREX with some intriguing results!
\end{posterbox}

\end{poster}

\end{document}

### 2014-10-14 code/beat/beat.py
Changing print format

@@ -185,7 +185,7 @@ mirex_scores = np.vstack(mirex_scores)
 
 # <codecell>
 
-np.set_printoptions(precision=5, threshold=10000, linewidth=150, suppress=True)
+np.set_printoptions(precision=3, threshold=10000, linewidth=150, suppress=True)
 
 # <codecell>
 
@@ -196,9 +196,8 @@ score_mean = score_mean + (score_mean == 0)
 
 diff = np.round(mirex_scores, 3) - np.round(mir_eval_scores, 3)
 diff[np.less_equal(np.abs(diff), .0010001)] = 0
-print ' ',
-for n, key in enumerate(METRIC_KEYS):
-    print '{:8s}'.format(key[:7]),
-print
-print np.mean(np.abs(diff)/score_mean, axis=0)
+print ' & '.join(['{:10s}'.format(key.replace('McKinney', '')) for key in METRIC_KEYS]),
+print '\\\\'
+print ' & '.join(['{:8.3f}\%'.format(score*100) for score in np.mean(np.abs(diff)/score_mean, axis=0)]),
+print '\\\\'
 

### 2014-10-14 code/melody/melody.py
Changing output formatting

@@ -251,13 +251,12 @@ score_mean = score_mean + (score_mean == 0)
 
 # <codecell>
 
-diff = np.round(mirex_scores, 4) - np.round(mir_eval_scores, 4)
-diff[np.less_equal(np.abs(diff), .00010001)] = 0
-print ' ',
-for n, key in enumerate(METRIC_KEYS):
-    print '{:13s}'.format(key[:12]),
-print
-print np.mean(np.abs(diff)/score_mean, axis=0)
+diff = np.round(mirex_scores, 3) - np.round(mir_eval_scores, 3)
+diff[np.less_equal(np.abs(diff), .0010001)] = 0
+print ' & '.join(['{:10s}'.format(key) for key in METRIC_KEYS]),
+print '\\\\'
+print ' & '.join(['{:8.3f}\%'.format(score*100) for score in np.mean(np.abs(diff)/score_mean, axis=0)]),
+print '\\\\'
 
 # <codecell>
 

### 2014-10-14 code/beat/beat.py
METRICS is no longer used

@@ -122,15 +122,15 @@ def get_mir_eval_scores(reference_beats, estimated_beats):
     F-Measure,Cemgil,Goto,McKinney P-score,CMLc,CMLt,AMLc,AMLt,D (bits)
     '''
     scores = []
-    for metric_name in ['F-measure', 'Cemgil', 'Goto', 'P-score', 'Continuity', 'Information Gain']:
-        
-        metric_output = mir_eval.beat.METRICS[metric_name](np.sort(mir_eval.beat.trim_beats(reference_beats)),
-                                                           np.sort(mir_eval.beat.trim_beats(estimated_beats)))
+    for metric in [mir_eval.beat.f_measure, mir_eval.beat.cemgil, mir_eval.beat.goto, mir_eval.beat.p_score,
+                   mir_eval.beat.continuity, mir_eval.beat.information_gain]:
+        metric_output = metric(np.sort(mir_eval.beat.trim_beats(reference_beats)),
+                               np.sort(mir_eval.beat.trim_beats(estimated_beats)))
         # MIREX only reports Cemgil for no metric variations
-        if metric_name == 'Cemgil':
+        if metric == mir_eval.beat.cemgil:
             scores.append(metric_output[0])
         # MIREX reports unnormalized information gain, we normalize by log2(41)
-        elif metric_name == 'Information Gain':
+        elif metric == mir_eval.beat.information_gain:
             scores.append(metric_output*np.log2(41.)/100.)
         else:
             # Some metrics return tuples

### 2014-10-14 code/melody/melody.py
Updating to not use METRICS dictionary and to match ref_v, ref_c, est_v, est_c call/return order, removing unecessary fetching of MIREX data

@@ -6,13 +6,9 @@
 import urllib
 import glob
 import os
-import sys
-sys.path.append('../')
-import convert_json_instants_to_lab
 import shutil
 import csv
 import mir_eval
-import scipy.interpolate
 import numpy as np
 
 # <codecell>
@@ -20,113 +16,6 @@ import numpy as np
 BASE_DATA_PATH = '../../data/melody'
 METRIC_KEYS = ['Overall Accuracy', 'Raw Pitch Accuracy', 'Raw Chroma Accuracy', 'Voicing Recall Rate', 'Voicing False-Alarm Rate']
 ALG_NAMES = ['SG2']
-
-# <codecell>
-
-# Download MIREX's reported files, which are subsampled to 50ms
-subsampled_dir = os.path.join(BASE_DATA_PATH, 'raw_50ms_js')
-try:
-    os.makedirs(subsampled_dir)
-except OSError:
-    pass
-JS_URL = 'http://nema.lis.illinois.edu/nema_out/mirex2011/results/ame/adc04/sg2melodytranscriptmeladc040000{:02d}.js'
-for n in xrange(12):
-    file_url = JS_URL.format(n)
-    urllib.urlretrieve(file_url, os.path.join(subsampled_dir, os.path.split(file_url)[1]))
-JS_URL = 'http://nema.lis.illinois.edu/nema_out/mirex2011/results/ame/adc04/sg2melodytranscriptmeladc04nv00000{}.js'
-for n in xrange(8):
-    file_url = JS_URL.format(n)
-    urllib.urlretrieve(file_url, os.path.join(subsampled_dir, os.path.split(file_url)[1]))
-
-# <codecell>
-
-# Maps between ADC2004 names and MIREX names
-FILENAME_MAPPING = {'opera_male5REF.txt' : 'sg2melodytranscriptmeladc04000000.js',
-                    'daisy3REF.txt' : 'sg2melodytranscriptmeladc04000001.js',
-                    'daisy1REF.txt' : 'sg2melodytranscriptmeladc04000002.js',
-                    'daisy2REF.txt' : 'sg2melodytranscriptmeladc04000003.js',
-                    'opera_male3REF.txt' : 'sg2melodytranscriptmeladc04000004.js',
-                    'daisy4REF.txt' : 'sg2melodytranscriptmeladc04000005.js',
-                    'pop1REF.txt' : 'sg2melodytranscriptmeladc04000006.js',
[…]

### 2014-10-14 code/onset/onset.py
Removing cruft, changing output formatting, moving makedirs to the top

@@ -17,8 +17,37 @@ import numpy as np
 # <codecell>
 
 BASE_DATA_PATH = '../../data/onset/'
+
 METRIC_KEYS = ['Average F-Measure', 'Average precision', 'Average recall']
 ALG_NAMES = ['CB1','CF4','CSF1','FMEGS1','FMESS1','MTB1','SB1','SB2','SB3','SB4','ZHZD1']
+
+# <codecell>
+
+try:
+    os.makedirs(BASE_DATA_PATH)
+except OSError:
+    pass
+
+js_dir = os.path.join(BASE_DATA_PATH, 'raw_js_data')
+reference_dir = os.path.join(BASE_DATA_PATH, 'reference')
+csv_dir = os.path.join(BASE_DATA_PATH, 'mirex_scores_raw')
+
+try:
+    os.makedirs(js_dir)
+except OSError:
+    pass
+try:
+    os.makedirs(reference_dir)
+except OSError:
+    pass
+try:
+    os.makedirs(csv_dir)
+except OSError:
+    pass
+try:
+    os.makedirs(os.path.join(BASE_DATA_PATH, 'mir_eval_scores'))
+except OSError:
+    pass
 
 # <codecell>
 
@@ -26,16 +55,11 @@ N_FILES = 85
 JS_URL = "http://nema.lis.illinois.edu/nema_out/mirex2013/results/aod/transcriptiononsetmrx050000{:02d}.js"
 for n in xrange(N_FILES):
     file_url = JS_URL.format(n)
-    urllib.urlretrieve(file_url, os.path.join(BASE_DATA_PATH, 'raw_js_data', os.path.split(file_url)[1]))
+    urllib.urlretrieve(file_url, os.path.join(js_dir, os.path.split(file_url)[1]))
 
 # <codecell>
 
 RESULT_URL = "http://nema.lis.illinois.edu/nema_out/mirex2013/results/aod/{}/per_track_results.csv"
-csv_dir = os.path.join(BASE_DATA_PATH, 'mirex_scores_raw')
-try:
-    os.makedirs(csv_dir)
-except OSError:
-    pass
 for alg in ALG_NAMES:
     file_url = RESULT_URL.format(alg)
     urllib.urlretrieve(file_url, os.path.join(csv_dir, alg + '.csv'))
@@ -62,18 +86,6 @@ for filename in glob.glob(os.path.join(csv_dir, '*.csv')):
 
 # <codecell>
 
[…]

### 2014-10-14 code/pattern/pattern.py
Removing cruft

@@ -43,14 +43,6 @@ with open(os.path.join(BASE_DATA_PATH, 'matlab_scores_raw', 'resultsMATLAB.txt')
 
 # <codecell>
 
-mir_eval.pattern.METRICS.keys()
-
-# <codecell>
-
-help(mir_eval.pattern.first_n_target_proportion_R)
-
-# <codecell>
-
 def get_mir_eval_scores(reference_pattern, estimated_pattern):
     ''' Computes all mir_eval pattern metrics and returns them in the correct order
     '''
@@ -159,10 +151,4 @@ diff[np.less_equal(np.abs(diff), .00010001)] = 0
 relative_change = np.mean(np.abs(diff)/score_mean, axis=0)
 for metric_name, change in zip(METRIC_KEYS, relative_change):
     print metric_name, ':', change*100, '%'
-
-# <codecell>
-
-for filename, d in zip(score_glob, np.round(diff, 3)):
-    print filename
-    print d
 

### 2014-10-14 code/segmentation/segmentation.py
Output formatting

@@ -268,8 +268,12 @@ score_mean = score_mean + (score_mean == 0)
 
 # <codecell>
 
-diff = np.round(mirex_scores, 4) - np.round(mir_eval_scores, 4)
-diff[np.less_equal(np.abs(diff), .00010001)] = 0
-for n, (key, score) in enumerate(zip(METRIC_KEYS, np.mean(np.abs(diff)/score_mean, axis=0))):
-    print "{} : {:.5f}".format(key, score)
+diff = np.round(mirex_scores, 3) - np.round(mir_eval_scores, 3)
+diff[np.less_equal(np.abs(diff), .0010001)] = 0
+print ' & '.join(['{:10s}'.format(key) for key in ['NCE-Over', 'NCE-under', 'Pairwise F', 'Pairwise P',
+                                                   'Pairwise R', 'Rand', 'F@.5', 'P@.5', 'R@.5',
+                                                   'F@3', 'P@3', 'R@3', 'Ref-est dev.', 'Est-ref dev.']]),
+print '\\\\'
+print ' & '.join(['{:8.3f}\%'.format(score*100) for score in np.mean(np.abs(diff)/score_mean, axis=0)]),
+print '\\\\'
 

### 2014-10-14 code/onset/onset.py
A way better way to check for dir existence

@@ -23,31 +23,22 @@ ALG_NAMES = ['CB1','CF4','CSF1','FMEGS1','FMESS1','MTB1','SB1','SB2','SB3','SB4'
 
 # <codecell>
 
-try:
+if not os.path.exists(BASE_DATA_PATH):
     os.makedirs(BASE_DATA_PATH)
-except OSError:
-    pass
 
 js_dir = os.path.join(BASE_DATA_PATH, 'raw_js_data')
 reference_dir = os.path.join(BASE_DATA_PATH, 'reference')
 csv_dir = os.path.join(BASE_DATA_PATH, 'mirex_scores_raw')
+estimated_dir = os.path.join(BASE_DATA_PATH, 'estimated')
 
-try:
+if not os.path.exists(js_dir):
     os.makedirs(js_dir)
-except OSError:
-    pass
-try:
+if not os.path.exists(reference_dir):
     os.makedirs(reference_dir)
-except OSError:
-    pass
-try:
+if not os.path.exists(csv_dir):
     os.makedirs(csv_dir)
-except OSError:
-    pass
-try:
+if not os.path.exists(os.path.join(BASE_DATA_PATH, 'mir_eval_scores')):
     os.makedirs(os.path.join(BASE_DATA_PATH, 'mir_eval_scores'))
-except OSError:
-    pass
 
 # <codecell>
 
@@ -78,10 +69,8 @@ for filename in glob.glob(os.path.join(csv_dir, '*.csv')):
                 output_path = filename.replace('mirex_scores_raw', 'mirex_scores')
                 output_path = os.path.join(os.path.split(output_path)[0], os.path.split(output_path)[1].replace('.csv', ''))
                 # Make sure output dir exists
-                try:
+                if not os.path.exists(output_path):
                     os.makedirs(output_path)
-                except OSError:
-                    pass
                 np.savetxt(os.path.join(output_path, output_filename), [float(x) for x in row[2:]])
 
 # <codecell>
@@ -93,8 +82,6 @@ for filename in glob.glob(os.path.join(js_dir, '*.js')):
 for filename in glob.glob(os.path.join(reference_dir, '*', '*.lab')):
     shutil.move(filename, filename.replace('.lab', '.txt'))
     
-estimated_dir = os.path.join(BASE_DATA_PATH, 'estimated')
-        
 for alg_name in ALG_NAMES:
     shutil.move(os.path.join(reference_dir, alg_name), os.path.join(estimated_dir, alg_name))
 
[…]

### 2014-10-14 code/segmentation/test_segment.py
Not using this for the actual test.

@@ -1,129 +1,0 @@
-'''
-Unit tests for mir_eval.segment
-'''
-
-import numpy as np
-import json
-import mir_eval
-import glob
-
-# We only need 1% absolute tolerance
-A_TOL = 1e-2
-
-# Path to the fixture files
-REF_GLOB    = 'data/ref*.lab'
-EST_GLOB    = 'data/est*.lab'
-MIREX_GLOB  = 'data/score*.json'
-
-def generate_data():
-
-    ref_files = sorted(glob.glob(REF_GLOB))
-    est_files = sorted(glob.glob(EST_GLOB))
-    sco_files = sorted(glob.glob(MIREX_GLOB))
-
-    for ref_f, est_f, sco_f in zip(ref_files, est_files, sco_files):
-        ref_t, ref_l = mir_eval.io.load_intervals(ref_f)
-        est_t, est_l = mir_eval.io.load_intervals(est_f)
-
-        with open(sco_f, 'r') as f:
-            scores = json.load(f)
-
-        yield ref_t, ref_l, est_t, est_l, scores
-
-def test_boundary_detection():
-
-    def __test_detection(_window, _ref_t, _est_t):
-        precision, recall, fmeasure = mir_eval.boundary.detection(_ref_t, _est_t, window=_window)
-
-        assert np.allclose(precision,   scores['P@%.1f'%_window], atol=A_TOL)
-        assert np.allclose(recall,      scores['R@%.1f'%_window], atol=A_TOL)
-        assert np.allclose(fmeasure,    scores['F@%.1f'%_window], atol=A_TOL)
-
-    # Iterate over fixtures
-    for ref_t, ref_l, est_t, est_l, scores in generate_data():
-
-        # Test boundary detection at each window size
-        for window in [0.5, 3.0]:
-            yield (__test_detection, window, ref_t, est_t)
-
-    # Done
-    pass
-
-def test_boundary_deviation():
-    def __test_deviation(_ref_t, _est_t):
-        t_to_p, p_to_t = mir_eval.boundary.deviation(_ref_t, _est_t)
-
-        assert np.allclose(t_to_p,  scores['T_to_P'], atol=A_TOL)
-        assert np.allclose(p_to_t,  scores['P_to_T'], atol=A_TOL)
-
-    # Iterate over fixtures
-    for ref_t, ref_l, est_t, est_l, scores in generate_data():
[…]

### 2014-10-14 code/chord/chord.py
Changing chord to match structure of other tests

@@ -1,63 +1,109 @@
-'''
-Compare mir_eval against MIREX 2013 chord results
-'''
+# -*- coding: utf-8 -*-
+# <nbformat>3.0</nbformat>
 
-import json
+# <codecell>
+
+import glob
+import os
+import csv
+import mir_eval
+import sys
 import numpy as np
-from mir_eval import chord
-from os.path import basename
+sys.path.append('../')
+import convert_json_labels_to_lab
+import shutil
+import joblib
+import urllib
+import collections
 
-# Consists of three aligned lists
-#   referece_files
-#   estimation_files
-#   scores
-result_json_file = "./data/mirex_results.json"
-with open(result_json_file) as fp:
-    results = json.load(fp)
+# <codecell>
 
-VOCABS = ['root', 'majmin', 'majmin-inv', 'sevenths', 'sevenths-inv']
-MIREX_VOCABS = [
-    "resultsMirexRoot", "resultsMirexMajMin", "resultsMirexMajMinBass",
-    "resultsMirexSevenths", "resultsMirexSeventhsBass"]
+BASE_DATA_PATH = '../../data/chord/'
+# What MIREX calls the vocabs
+MIREX_VOCABS = ["resultsMirexRoot", "resultsMirexMajMin", "resultsMirexMajMinBass",
+                "resultsMirexSevenths", "resultsMirexSeventhsBass"]
+# What mir_eval calls the vocabs
+VOCABS = ['root', 'majmin', 'majmin_inv', 'sevenths', 'sevenths_inv']
+ALG_NAMES = ['CB3', 'CB4', 'CF2', 'KO1', 'KO2', 'NG1', 'NG2', 'NMSD1', 'NMSD2', 'PP3', 'PP4', 'SB8']
 
+# <codecell>
 
-def filebase(fpath):
-    return basename(fpath).split('.')[0]
+# Convert scores in mirex_scores_raw to the format we want
+# These csv files come from http://music-ir.org/mirex/results/2013/ace/MirexChord2009.zip
+raw_mirex_dir = os.path.join(BASE_DATA_PATH, 'mirex_scores_raw')
+mirex_dir = os.path.join(BASE_DATA_PATH, 'mirex_scores')
+for alg in ALG_NAMES:
+    if not os.path.exists(os.path.join(mirex_dir, alg)):
+        os.makedirs(os.path.join(mirex_dir, alg))
+    name_to_scores = collections.defaultdict(list)
+    for vocab in MIREX_VOCABS:
[…]

### 2014-10-14 code/segmentation/segmentation.py
Updated for new mir_eval, also using path.exists instead of try catch

@@ -42,6 +42,25 @@ ALG_NAMES = ['RBH3', 'RBH2', 'RBH1', 'MP1', 'RBH4', 'MP2', 'CF5', 'CF6']
 
 # <codecell>
 
+if not os.path.exists(BASE_DATA_PATH):
+    os.makedirs(BASE_DATA_PATH)
+
+js_dir = os.path.join(BASE_DATA_PATH, 'raw_js_data')
+reference_dir = os.path.join(BASE_DATA_PATH, 'reference')
+csv_dir = os.path.join(BASE_DATA_PATH, 'mirex_scores_raw')
+raw_js_dir = os.path.join(BASE_DATA_PATH, 'raw_js_data')
+
+if not os.path.exists(js_dir):
+    os.makedirs(js_dir)
+if not os.path.exists(reference_dir):
+    os.makedirs(reference_dir)
+if not os.path.exists(csv_dir):
+    os.makedirs(csv_dir)
+if not os.path.exists(raw_js_dir):
+    os.makedirs(raw_js_dir)
+
+# <codecell>
+
 datasets = ['mrx09', 'mrx10_1', 'mrx10_2', 'sal']
 js_prefixes = ['structmrx09', 'structmrx10', 'structmrx10', 'salami']
 # Salami is missing a bunch of entries
@@ -99,9 +118,6 @@ file_ranges = [range(297),
                           1601, 1602, 1606, 1608, 1609, 1612, 1616, 1621, 1629, 1631, 1632, 1633,
                           1637, 1638])]
 JS_URL = "http://nema.lis.illinois.edu/nema_out/mirex2013/results/struct/{}/segments{}{:06d}.js"
-raw_js_dir = os.path.join(BASE_DATA_PATH, 'raw_js_data')
-if not os.path.exists(raw_js_dir):
-    os.makedirs(raw_js_dir)
 for dataset, js_prefix, file_range in zip(datasets, js_prefixes, file_ranges):
     for n in file_range:
         file_url = JS_URL.format(dataset, js_prefix, n)
@@ -110,9 +126,6 @@ for dataset, js_prefix, file_range in zip(datasets, js_prefixes, file_ranges):
 # <codecell>
 
 RESULT_URL = "http://nema.lis.illinois.edu/nema_out/mirex2013/results/struct/{}/{}/per_track_results.csv"
-csv_dir = os.path.join(BASE_DATA_PATH, 'mirex_scores_raw')
-if not os.path.exists(csv_dir):
[…]

### 2014-10-14 code/chord/build_comparison_set.py
Not using this file anymore

@@ -1,126 +1,0 @@
-"""Mainfile for building a subset of MIREX output data for comparison."""
-
-import argparse
-import csv
-from collections import OrderedDict
-from glob import glob
-import json
-from os.path import join, basename
-from random import shuffle
-
-
-GROUND_TRUTH = 'Ground-truth'
-RESULTS_PREFIX = 'results'
-SCORE_COLUMN_IDX = 1
-
-
-def filebase(fpath):
-    return basename(fpath).split('.')[0]
-
-
-def collect_MIREX_output_data(base_directory):
-    """Randomly sample a collection of output data from MIREX.
-
-    Assumes 'base_directory' has the following structure:
-    base_directory/
-        {AlgorithmCode}/
-            {FileBase}.txt
-        Ground-truth/   <--- This is specific and required.
-            {FileBase}.lab
-        ...
-
-    Parameters
-    ----------
-    base_directory: str
-        Path to a directory of MIREX output data (annotations).
-    num_pairs: int
-        Number of annotation pairs to sample.
-
-    Returns
-    -------
-    reference_files: list
-        List of reference files
-    estimation_files: list
-        List of algorithmic outputs, corresponding to the references.
-    """
-    reference_files = glob(join(base_directory, "%s/*.lab" % GROUND_TRUTH))
-    estimation_fileset = OrderedDict()
-    # Collect estimations and group by filebase.
-    for est_file in glob(join(base_directory, "*/*.txt")):
-        fbase = filebase(est_file)
-        if not fbase in estimation_fileset:
-            estimation_fileset[fbase] = []
-        estimation_fileset[fbase].append(est_file)
-
-    all_refs, all_ests = [], []
-    for ref_file in reference_files:
-        for est_file in estimation_fileset[filebase(ref_file)]:
-            all_refs.append(ref_file)
-            all_ests.append(est_file)
-
-    return all_refs, all_ests
-
-
-def load_MIREX_results(base_directory):
-    """Retrieve the evaluation results for a collection of estimation files.
-
-    Assumes 'base_directory' has the following structure:
-    base_directory/
-        results{TaskName}/
-            {AlgorithmCode}.txt
-            {AlgorithmCode}.csv
-        ...
-
-    Parameters
-    ----------
-    base_directory: str
-        Path to a directory of MIREX output data (annotations).
-    estimation_files: list
-        Files to collect from the results.
-
-    Returns
-    -------
-    results: dunnoyet
-        Results corresponding to each file as a dictionary keyed by TaskName.
-    """
-    results = dict()
[…]

### 2014-10-14 code/beat.py
Flattening dirs

@@ -14,7 +14,6 @@ import os
 import csv
 import mir_eval
 import sys
-sys.path.append('../')
 import convert_json_instants_to_lab
 import shutil
 import joblib
@@ -23,7 +22,7 @@ import numpy as np
 
 # <codecell>
 
-BASE_DATA_PATH = '../../data/beat/'
+BASE_DATA_PATH = '../data/beat/'
 METRIC_KEYS = ['F-Measure', 'Cemgil', 'Goto', 'McKinney P-score', 'CMLc', 'CMLt', 'AMLc', 'AMLt', 'D (bits)']
 ALG_NAMES = ['FW4', 'ZDBG1', 'FW2', 'FW1', 'KFRO1', 'ZDG1', 'ZDG2', 'CDF2', 'CDF1', 'GP3',
              'DP1', 'SB6', 'GP1', 'GKC3', 'SB5', 'GP2', 'ES3', 'ES1', 'EWFS1', 'FK1']

### 2014-10-14 code/chord.py

@@ -7,18 +7,12 @@ import glob
 import os
 import csv
 import mir_eval
-import sys
 import numpy as np
-sys.path.append('../')
-import convert_json_labels_to_lab
-import shutil
-import joblib
-import urllib
 import collections
 
 # <codecell>
 
-BASE_DATA_PATH = '../../data/chord/'
+BASE_DATA_PATH = '../data/chord/'
 # What MIREX calls the vocabs
 MIREX_VOCABS = ["resultsMirexRoot", "resultsMirexMajMin", "resultsMirexMajMinBass",
                 "resultsMirexSevenths", "resultsMirexSeventhsBass"]

### 2014-10-14 code/melody.py

@@ -6,14 +6,13 @@
 import urllib
 import glob
 import os
-import shutil
 import csv
 import mir_eval
 import numpy as np
 
 # <codecell>
 
-BASE_DATA_PATH = '../../data/melody'
+BASE_DATA_PATH = '../data/melody'
 METRIC_KEYS = ['Overall Accuracy', 'Raw Pitch Accuracy', 'Raw Chroma Accuracy', 'Voicing Recall Rate', 'Voicing False-Alarm Rate']
 ALG_NAMES = ['SG2']
 

### 2014-10-14 code/onset.py

@@ -6,8 +6,6 @@
 import urllib
 import glob
 import os
-import sys
-sys.path.append('../')
 import convert_json_instants_to_lab
 import shutil
 import csv
@@ -16,7 +14,7 @@ import numpy as np
 
 # <codecell>
 
-BASE_DATA_PATH = '../../data/onset/'
+BASE_DATA_PATH = '../data/onset/'
 
 METRIC_KEYS = ['Average F-Measure', 'Average precision', 'Average recall']
 ALG_NAMES = ['CB1','CF4','CSF1','FMEGS1','FMESS1','MTB1','SB1','SB2','SB3','SB4','ZHZD1']

### 2014-10-14 code/pattern.py

@@ -6,13 +6,12 @@
 import glob
 import os
 import sys
-import shutil
 import mir_eval
 import numpy as np
 
 # <codecell>
 
-BASE_DATA_PATH = '../../data/pattern/'
+BASE_DATA_PATH = '../data/pattern/'
 METRIC_KEYS = ['P_est', 'R_est', 'F1_est', 'P_occ(c=.75)', 'R_occ(c=.75)', 'F_1occ(c=.75)', 'P_3', 'R_3',
                'TLF_1', 'FFTP_est', 'FFP', 'P_occ(c=.5)', 'R_occ(c=.5)', 'F_1occ(c=.5)', 'P', 'R', 'F_1']
 

### 2014-10-14 code/segmentation.py

@@ -13,9 +13,7 @@ import glob
 import os
 import csv
 import mir_eval
-import sys
 import numpy as np
-sys.path.append('../')
 import convert_json_labels_to_lab
 import shutil
 import joblib
@@ -23,7 +21,7 @@ import urllib
 
 # <codecell>
 
-BASE_DATA_PATH = '../../data/segment/'
+BASE_DATA_PATH = '../data/segment/'
 METRIC_KEYS = ['Normalised conditional entropy based over-segmentation score',
                'Normalised conditional entropy based under-segmentation score',
                'Frame pair clustering F-measure',
